### 2019-03-25 paper/example.tex
Initial commit

\documentclass[9pt]{entcs} \usepackage{entcsmacro}
\usepackage{graphicx}
\sloppy
% The following is enclosed to allow easy detection of differences in
% ascii coding.
% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
% Digits        0 1 2 3 4 5 6 7 8 9
% Exclamation   !           Double quote "          Hash (number) #
% Dollar        $           Percent      %          Ampersand     &
% Acute accent  '           Left paren   (          Right paren   )
% Asterisk      *           Plus         +          Comma         ,
% Minus         -           Point        .          Solidus       /
% Colon         :           Semicolon    ;          Less than     <
% Equals        =3D           Greater than >          Question mark ?
% At            @           Left bracket [          Backslash     \
% Right bracket ]           Circumflex   ^          Underscore    _
% Grave accent  `           Left brace   {          Vertical bar  |
% Right brace   }           Tilde        ~

% A couple of exemplary definitions:

\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\def\lastname{Please list Your Lastname Here}
\begin{document}
\begin{frontmatter}
  \title{An Example Paper} \author{My
    Name\thanksref{ALL}\thanksref{myemail}}
  \address{My Department\\ My University\\
    My City, My Country} \author{My Co-author\thanksref{coemail}}
  \address{My Co-author's Department\\My Co-author's University\\
    My Co-author's City, My Co-author's Country} \thanks[ALL]{Thanks
    to everyone who should be thanked} \thanks[myemail]{Email:
    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}
\begin{abstract} 
  This is a short example to show the basics of using the ENTCS style
  macro files.  Ample examples of how files should look may be found
  among the published volumes of the series at the ENTCS Home Page
  \texttt{http://www.elsevier.com/locate/entcs}.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}
\section{Introduction}
\label{intro}

\subsection*{Preliminaries}

\section{Signature of HITs}

\begin{definition}
Code for polynomials
\end{definition}

\begin{definition}
Endpoints
\end{definition}

\begin{definition}
Signature of a HIT
\end{definition}

\section{Algebras}
Note: algebra structure is point constructor rule.

\begin{definition}
Semantics of a polynomial on sets
\end{definition}

\begin{definition}
Category of prealgebras on a polynomial
\end{definition}

\begin{definition}
Semantics of endpoints
\end{definition}

\begin{definition}
Category of algebras
\end{definition}

\begin{proposition}
The category of algebras is univalent.
\end{proposition}

\begin{definition}
Semantics of a polynomial on setoids
\end{definition}

\begin{definition}
Category of prealgebras on a polynomial (setoids)
\end{definition}

\begin{definition}
Semantics of endpoints (setoids)
\end{definition}

\begin{definition}
Category of algebras in setoids
\end{definition}

\section{Initial Algebra Semantics}

\subsection{The Induction Principle}

\begin{definition}
Displayed algebra
\end{definition}

\begin{definition}
Section for displayed algebra
\end{definition}

\begin{definition}
A HIT: every displayed algebra has a section
\end{definition}

\subsection{Obtaining Induction from Initiality}

\begin{definition}
Total algebra
\end{definition}

\begin{definition}
Projection of total algebra
\end{definition}

\begin{proposition}
Map to total algebra which projects into identity is section.
\end{proposition}

Hence, to construct a HIT, it suffices to construct an initial object in the category of algebras.

\section{Constructing the Initial Algebra}

\subsection{Adjunction between Algebras}
To construct the adjunction between the category of algebras, we use two lemmata

\begin{lemma}
Adjunction between algebras
\end{lemma}

\begin{lemma}
Adjunction between full subcategories
\end{lemma}

\subsection{Initial Setoid Algebra}

Hence, we conclude

\begin{theorem}
HITs exist
\end{theorem}

\section{Consequences}

\subsection{Recursion}

\subsection{Uniqueness of HITs}

\begin{proposition}
Induction implies initiality
\end{proposition}

\begin{corollary}
HITs are initial objects
\end{corollary}

\subsection{Path Spaces of HITs}

\section{Conclusion}

\begin{thebibliography}{10}\label{bibliography}
\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.

\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
  Providence, R.I., 1961.

\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
  Theoretical Computer Science {\bf 1} (1995), URL:
  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.

\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
  preprint 93/52.

\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
  London, New York (1198), 565pp. With associated web site\\  
  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.

\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.

\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
  Press, Princeton, N.J., 1946.

\end{thebibliography}

\end{document}

### 2019-03-26 paper/example.tex
Documentation in code

@@
-\documentclass[9pt]{entcs} \usepackage{entcsmacro}
+\documentclass[9pt]{entcs}
+
+\usepackage{entcsmacro}
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{bussproofs}
+\usepackage{stmaryrd}
+
 \sloppy
@@
 
-% A couple of exemplary definitions:
+\newenvironment{bprooftree}
+{\leavevmode\hbox\bgroup}
+{\DisplayProof\egroup}
 
-\newcommand{\Nat}{{\mathbb N}}
-\newcommand{\Real}{{\mathbb R}}
+\newcommand{\type}[1]{#1}
+\newcommand{\constructor}[1]{#1}
+\newcommand{\category}[1]{#1}
+\newcommand{\functortxt}[1]{#1}
+\newcommand{\nattranstxt}[1]{#1}
+
+\newcommand{\hset}{\type{hSet}} % sets
+\newcommand{\1}{\type{1}} % sets
+
+% Category theory
+\newcommand{\setoids}{\category{Setoid}}
+\newcommand{\functor}[2]{#1 \rightarrow #2} % functors
+\newcommand{\idf}{\functortxt{id}} % identity functor
+\newcommand{\compf}[2]{#1 \circ #2} % composition of functors
+\newcommand{\prodf}[2]{#1 \times #2} % product of functors
+\newcommand{\sumf}[2]{#1 + #2} % sum of functors
+\newcommand{\nattrans}[2]{#1 \Rightarrow #2} % natural transfomations
+\newcommand{\idt}[1]{\nattranstxt{id}} % identity transformation
+\newcommand{\compt}[2]{#1 \circ #2} % composition of natural transformations
+\newcommand{\lwhisker}[2]{#1 \vartriangleleft #2} % left whiskering of transformations
+\newcommand{\inlt}{\nattranstxt{inl}} %left inclusion of transformations
+\newcommand{\inrt}{\nattranstxt{inr}} % right inclusion of transformations
+\newcommand{\prlt}{\nattranstxt{pr}_1} % first projection of transformations
+\newcommand{\prrt}{\nattranstxt{pr}_2} % second projection of transformations
+\newcommand{\pairt}[2]{(#1 , #2)} % pairing of transformations
+
+% Polynomials
+\newcommand{\poly}{\mathcal{P}} % type of polynomials
+\newcommand{\C}{\constructor{C}} % constant polynomial
+\newcommand{\I}{\constructor{I}} % identity polynomial
+\newcommand{\sumP}[2]{#1 + #2} % sum of polynomials
+\newcommand{\prodP}[2]{#1 \times #2} % product of polynomials
+
+% Endpoints
+\newcommand{\ep}[3]{\mathcal{E}_{#1}(#2,#3)} % type of endpoinst
+\newcommand{\id}[1]{\constructor{id}_{#1}} % identity endpoints
+\newcommand{\comp}[2]{#1 \cdot #2} % composition of endpoints
+\newcommand{\inle}{\constructor{inl}} %left inclusion of endpoints
+\newcommand{\inre}{\constructor{inr}} % right inclusion of endpoints
+\newcommand{\prle}{\constructor{pr}_1} % first projection of endpoints
+\newcommand{\prre}{\constructor{pr}_2} % second projection of endpoints
+\newcommand{\pair}[2]{(#1 , #2)} % pairing of endpoints
+\newcommand{\Ce}{\constructor{c}} % constant endpoint
+\newcommand{\constr}{\constructor{constr}} % constructor endpoint
+
+% Algebras
+\newcommand{\semP}[1]{\llbracket #1 \rrbracket} % semantics of polynomials
+\newcommand{\prealg}[1]{\category{PreAlg}(#1)} % category of prealgebras
+\newcommand{\forget}[1]{F_{#1}} % forgetful functor
+\newcommand{\semE}[1]{\llbracket #1 \rrbracket} % semantics of endpoints
+
+% Algebras in setoids
+\newcommand{\semPT}[1]{\langle #1 \rangle} % semantics of polynomials in setoids
+\newcommand{\semET}[1]{\langle #1 \rangle} % semantics of endpoints in setoids
+
 \def\lastname{Please list Your Lastname Here}
@@
 \begin{definition}
-Code for polynomials
+We define the type $\mathcal{\poly}$ inductively by the following rules
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$X : \hset$}
+\UnaryInfC{$\C \> X : \poly$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$\I : \poly$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P : \poly$}
+\AxiomC{$Q : \poly$}
+\BinaryInfC{$\sumP{P}{Q} : \poly$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P : \poly$}
+\AxiomC{$Q : \poly$}
+\BinaryInfC{$\prodP{P}{Q} : \poly$}
+\end{bprooftree}
+\end{center}
 \end{definition}
@@
 \begin{definition}
-Endpoints
+Given polynomials, $A, P, Q : \poly$, we define the type $\ep{A}{P}{Q}$ of endpoints inductively by the following rules
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$P : \poly$}
+\UnaryInfC{$\id{A} : \ep{A}{P}{P}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P, Q, R : \poly$}
+\AxiomC{$e_1 : \ep{A}{P}{Q}$}
+\AxiomC{$e_2 : \ep{A}{Q}{R}$}
+\TrinaryInfC{$\comp{e_1}{e_2} : \ep{A}{P}{R}$}
+\end{bprooftree}
+\end{center}
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$P, Q : \poly$}
+\UnaryInfC{$\inle : \ep{A}{P}{\sumP{P}{Q}}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P, Q : \poly$}
+\UnaryInfC{$\inre : \ep{A}{Q}{\sumP{P}{Q}}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P, Q : \poly$}
+\UnaryInfC{$\prle : \ep{A}{\prodP{P}{Q}}{P}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P, Q : \poly$}
+\UnaryInfC{$\prre : \ep{A}{\prodP{P}{Q}}{Q}$}
+\end{bprooftree}
+\end{center}
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$\constr : \ep{A}{A}{\I}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P : \poly$}
+\AxiomC{$X : \hset$}
+\AxiomC{$x : X$}
+\TrinaryInfC{$\Ce \> x : \ep{A}{P}{\C \> X}$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$P, Q, R: \poly$}
+\AxiomC{$e_1 : \ep{A}{P}{Q}$}
+\AxiomC{$e_2 : \ep{A}{P}{R}$}
+\TrinaryInfC{$\pair{e_1}{e_2} : \ep{A}{P}{\prodP{Q}{R}}$}
+\end{bprooftree}
+\end{center}
 \end{definition}
@@
 \begin{definition}
-Signature of a HIT
+A signature of a higher inductive type consists of
+\begin{enumerate}
+	\item A polynomial $P : \poly$;
+	\item A type $J$;
+	\item A family $Q : J \rightarrow \poly$;
+	\item For each $j : J$, endpoints $l, r : \ep{P}{Q \> j}{I}$.
+\end{enumerate}
 \end{definition}
+
+\begin{example}
+Set with assocative operation.
+\end{example}
+
+Similarly, one can define signatures for groups or finite sets.
+Note that signatures can also depend on types.
+
+\begin{example}
+Propositional truncation of a type
+\end{example}
 
@@
 \begin{definition}
-Semantics of a polynomial on sets
+For each $P : \poly$, we define a functor $\semP{P} : \functor{\hset}{\hset}$. On the objects, they act as follows
+\begin{itemize}
+	\item $\semP{\C \> X} \> Z = X$;
+	\item $\semP{\I} \> Z = Z$;
+	\item $\semP{\sumP{P}{Q}} \> Z = \semP{P} \> Z + \semP{Q} \> Z$;
+	\item $\semP{\sumP{P}{Q}} \> Z = \semP{P} \> Z \times \semP{Q} \> Z$.
+\end{itemize}
 \end{definition}
@@
 \begin{definition}
-Category of prealgebras on a polynomial
+For each $P : \poly$, we define $\prealg{P}$ as the category on algebras on $\semP{P}$.
+\end{definition}
+
+Note that we have a functor $\forget{P} : \functor{\semP{P}}{\hset}$.
+
+To define the interpretation of endpoints, we first note that for every two functors $F, G$ we have a natural transformation $\inlt : \nattrans{F}{\sumf{F}{G}}$, and we also have operations representing the other inclusion and the projections.
+In addition, given $\eta_1 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_2}}$ and $\eta_2 : : \nattrans{\compf{F}{G_1}}{\compf{F}{G_3}}$, we get $\pairt{\eta_1}{\eta_2} : \nattrans{\compf{F}{G_1}}{\compf{F}{\prodf{G_2}{G_3}}}$.
+
+\begin{definition}
+For each endpoint $e : \ep{A}{P}{Q}$, we define a natural transformation $\semE{e} : \nattrans{\compf{\forget{A}}{\semP{P}}} {\compf{\forget{A}}{\semP{Q}}}$
+\begin{itemize}
+	\item $\semE{\id{P}} = \idt{\compf{\forget{A}}{\semP{P}}}$;
+	\item $\semE{\comp{e_1}{e_2}} = \compt{\semE{e_1}}{\semE{e_2}}$;
+	\item $\semE{\inle} = \lwhisker{\forget{A}}{\inlt}$;
+	\item $\semE{\inre} = \lwhisker{\forget{A}}{\inrt}$;
+	\item $\semE{\prle} = \lwhisker{\forget{A}}{\prlt}$;
+	\item $\semE{\prre} = \lwhisker{\forget{A}}{\prrt}$;
+	\item $\semE{\pair{e_1}{e_2}} = \pairt{\semE{e_1}}{\semE{e_2}}$;
+	\item $\semE{\Ce \> t} = $;
+	\item $\semE{\constr} = $.
+\end{itemize}
 \end{definition}
@@
 \begin{definition}
-Semantics of endpoints
+Let $\Sigma$ be a HIT signature.
+Then we define the category of \emph{$\Sigma$-algebras} as the full subcategory of $\prealg{}$ with respect to
 \end{definition}
 
-\begin{definition}
-Category of algebras
-\end{definition}
+Since the category of prealgebra is univalent and univalence is preserved under taking subcategories, we conclude that this category is univalent.
 
@@
 
+Next we define algebras in setoids.
+For these, we take a slightly different approach.
+Instead of defining the interpretation of the polynomial $P$ inductively making use of binary sums and products in $\setoids$, we define an equivalence relation on $\semP{P}$, and show this action is functorial.
+
 \begin{definition}
-Semantics of a polynomial on setoids
+Let $R$ be an equivalence relation on a set $X$ and let $P : \poly$ be a polynomial.
+By induction, we define an equivalence relation $P \> R$ on $\semP{P} \> X$.
+\begin{itemize}
+	\item
+	\item
+	\item
+	\item
+\end{itemize}
+Now we define a functor $\semPT{P} : \functor{\setoids}{\setoids}$ for which $\semPT{P}(X,R) = (\semP{P} \> X, P \> R)$.
+\end{definition}
+
+Again this gives rise to a category $\prealg{P}$
+
+\begin{definition}
+Let $e : \ep{A}{P}{Q}$ be an endpoint and let $X$ be a setoid prealgebra on $A$.
+Then we define $\semE{e}$ to be the setoid morphism from $\semE{P}(X)$ to $\semE{Q}(X)$ whose carrier is $\semP{e}$.
 \end{definition}
@@
 \begin{definition}
-Category of prealgebras on a polynomial (setoids)
+Let $\Sigma$ be a HIT signature.
+Then we define the category of \emph{$\Sigma$-setoid-algebras} as the full subcategory of $\prealg{}$ with respect to
 \end{definition}
 
-\begin{definition}
-Semantics of endpoints (setoids)
-\end{definition}
-
-\begin{definition}
-Category of algebras in setoids
-\end{definition}
+\begin{proposition}
+The category of $\Sigma$-setoid-algebras is unvialent.
+\end{proposition}
 
@@
 \begin{definition}
+Action of polynomials on families.
+\end{definition}
+
+\begin{definition}
+Dependent action of endpoints
+\end{definition}
+
+\begin{definition}
 Displayed algebra
+\end{definition}
+
+\begin{definition}
+Action of polynomials on dependent maps
 \end{definition}
@@
 \subsection{Obtaining Induction from Initiality}
+Now suppose that we have some displayed algebra.
+Our goal is to construct an algebra whose objects are dependent pairs.
 
-\begin{definition}
-Total algebra
-\end{definition}
+Give the carrier and operation in plain text
 
-\begin{definition}
-Projection of total algebra
-\end{definition}
+\begin{lemma}
+pr1 endpoint
+\end{lemma}
+
+\begin{lemma}
+pr2 endpoint
+\end{lemma}
+
+All in all, we get the following construction.
+
+\begin{theorem}
+Total algebra and projection
+\end{theorem}
 
@@
 
+\begin{corollary}
+
+\end{corollary}
+
 \section{Constructing the Initial Algebra}
@@
 \begin{lemma}
-Adjunction between algebras
+Adjunction between prealgebras
 \end{lemma}
@@
 \end{lemma}
+
+All in all, we get
+
+\begin{proposition}
+We have an adjunction
+\end{proposition}
 

### 2019-03-27 paper/example.tex
Work on text

@@
 
+% Setting modes
 \newcommand{\type}[1]{#1}
+\newcommand{\term}[1]{#1}
 \newcommand{\constructor}[1]{#1}
@@
 \newcommand{\nattranstxt}[1]{#1}
+\newcommand{\function}[1]{#1}
 
+% HoTT
+\newcommand{\deprod}[3]{\prod_{#1 : #2} #3}
 \newcommand{\hset}{\type{hSet}} % sets
 \newcommand{\1}{\type{1}} % sets
+\newcommand{\inl}{\term{inl}} %left inclusion
+\newcommand{\inr}{\term{inr}} % right inclusion
+\newcommand{\prl}{\term{pr}_1} % first projection
+\newcommand{\prr}{\term{pr}_2} % second projection
+\newcommand{\pairTm}[2]{(#1 , #2)} % pairing
 
@@
 \newcommand{\pairt}[2]{(#1 , #2)} % pairing of transformations
+\newcommand{\idtoiso}{\function{idtoiso}}
 
@@
 
+% Signatures
+\newcommand{\pt}[0]{pt}
+\newcommand{\pthI}[0]{pthI}
+\newcommand{\pthA}[0]{ptha}
+\newcommand{\pthlh}[0]{pthl}
+\newcommand{\pthrh}[0]{pthr}
+\newcommand{\pointc}[1]{#1_{\pt}} % point constructor
+\newcommand{\pathI}[1]{#1_{\pthI}} % path constructor index
+\newcommand{\pathA}[1]{#1_{\pthA}} % path constructor index
+\newcommand{\pathlh}[1]{#1_{\pthlh}} % left endpoint of path constructor
+\newcommand{\pathrh}[1]{#1_{\pthrh}} % left endpoint of path constructor
+
+\newcommand{\comm}{comm}
+\newcommand{\trunc}{trunc}
+
 % Algebras
@@
 \newcommand{\semET}[1]{\langle #1 \rangle} % semantics of endpoints in setoids
+
+% Displayed algebras
+\newcommand{\polydact}[2]{\overline{#1} \> #2}
+\newcommand{\epdact}[2]{\overline{#1} \> Y}
 
@@
 \section{Signature of HITs}
+Before we study the construction of set truncated HITs, we must first give a precise definition of those.
+We do this by internalizing a scheme, so, more concretely, we define a type of signatures.
+In this section, we give the definition of signatures, and then in the upcoming sections, we define the notion of HITs for a signature.
+
+Higher inductive types are freely generated by both point and path constructors.
+The data of the point constructor is a \emph{polynomial functor}.
+These are described by the following type.
 
 \begin{definition}
-We define the type $\mathcal{\poly}$ inductively by the following rules
+We define the type $\mathcal{\poly}$ of \emph{polynomial functors} inductively by the following rules
 \begin{center}
@@
 
+Next we describe the possible path constructors.
+Note that these depend on the point constructor.
+Furthermore, the path constructors are universally quantified equations of which the arguments depend polynomially on the type being defined.
+Again we use an inductive definition to describe all possibilities.
+
 \begin{definition}
-Given polynomials, $A, P, Q : \poly$, we define the type $\ep{A}{P}{Q}$ of endpoints inductively by the following rules
+Given polynomials, $A, P, Q : \poly$, we define the type $\ep{A}{P}{Q}$ of \emph{endpoints} inductively by the following rules
 \begin{center}
@@
 
+Next we put it all together.
+Note that we index the path constructors by a type meaning that we could possibly have infinitely many path constructors.
+
 \begin{definition}
-A signature of a higher inductive type consists of
+A \emph{HIT signature} $\Sigma$ consists of
 \begin{enumerate}
-	\item A polynomial $P : \poly$;
-	\item A type $J$;
-	\item A family $Q : J \rightarrow \poly$;
-	\item For each $j : J$, endpoints $l, r : \ep{P}{Q \> j}{I}$.
+	\item A polynomial $\pointc{\Sigma} : \poly$;
+	\item A type $\pathI{\Sigma}$;
+	\item A family $\pathA{\Sigma} : \pathI{\Sigma} \rightarrow \poly$;
+	\item For each $j : \pathI{\Sigma}$, endpoints $\pathlh{\Sigma} \> j, \pathrh{\Sigma} \> j : \ep{P}{Q \> j}{I}$.
 \end{enumerate}
@@
 
+To illustrate the possibilities of this definition, we consider two examples.
+The first one is a set with a commutative operation and the second one is the propositional truncation.
+
 \begin{example}
-Set with assocative operation.
+Define a signature $\comm$ such that
+\begin{itemize}
+	\item $\pointc{\comm} = \prodP{\I}{\I}$;
+	\item $\pathI{\comm} = \1$;
+	\item $\pathA{\comm} = \prodP{\I}{\I}$;
+	\item $\pathlh{\comm} \> j = \comp{\constr}{\id{\prodP{\I}{\I}}}$;
+	\item $\pathrh{\comm} \> j = \comp{\constr}{\pair{\comp{\prle}{\id{\prodP{\I}{\I}}}}{\comp{\prre}{\id{\prodP{\I}{\I}}}}}$;
+\end{itemize}
 \end{example}
@@
 Similarly, one can define signatures for groups or finite sets.
-Note that signatures can also depend on types.
+Since signatures can depend on types, we can define the propositional truncation.
 
 \begin{example}
-Propositional truncation of a type
+Let $A$ be a set.
+Define a signature $\trunc$ such that
+\begin{itemize}
+	\item $\pointc{\trunc} = \C \> A$;
+	\item $\pathI{\trunc} = \1$;
+	\item $\pathA{\trunc} = \prodP{\I}{\I}$;
+	\item $\pathlh{\trunc} \> j = \comp{\prle}{\id{\prodP{\I}{\I}}}$;
+	\item $\pathrh{\trunc} \> j = \comp{\prre}{\id{\prodP{\I}{\I}}}$;
+\end{itemize}
 \end{example}
@@
 \section{Algebras}
-Note: algebra structure is point constructor rule.
+Now we know what signatures are, the next goal is to define HITs for signatures.
+One possibility for that, is to immediately give the introduction, elimination, and computation rules.
+However, we refrain to do so.
+Instead we first define a category of algebras and then we say when an algebra is a HIT.
+
+The goal of this section is to define algebras on signatures.
+Since ultimately, we want to construct HITs as quotients, we define algebras both in sets and setoids.
+The algebras in sets are those types which have the correct introduction rules, while we use those in setoids for the quotient.
+
+Let us start by interpreting polynomials as functors.
 
@@
 
-\begin{definition}
-For each $P : \poly$, we define $\prealg{P}$ as the category on algebras on $\semP{P}$.
-\end{definition}
+Now we define the category $\prealg{P}$ to be the category of $\semP{P}$-algebras.
+Its objects are maps $\semP{P} \> X \rightarrow X$ and, for clarity, we call these \emph{prealgebras}.
+Furthermore, note that we have a functor $\forget{P} : \functor{\semP{P}}{\hset}$.
 
-Note that we have a functor $\forget{P} : \functor{\semP{P}}{\hset}$.
-
-To define the interpretation of endpoints, we first note that for every two functors $F, G$ we have a natural transformation $\inlt : \nattrans{F}{\sumf{F}{G}}$, and we also have operations representing the other inclusion and the projections.
-In addition, given $\eta_1 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_2}}$ and $\eta_2 : : \nattrans{\compf{F}{G_1}}{\compf{F}{G_3}}$, we get $\pairt{\eta_1}{\eta_2} : \nattrans{\compf{F}{G_1}}{\compf{F}{\prodf{G_2}{G_3}}}$.
+Endpoints are interpreted as natural transformations.
+Before we give the precise interpretation, we first need that for every two functors $F, G$ we have transformations
+\[
+\inlt : \nattrans{F}{\sumf{F}{G}}
+\quad \quad
+\inrt : \nattrans{G}{\sumf{F}{G}}
+\quad \quad
+\prlt : \nattrans{\prodf{F}{G}}{F}
+\quad \quad
+\prrt : \nattrans{\prodf{F}{G}}{G}
+\]
+In addition, given $\eta_1 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_2}}$ and $\eta_2 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_3}}$, we get $\pairt{\eta_1}{\eta_2} : \nattrans{\compf{F}{G_1}}{\compf{F}{\prodf{G_2}{G_3}}}$.
+With these operations in place, we define
 
@@
 
+Now we have everything in place to define algebras on $\Sigma$.
+An algebra on $\Sigma$ need to have an operation which satisfies certain equations.
+For the operation, we use $\prealg{\pointc{\Sigma}}$.
+Since the carrier of each prealgebra is a set, the equations form a proposition.
+Hence, we define the category of \emph{$\Sigma$-algebras} as a full subcategory of $\prealg{\pointc{\Sigma}}$.
+
 \begin{definition}
 Let $\Sigma$ be a HIT signature.
-Then we define the category of \emph{$\Sigma$-algebras} as the full subcategory of $\prealg{}$ with respect to
+Then we define the category of \emph{$\Sigma$-algebras} as the full subcategory of $\prealg{\pointc{\Sigma}}$ such that each object satisfies
+\[
+\deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x = \semE{\pathrh{\Sigma} \> j} \> x}}.
+\]
 \end{definition}
 
-Since the category of prealgebra is univalent and univalence is preserved under taking subcategories, we conclude that this category is univalent.
+In univalent foundations, the 'right' notion of a category is a ``\emph{univalent category}''.
+In such categories, the notion of equality corresponds with isomorphism.
+More concretely, we have a map $\idtoiso$ which sends equalities $X = Y$ to isomorphisms from $X$ to $Y$, and a category is univalent whenever this map is a weak equivalence.
+By the univalence axiom, the category of sets is univalent.
+
+The category of $\Sigma$-algebras also is univalent, which means that isomorphism of algebras corresponds to equality of algebras.
+This follows from the factor that the category of algebras on a functor is univalent and that univalence is preserved under taking full subcategories.
 
 \begin{proposition}
-The category of algebras is univalent.
+The category of $\Sigma$-algebras is univalent.
 \end{proposition}
 
-Next we define algebras in setoids.
-For these, we take a slightly different approach.
+Before we look at algebras in setoids in more detail, we recall the examples in the previous section and look what algebras on those signatures are.
+
+\begin{example}
+Recall the signature $\comm$.
+An algebra of $\comm$ consists of a set $X$ and a map $f : X \times X \rightarrow X$ such that for all $(x , y) : X \times X$, we have $f(x, y) = f(y, x)$.
+\end{example}
+
+\begin{example}
+Recall the signature $\trunc \> A$.
+An algebra of $\trunc$ consists of a set $X$ and a map $f : A \rightarrow X$ such that for all $(x , y) : X \times X$, we have $x = y$.
+In particular, this means $X$ is a mere proposition.
+\end{example}
+
+Recall that the core idea is that we define the initial algebra in set by taking the quotient of the initial algebra in setoids.
+For that reason, we also need to define algebras in setoids and for these, we take a slightly different approach.
 Instead of defining the interpretation of the polynomial $P$ inductively making use of binary sums and products in $\setoids$, we define an equivalence relation on $\semP{P}$, and show this action is functorial.
@@
 \begin{definition}
-Action of polynomials on families.
+Given are a polynomial $P$ and a family $Y : X \rightarrow \hset$.
+We define a family $\polydact{P}{Y} : \semP{P} \> X \rightarrow \hset$ by induction
+\begin{itemize}
+	\item $\polydact{\C \> X}{Y} \> x = X$;
+	\item $\polydact{\I}{Y} \> x = Y \> x$;
+	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inl \> x) = \polydact{P}{Y} \> x$;
+	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inr \> x) = \polydact{Q}{Y} \> x$;
+	\item $\polydact{\prodP{P}{Q}}{Y} \> (\inl \> x) = \polydact{P}{Y} \> (\prr \> x) \times \polydact{Q}{Y} \> (\prl \> x)$.
+\end{itemize}
 \end{definition}
@@
 \begin{definition}
-Dependent action of endpoints
+Let $A$ be a polynomial, $(X , f)$ be a prealgebra on $A$, and let $e : \ep{A}{P}{Q}$.
+Suppose, we also have a family $Y$ on $X$ and an
+\[
+c : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (f \> z)}.
+\]
+We define, by induction on e, a map
+\[
+\epdact{e}{Y} : \deprod{z}{\semP{P}{X}}{\polydact{P}{Y} \> z \rightarrow \polydact{Q}{Y} \> (\semE{e} \> z)}.
+\]
 \end{definition}
@@
 \begin{definition}
-Displayed algebra
+Let $\Sigma$ be a HIT signature and let $X$ be an algebra on $\sigma$.
+Then a displayed algebra over $X$ consists of
+\begin{itemize}
+	\item A type family $Y : X \rightarrow \hset$;
+	\item An operation 
+	\[
+	c : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (f \> z)};
+	\]
+	\item For each ..., a path
+	\[
+	\]
+\end{itemize} 
 \end{definition}
@@
 \begin{definition}
-Action of polynomials on dependent maps
+Let $Y$ be a displayed algebra over $X$.
+Then a displayed algebra map to $Y$ consists of $f : \deprod{x}{X}{Y \> x}$ such that for each $x : ...$, we have
+\[
+...
+\]
 \end{definition}
@@
 \begin{definition}
-Section for displayed algebra
-\end{definition}
-
-\begin{definition}
-A HIT: every displayed algebra has a section
+Let $\Sigma$ be a HIT signature.
+A HIT on $\Sigma$ consists of an algebra $H$ such that for each displayed algebra $Y$ on $H$, we have a displayed algebra map to $Y$.
 \end{definition}
@@
 \begin{lemma}
-Adjunction between prealgebras
+Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and $F : \functor{\mathcal{C}}{\mathcal{D}}$.
+Then we get a functor 
+\end{lemma}
+
+\begin{lemma}
+Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and an adjunction ....
+Suppose, the following diagrams commute
+
+Then we get an adjunction
 \end{lemma}
@@
 Adjunction between full subcategories
+\end{lemma}
+
+Now we apply these to get an adjunction between set HIT-algebras and setoid HIT-algebras.
+For this, we do the following steps.
+
+\begin{lemma}
+The path setoid commutes with sums and products.
+
+The quotient commutes with sums and products.
+\end{lemma}
+
+\begin{lemma}
+We have a natural isomorphism (path setoid/quotients commutes with polynomials).
+\end{lemma}
+
+Now we can lift the quotient and path setoid.
+We can verify the conditions and we get
+
+\begin{lemma}
+There is an adjunction between prealgebras ...
+\end{lemma}
+
+To show this adjunction lifts to an adjunction between algebras, we need to show that they map algebras to algebras.
+We only show this for the path setoid
+
+\begin{lemma}
+path setoid endpoint
+\end{lemma}
+
+\begin{lemma}
+Path setoid factors through algebras
 \end{lemma}

### 2019-03-28 paper/paper.tex
Further work on paper

\documentclass[9pt]{entcs}

\usepackage{cleveref}
\usepackage{entcsmacro}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bussproofs}
\usepackage{stmaryrd}
\usepackage{cleveref}

\sloppy
% The following is enclosed to allow easy detection of differences in
% ascii coding.
% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
% Digits        0 1 2 3 4 5 6 7 8 9
% Exclamation   !           Double quote "          Hash (number) #
% Dollar        $           Percent      %          Ampersand     &
% Acute accent  '           Left paren   (          Right paren   )
% Asterisk      *           Plus         +          Comma         ,
% Minus         -           Point        .          Solidus       /
% Colon         :           Semicolon    ;          Less than     <
% Equals        =3D           Greater than >          Question mark ?
% At            @           Left bracket [          Backslash     \
% Right bracket ]           Circumflex   ^          Underscore    _
% Grave accent  `           Left brace   {          Vertical bar  |
% Right brace   }           Tilde        ~

\newenvironment{bprooftree}
{\leavevmode\hbox\bgroup}
{\DisplayProof\egroup}

\crefname{lemma}{lemma}{lemmata}
\Crefname{lemma}{lemma}{lemmata}

% Setting modes
\newcommand{\type}[1]{\textsc{#1}}
\newcommand{\term}[1]{\mathsf{#1}}
\newcommand{\constructor}[1]{\mathbf{#1}}
\newcommand{\category}[1]{\textsc{#1}}
\newcommand{\functortxt}[1]{\mathsf{#1}}
\newcommand{\nattranstxt}[1]{\mathsf{#1}}
\newcommand{\function}[1]{\mathsf{#1}}
\newcommand{\morphism}[1]{\mathsf{#1}}

% HoTT
\newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
\newcommand{\hset}{\type{hSet}} % sets
\newcommand{\0}{\textbf{0}} % empty type
\newcommand{\1}{\textbf{1}} % unit type
\newcommand{\inl}{\term{inl}} %left inclusion
\newcommand{\inr}{\term{inr}} % right inclusion
\newcommand{\prl}{\term{pr}_1} % first projection
\newcommand{\prr}{\term{pr}_2} % second projection
\newcommand{\pairTm}[2]{(#1 , #2)} % pairing
\newcommand{\weq}{\simeq} % weak equivalence
\newcommand{\setquot}[2]{#1 / #2} % quotient type
\newcommand{\transport}[2]{\function{transport}^{#1} #2} % transport
\newcommand{\classof}{\constructor{class}} % class construcor
\newcommand{\classeq}{\constructor{classeq}} % path between classes
\newcommand{\isaprop}[1]{\function{isaprop}(#1)} % a type is a set
\newcommand{\isaset}[1]{\function{isaset}(#1)} % a type is a set
\newcommand{\trunct}[1]{\lVert #1 \rVert} % propositional truncation
\newcommand{\truncel}[1]{| #1 |} % constructor of truncation
\newcommand{\depeq}[3]{#2 =_{#1} #3} % dependent equality type

% Category theory
\newcommand{\idm}[1]{\morphism{id}_{#1}} % identity morphism
\newcommand{\compm}[2]{#1 \circ #2} % composition of morphisms
\newcommand{\iso}[2]{#1 \cong #2} % isomorphisms
\newcommand{\setoids}{\category{Setoid}} % category of setoids
\newcommand{\functor}[2]{#1 \longrightarrow #2} % functors
\newcommand{\idf}[1]{\functortxt{id}_{#1}} % identity functor
\newcommand{\Cf}[1]{\functortxt{C}_{#1}} % constant functor
\newcommand{\compf}[2]{#1 \circ #2} % composition of functors
\newcommand{\prodf}[2]{#1 \times #2} % product of functors
\newcommand{\sumf}[2]{#1 + #2} % sum of functors
\newcommand{\nattrans}[2]{#1 \Longrightarrow #2} % natural transfomations
\newcommand{\ctrans}[1]{\nattranstxt{c}_{#1}} % constant transformation
\newcommand{\constrt}[1]{\nattranstxt{constr}_{#1}} % constructor transformation
\newcommand{\idt}[1]{\nattranstxt{id}} % identity transformation
\newcommand{\compt}[2]{#1 \circ #2} % composition of natural transformations
\newcommand{\lwhisker}[2]{#1 \vartriangleleft #2} % left whiskering of transformations
\newcommand{\inlt}{\nattranstxt{inl}} %left inclusion of transformations
\newcommand{\inrt}{\nattranstxt{inr}} % right inclusion of transformations
\newcommand{\prlt}{\nattranstxt{pr}_1} % first projection of transformations
\newcommand{\prrt}{\nattranstxt{pr}_2} % second projection of transformations
\newcommand{\pairt}[2]{(#1 , #2)} % pairing of transformations
\newcommand{\idtoiso}{\function{idtoiso}} % identity to iso

% Polynomials
\newcommand{\poly}{\mathcal{P}} % type of polynomials
\newcommand{\C}{\constructor{C}} % constant polynomial
\newcommand{\I}{\constructor{I}} % identity polynomial
\newcommand{\sumP}[2]{#1 + #2} % sum of polynomials
\newcommand{\prodP}[2]{#1 \times #2} % product of polynomials

% Equivalence relations
\newcommand{\pathR}[1]{\function{Path} \> #1} % path equivalence relation
\newcommand{\sumR}[2]{#1 + #2} % sum of equivalence relations
\newcommand{\prodR}[2]{#1 \times #2} % product of equivalence relations
\newcommand{\polyR}[2]{#1 \> #2} % action of polynomials on equivalence relations

% Endpoints
\newcommand{\ep}[3]{\mathcal{E}_{#1}(#2,#3)} % type of endpoinst
\newcommand{\id}[1]{\constructor{id}_{#1}} % identity endpoints
\newcommand{\comp}[2]{#1 \cdot #2} % composition of endpoints
\newcommand{\inle}{\constructor{inl}} %left inclusion of endpoints
\newcommand{\inre}{\constructor{inr}} % right inclusion of endpoints
\newcommand{\prle}{\constructor{pr}_1} % first projection of endpoints
\newcommand{\prre}{\constructor{pr}_2} % second projection of endpoints
\newcommand{\pair}[2]{(#1 , #2)} % pairing of endpoints
\newcommand{\Ce}{\constructor{c}} % constant endpoint
\newcommand{\constr}{\constructor{constr}} % constructor endpoint

% Signatures
\newcommand{\pt}[0]{\textsf{pt}}
\newcommand{\pthI}[0]{\textsf{pth}}
\newcommand{\pthA}[0]{\textsf{arg}}
\newcommand{\pthlh}[0]{\textsf{lhs}}
\newcommand{\pthrh}[0]{\textsf{rhs}}
\newcommand{\pointc}[1]{#1_{\pt}} % point constructor
\newcommand{\pathI}[1]{#1_{\pthI}} % path constructor index
\newcommand{\pathA}[1]{#1_{\pthA}} % path constructor index
\newcommand{\pathlh}[1]{#1_{\pthlh}} % left endpoint of path constructor
\newcommand{\pathrh}[1]{#1_{\pthrh}} % left endpoint of path constructor

\newcommand{\comm}{\function{comm}}
\newcommand{\trunc}{\function{trunc}}

% Algebras
\newcommand{\semP}[1]{\llbracket #1 \rrbracket} % semantics of polynomials
\newcommand{\prealg}[1]{\category{PreAlg}_{\hset}(#1)} % category of prealgebras
\newcommand{\forget}[1]{F_{#1}} % forgetful functor
\newcommand{\semE}[1]{\llbracket #1 \rrbracket} % semantics of endpoints

\newcommand{\Alg}[1]{\category{Alg}_{\hset}(#1)} % category of algebras
\newcommand{\constrA}[1]{\function{map}_{#1}} % point constructor of algebra
\newcommand{\constrP}[1]{\function{path}_{#1}} % path constructor of algebra

% Algebras in setoids
\newcommand{\semPT}[1]{\langle #1 \rangle} % semantics of polynomials in setoids
\newcommand{\semET}[1]{\langle #1 \rangle} % semantics of endpoints in setoids
\newcommand{\prealgst}[1]{\category{PreAlg}_{\setoids}(#1)} % category of setoid prealgebras
\newcommand{\Algst}[1]{\category{Alg}_{\setoids}(#1)} % category of algebras in setoids

% Displayed algebras
\newcommand{\polydact}[2]{\overline{#1} \> #2}
\newcommand{\epdact}[2]{\overline{#1} \> #2}
\newcommand{\polydmap}[2]{\overline{#1} \> #2}

\def\lastname{Please list Your Lastname Here}
\begin{document}
\begin{frontmatter}
  \title{An Example Paper} \author{My
    Name\thanksref{ALL}\thanksref{myemail}}
  \address{My Department\\ My University\\
    My City, My Country} \author{My Co-author\thanksref{coemail}}
  \address{My Co-author's Department\\My Co-author's University\\
    My Co-author's City, My Co-author's Country} \thanks[ALL]{Thanks
    to everyone who should be thanked} \thanks[myemail]{Email:
    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}
\begin{abstract} 
  This is a short example to show the basics of using the ENTCS style
  macro files.  Ample examples of how files should look may be found
  among the published volumes of the series at the ENTCS Home Page
  \texttt{http://www.elsevier.com/locate/entcs}.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}
\section{Introduction}
\label{intro}

\section{Preliminaries}
\label{sec:prelim}
We start by recalling some definitions from homotopy type theory (HoTT) and fixing the notation.
The first definition we need, is the \emph{dependent equality type}.

\begin{definition}
\label{def:depeq}
Given a type $X$, a type family $Y$ on $X$, and a path $p : x = y$, then we have a map
\[
\transport{Y}{p} : Y \> x \rightarrow Y \> y.
\]
Given a path $p : x = y$ and inhabitants $z_1 : Y \> x$ and $z_2 : Y \> y$, we write $\depeq{p}{z_1}{z_2}$ for $\transport{Y}{p} \> z_1 = z_2$.
\end{definition}

One of the core features of HoTT, is that equality is proof relevant.
This means that not every inhabitant of $x = y$ is necessarily equal.
There might be some types for which this is the case though, and we call such types \emph{sets}.
More precisely, we define

\begin{definition}
\label{def:prop}
\label{def:set}
A type $X$ is a \emph{(mere) proposition} if for all $x, y : X$ we have $x = y$.
A type $X$ is a \emph{set} if for all $x, y : X$ the type $x = y$ is a proposition.
We write $\isaprop{X}$ and $\isaset{X}$ to say that $X$ is a proposition and set respectively.
\end{definition}

To construct higher inductive types, we make use of only two.
These are the \emph{quotient type} and the \emph{propositional truncation}.
For their elimination and computation rules, we refer the reader to the literature.

\begin{definition}
\label{def:quot}
Let $X$ be a type and let $R$ be an equivalence relation on $X$.
The \emph{quotient type} $\setquot{X}{R}$ is the higher inductive type generated by the following rules
\begin{center}
\begin{bprooftree}
\AxiomC{$x : X$}
\UnaryInfC{$\classof \> x : \setquot{X}{R}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$x, y : X$}
\AxiomC{$r : R \> x \> y$}
\BinaryInfC{$\classeq \> r : \classof \> x = \classof \> y$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$\isaset{\setquot{X}{R}}$}
\end{bprooftree}
\end{center}
\end{definition}

\begin{definition}
\label{def:trunc}
Let $X$ be a type.
The \emph{propositional truncation} $\trunct{X}$ is the higher inductive type generated by the following rules
\begin{center}
\begin{bprooftree}
\AxiomC{$x : X$}
\UnaryInfC{$\truncel{x} : \trunct{X}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$\isaprop{\trunct{X}}$}
\end{bprooftree}
\end{center}
\end{definition}

Next we briefly discuss category theory in univalent foundations.
We start by recalling the definition of categories.
This is almost the same as the usual definition in mathematics, but their is a slight discrepancy between the objects and arrows.
While the objects can be any type, the arrows have to form a set.
If equality was proof relevant, then this would give the structure of a higher category instead of an ordinary one.
This leads to the following definition.

\begin{definition}
\label{def:cat}
A \emph{category} $\mathcal{C}$ consists of
\begin{itemize}
	\item a type $\mathcal{C}_0$ of objects;
	\item for each $X, Y : \mathcal{C}_0$ a set $\mathcal{C}_1(X,Y)$ of morphisms;
	\item for each $X : \mathcal{C}_0$ a morphisms $\idm{X}$;
	\item for all objects $X, Y, Z : \mathcal{C}_0$ and morphisms $f : \mathcal{C}_1(X,Y)$ and $g : \mathcal{C}_1(Y,Z)$, a morphism $\compm{f}{g} : \mathcal{C}_1(X,Z)$
\end{itemize}
such that the usual associativity and identity laws holds.
\end{definition}

We define isomorphisms in the usual way and we denote the type of isomorphisms from $X$ to $Y$ by $\iso{X}{Y}$.
... is the notion of \emph{univalent categories}.
These are categories in which equality on objects is equivalent to isomorphisms between them.
More precisely, we define them as follows.

\begin{definition}
\label{def:univalent}
Let $\mathcal{C}$ be a category.
Note that for all objects $X$ and $Y$ we have a map $\idtoiso_{X,Y} : X = Y \rightarrow \iso{X}{Y}$ sending the reflexivity path to the identity isomorphism.
Then we say $\mathcal{C}$ is \emph{univalent} if $\idtoiso_{X,Y}$ is a weak equivalence for each $X$ and $Y$.
\end{definition}

The primary example of a univalent category is the category $\hset$ of sets and functions between them.
Its univalence follows from the univalence axiom.
Another example of a univalent category which we use frequently, is the category of \emph{setoids}.

\begin{definition}
\label{def:setoid}
We define
\begin{itemize}
	\item A \emph{setoid} is a set $X$ together with an equivalence relation on $X$;
	\item A \emph{setoid morphism} between two setoids  is a map between the underlying sets which preserves the equivalence relation.
\end{itemize}
The \emph{category of setoids} $\setoids$ is the category with setoids and setoid morphisms as objects and morphisms.
\end{definition}

If $X$ is a set and $R$ is an equivalence relation on $X$, then we write $(X, R)$ for the setoid with this data.
When it is clear from the context, we write $\equiv$ for the relation.
We finish this section by giving some operations of functor and natural transformations.
For categories $\mathcal{C}$ and $\mathcal{D}$, we write $\functor{\mathcal{C}}{\mathcal{D}}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$.
For functor $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we write $\nattrans{F}{G}$ for the type of natural transformations from $\mathcal{F}$ to $\mathcal{G}$.

\begin{lemma}
\label{def:functor}
We have the following functors.
\begin{itemize}
	\item For each category $\mathcal{C}$, we have the identity $\idf{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$.
	\item For $F : \functor{\mathcal{C}_1}{\mathcal{C}_2}$ and $G : \functor{\mathcal{C}_2}{\mathcal{C}_3}$, we have a composition $\compf{F}{G} : \functor{\mathcal{C}_1}{\mathcal{C}_2}$;
	\item If $\mathcal{D}$ has binary products, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a product $\prodf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
	\item If $\mathcal{D}$ has binary sum, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a sum $\sumf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
	\item For each object $X : \mathcal{D}$, we have a constant functor $\Cf{X} : \functor{\mathcal{C}}{\mathcal{D}}$.
\end{itemize}
\end{lemma}

\begin{lemma}
\label{def:nattrans}
We have the following transformations.
\begin{itemize}
	\item Suppose, $F, G : \functor{\mathcal{C}}{\mathcal{D}}$
	\[
	\inlt : \nattrans{F}{\sumf{F}{G}}
	\quad \quad
	\inrt : \nattrans{G}{\sumf{F}{G}}
	\quad \quad
	\prlt : \nattrans{\prodf{F}{G}}{F}
	\quad \quad
	\prrt : \nattrans{\prodf{F}{G}}{G}
	\]
	\item Given two transformations $\eta_1 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_2}}$ and $\eta_2 : \nattrans{\compf{F}{G_1}}{\compf{F}{G_3}}$, we have a pairing 
	\[
	\pairt{\eta_1}{\eta_2} : \nattrans{\compf{F}{G_1}}{\compf{F}{\prodf{G_2}{G_3}}}.
	\]
	\item Given functors $F : \functor{\mathcal{C}_1}{\mathcal{C}_2}$ and $G_1. G_2 : \functor{\mathcal{C}_2}{\mathcal{C}_3}$, and a transformation $\eta : \nattrans{G_1}{G_2}$, we have
	\[
	\lwhisker{F}{\eta} : \nattrans{\compf{F}{G_1}}{\compf{F}{G_2}}
	\]
	\item Given a functor $F : \functor{\mathcal{C}}{\hset}$, a set $X : \hset$, and $x : X$, we have a transformation $\ctrans{x} : \nattrans{F}{\Cf{X}}$
\end{itemize}
\end{lemma}

\section{Signature of HITs}
\label{sec:signature}
Before we study the construction of set truncated HITs, we first give a precise definition of those.
We do this by internalizing a scheme, so, more concretely, we define a type of signatures.
In this section, we give the definition of signatures, and then in the upcoming sections, we define the notion of HITs for a signature.

Higher inductive types are freely generated by both point and path constructors.
The data of the point constructor is a \emph{polynomial functor}.
These are described by the following type.

\begin{definition}
\label{def:poly}
We define the type $\mathcal{\poly}$ of \emph{polynomial functors} inductively by the following rules
\begin{center}
\begin{bprooftree}
\AxiomC{$X : \hset$}
\UnaryInfC{$\C \> X : \poly$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$\I : \poly$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P : \poly$}
\AxiomC{$Q : \poly$}
\BinaryInfC{$\sumP{P}{Q} : \poly$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P : \poly$}
\AxiomC{$Q : \poly$}
\BinaryInfC{$\prodP{P}{Q} : \poly$}
\end{bprooftree}
\end{center}
\end{definition}

Next we describe the possible path constructors.
Note that these depend on the point constructor.
Furthermore, the path constructors are universally quantified equations of which the arguments depend polynomially on the type being defined.
Again we use an inductive definition to describe all possibilities.

\begin{definition}
\label{def:endpoint}
Given polynomials, $A, P, Q : \poly$, we define the type $\ep{A}{P}{Q}$ of \emph{endpoints} inductively by the following rules
\begin{center}
\begin{bprooftree}
\AxiomC{$P : \poly$}
\UnaryInfC{$\id{A} : \ep{A}{P}{P}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P, Q, R : \poly$}
\AxiomC{$e_1 : \ep{A}{P}{Q}$}
\AxiomC{$e_2 : \ep{A}{Q}{R}$}
\TrinaryInfC{$\comp{e_1}{e_2} : \ep{A}{P}{R}$}
\end{bprooftree}
\end{center}
\begin{center}
\begin{bprooftree}
\AxiomC{$P, Q : \poly$}
\UnaryInfC{$\inle : \ep{A}{P}{\sumP{P}{Q}}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P, Q : \poly$}
\UnaryInfC{$\inre : \ep{A}{Q}{\sumP{P}{Q}}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P, Q : \poly$}
\UnaryInfC{$\prle : \ep{A}{\prodP{P}{Q}}{P}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P, Q : \poly$}
\UnaryInfC{$\prre : \ep{A}{\prodP{P}{Q}}{Q}$}
\end{bprooftree}
\end{center}
\begin{center}
\begin{bprooftree}
\AxiomC{$\constr : \ep{A}{A}{\I}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P : \poly$}
\AxiomC{$X : \hset$}
\AxiomC{$x : X$}
\TrinaryInfC{$\Ce \> x : \ep{A}{P}{\C \> X}$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P, Q, R: \poly$}
\AxiomC{$e_1 : \ep{A}{P}{Q}$}
\AxiomC{$e_2 : \ep{A}{P}{R}$}
\TrinaryInfC{$\pair{e_1}{e_2} : \ep{A}{P}{\prodP{Q}{R}}$}
\end{bprooftree}
\end{center}
\end{definition}

Next we put it all together.
Note that we index the path constructors by a type meaning that we could possibly have infinitely many path constructors.

\begin{definition}
\label{def:signature}
A \emph{HIT signature} $\Sigma$ consists of
\begin{itemize}
	\item A polynomial $\pointc{\Sigma} : \poly$;
	\item A type $\pathI{\Sigma}$;
	\item A family $\pathA{\Sigma} : \pathI{\Sigma} \rightarrow \poly$;
	\item For each $j : \pathI{\Sigma}$, endpoints $\pathlh{\Sigma} \> j, \pathrh{\Sigma} \> j : \ep{P}{Q \> j}{I}$.
\end{itemize}
\end{definition}

To illustrate the possibilities of this definition, we consider two examples.
The first one is a set with a commutative operation and the second one is the propositional truncation.

\begin{example}
\label{ex:commsig}
Define a signature $\comm$ such that
\begin{itemize}
	\item $\pointc{\comm} = \prodP{\I}{\I}$;
	\item $\pathI{\comm} = \1$;
	\item $\pathA{\comm} = \prodP{\I}{\I}$;
	\item $\pathlh{\comm} \> j = \comp{\constr}{\id{\prodP{\I}{\I}}}$;
	\item $\pathrh{\comm} \> j = \comp{\constr}{\pair{\comp{\prle}{\id{\prodP{\I}{\I}}}}{\comp{\prre}{\id{\prodP{\I}{\I}}}}}$;
\end{itemize}
\end{example}

Similarly, one can define signatures for groups or finite sets.
Since signatures can depend on types, we can define the propositional truncation.

\begin{example}
\label{ex:truncsig}
Let $A$ be a set.
Define a signature $\trunc$ such that
\begin{itemize}
	\item $\pointc{\trunc} = \C \> A$;
	\item $\pathI{\trunc} = \1$;
	\item $\pathA{\trunc} = \prodP{\I}{\I}$;
	\item $\pathlh{\trunc} \> j = \comp{\prle}{\id{\prodP{\I}{\I}}}$;
	\item $\pathrh{\trunc} \> j = \comp{\prre}{\id{\prodP{\I}{\I}}}$;
\end{itemize}
\end{example}

\section{Algebras}
\label{sec:algebras}
Now we know what signatures are, the next goal is to define HITs for signatures.
For that we need to give its introduction, elimination, and computation rules.
In this section, we study the introduction rule of HITs and we do that by defining a category of algebras on a polynomial.
Furthermore, since ultimately we want to construct HITs as quotients, we do not just define algebra in sets, but also in setoids.
Let us start by interpreting polynomials as functors.

\begin{definition}
\label{def:sempoly}
For each $P : \poly$, we define a functor $\semP{P} : \functor{\hset}{\hset}$ as follows
\begin{itemize}
	\item $\semP{\C \> X} = \Cf{X}$;
	\item $\semP{\I} = \idf{\hset}$;
	\item $\semP{\sumP{P}{Q}} = \sumf{\semP{P}}{\semP{Q}}$;
	\item $\semP{\sumP{P}{Q}} = \prodf{\semP{P}}{\semP{Q}}$.
\end{itemize}
\end{definition}

Now we define the category $\prealg{\Sigma}$ to be the category of algebras on the functor $\semP{\pointc{\Sigma}}$.
Its objects are maps $\semP{\pointc{\Sigma}} \> X \rightarrow X$.
We call this the category of \emph{prealgebras} since these do not yet satisfy the equations in $\Sigma$.
Note that we always have a forgetful functor $\forget{P} : \functor{\semP{P}}{\hset}$.

To obtain actual algebras of $\Sigma$, we need to be able to interpret the equations and for that, we first need to interpret endpoints.
These are interpreted as natural transformations, which are constructed using the transformations from Lemma \ref{def:nattrans}.
Beside those, we need a transformation $\constrt{P} : \nattrans{\comp{\forget{P}}{\semP{P}}}{\comp{\forget{P}}{\semP{\I}}}$ for each polynomial $P$.
Its components are given by the prealgebra map.

\begin{definition}
\label{def:semendpoint}
For each endpoint $e : \ep{A}{P}{Q}$, we define a natural transformation $\semE{e} : \nattrans{\compf{\forget{A}}{\semP{P}}} {\compf{\forget{A}}{\semP{Q}}}$
\begin{itemize}
	\item $\semE{\id{P}} = \idt{\compf{\forget{A}}{\semP{P}}}$;
	\item $\semE{\comp{e_1}{e_2}} = \compt{\semE{e_1}}{\semE{e_2}}$;
	\item $\semE{\inle} = \lwhisker{\forget{A}}{\inlt}$;
	\item $\semE{\inre} = \lwhisker{\forget{A}}{\inrt}$;
	\item $\semE{\prle} = \lwhisker{\forget{A}}{\prlt}$;
	\item $\semE{\prre} = \lwhisker{\forget{A}}{\prrt}$;
	\item $\semE{\pair{e_1}{e_2}} = \pairt{\semE{e_1}}{\semE{e_2}}$;
	\item $\semE{\Ce \> t} = \ctrans{t}$;
	\item $\semE{\constr} = \constrt{A}$.
\end{itemize}
\end{definition}

Now we have everything in place to define algebras on $\Sigma$.
An algebra on $\Sigma$ need to have an operation which satisfies certain equations.
For the operation, we use $\prealg{\pointc{\Sigma}}$.
Since the carrier of each prealgebra is a set, the equations form a proposition.
Hence, we define the category of \emph{$\Sigma$-algebras} as a full subcategory of $\prealg{\pointc{\Sigma}}$.

\begin{definition}
\label{def:algebra}
Let $\Sigma$ be a HIT signature.
Then we define the category $\Alg{\Sigma}$ of \emph{$\Sigma$-algebras} as the full subcategory of $\prealg{\pointc{\Sigma}}$ such that each object satisfies
\[
\deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x = \semE{\pathrh{\Sigma} \> j} \> x}}.
\]
\end{definition}

For an algebra $X$, we denote its operation by $\constrA{X} : \semP{\pointc{\Sigma}} \> X \rightarrow X$.
The path witnessing the equalities of the algebra is denoted by $\constrP{X} : \deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x = \semE{\pathrh{\Sigma} \> j} \> x}}$.
The category of $\Sigma$-algebras is univalent, which means that isomorphism of algebras corresponds to equality of algebras.
This follows from the fact that the category of algebras on a functor is univalent and that univalence is preserved under taking full subcategories.

\begin{proposition}
\label{prop:univalg}
The category of $\Sigma$-algebras is univalent.
\end{proposition}

Before we look at algebras in setoids in more detail, we recall the examples in the previous section and look what algebras on those signatures are.

\begin{example}
\label{ex:commalg}
Recall the signature $\comm$ from Example \ref{ex:commsig}.
An algebra of $\comm$ consists of a set $X$ and a map $f : X \times X \rightarrow X$ such that for all $(x , y) : X \times X$, we have $f(x, y) = f(y, x)$.
\end{example}

\begin{example}
\label{ex:truncalg}
Recall $\trunc$ from Example \ref{ex:truncsig}.
For a set $A$. an algebra of $\trunc \> A$ consists of a set $X$ and a map $f : A \rightarrow X$ such that for all $(x , y) : X \times X$, we have $x = y$.
In particular, this means $X$ is a proposition.
\end{example}

Recall that the core idea is that we define the initial algebra in sets by taking the quotient of the initial algebra in setoids.
For that reason, we also define algebras in setoids and for these, we take a slightly different approach.
Instead of defining the interpretation of the polynomial $P$ inductively making use of binary sums and products in $\setoids$, we define an equivalence relation on $\semP{P}$.

To define the action of polynomials on equivalence relations, we need so preliminary operations.
For a set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y = (x = y)$.
Furthermore, given types $X$ and $Y$ with equivalence relations $R_X$ and $R_Y$ on them, we can define equivalence relations $\sumR{R_X}{R_Y}$ and $\prodR{R_X}{R_Y}$ on $X + Y$ and $X \times Y$ respectively.
These are defined such that
\[
\prodR{R_X}{R_Y} \> (x_1,y_1) \> (x_2,y_2) = (R_X \> x_1 \> x_2) \times (R_Y \> y_1 \> y_2)
\]
\[
\begin{array}{ccc}
\sumR{R_X}{R_Y} \> (\inl \> x_1) \> (\inl \> x_2) = R_X \> x_1 \> x_2 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y_1) \> (\inr \> y_2) = R_Y \> y_1 \> y_2\\
\sumR{R_X}{R_Y} \> (\inl \> x) \> (\inr \> y) = \0 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y) \> (\inl \> x) = \0\\ 
\end{array}
\]

\begin{definition}
Let $R$ be an equivalence relation on a set $X$ and let $P : \poly$ be a polynomial.
By induction, we define an equivalence relation $\polyR{P}{R}$ on $\semP{P} \> X$.
\begin{itemize}
	\item $\polyR{(\C \> T)}{R} = \pathR{T}$;
	\item $\polyR{\I}{R} = R$;
	\item $\polyR{(\sumP{P}{Q})}{R} = \sumR{(\polyR{P}{R})}{(\polyR{Q}{R})}$;
	\item $\polyR{(\prodP{P}{Q})}{R} = \prodR{(\polyR{P}{R})}{(\polyR{Q}{R})}$.
\end{itemize}
Now we define a functor $\semPT{P} : \functor{\setoids}{\setoids}$ such that $\semPT{P}(X,R) = (\semP{P} \> X, P \> R)$.
\end{definition}

Again this gives rise to a category $\prealgst{\Sigma}$ of \emph{setoid prealgebras on $\Sigma$}.
To define algebras on $\Sigma$, we also need to interpret endpoints.
However, these are just setoid morphisms instead of natural transformations.

\begin{definition}
Let $e : \ep{A}{P}{Q}$ be an endpoint and let $X$ be a setoid prealgebra on $A$.
Then we define $\semE{e}$ to be the setoid morphism from $\semE{P}(X)$ to $\semE{Q}(X)$ whose carrier is $\semP{e}$.
\end{definition}

The category of algebras on $\Sigma$ is defined differently for setoids that for sets.
While for sets we require actual equalities, for setoids the equations need to be witnessed by the equivalence relation instead.
Note that such relations are families of propositions meaning again this gives rise to a proposition and thus we define i as a full subcategory.

\begin{definition}
Let $\Sigma$ be a HIT signature.
Then we define the category of \emph{$\Sigma$-setoid-algebras} as the full subcategory of $\prealgst{\pointc{\Sigma}}$ such that each object satisfies
\[
\deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x \equiv \semE{\pathrh{\Sigma} \> j} \> x}}.
\]
\end{definition}

Since the category of setoids is univalent, the category of $\Sigma$-setoid-algebras is univalent as well.

\begin{proposition}
The category of $\Sigma$-setoid-algebras is unvialent.
\end{proposition}

\section{The Induction Principle}
\label{sec:induction}
The introduction rules of higher inductive types are covered by the algebra structure, but the elimination and computation rules require additional structure.
The main feature of the elimination rule is that it allows defining dependent ``homomorphisms'' to families with some kind of ``dependent algebra structures'' and the computation rule says the algebraic structure is preserved.
To formulate these two rules, we make use of \emph{displayed algebras}, which represent the input of the elimination rule.
When we got all this machinery in place, we define the notion of \emph{higher inductive type} for a signature.

Since our goal is to construct HITs, we need verify the induction rule and for that, we use initial algebra semantics.
More specifically, we show that the initial algebra satisfies the induction rule.
Hence, to obtain it a HIT, it suffices to construct the initial algebra for which we use category theory.

\subsection{Displayed Algebras}
A displayed algebra is the input of the elimination rule.
This means that we have a dependent family and a dependent map over the point constructor.
Furthermore, dependent versions of the equations in the signature needs to hold.
To formulate these requirements more precisely, we need two preliminary definitions.
The first one gives an action of polynomials on type families while the second one interprets endpoints as dependent maps.

\begin{definition}
Given are a polynomial $P$ and a family $Y : X \rightarrow \hset$.
We define a family $\polydact{P}{Y} : \semP{P} \> X \rightarrow \hset$ by induction
\begin{itemize}
	\item $\polydact{\C \> X}{Y} \> x = X$;
	\item $\polydact{\I}{Y} \> x = Y \> x$;
	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inl \> x) = \polydact{P}{Y} \> x$;
	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inr \> x) = \polydact{Q}{Y} \> x$;
	\item $\polydact{\prodP{P}{Q}}{Y} \> x = \polydact{P}{Y} \> (\prl \> x) \times \polydact{Q}{Y} \> (\prr \> x)$.
\end{itemize}
\end{definition}

\begin{definition}
Let $A$ be a polynomial, $X$ be a prealgebra on $A$, and let $e : \ep{A}{P}{Q}$.
Suppose, we have a family $Y$ on $X$ and a map $c : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)}$.
We define a map $\epdact{e}{c} : \deprod{z}{\semP{P}{X}}{\polydact{P}{Y} \> z \rightarrow \polydact{Q}{Y} \> (\semE{e} \> z)}$ by induction on $e$
\begin{itemize}
	\item $\epdact{\id{P}}{c} \> z \> y = y$;
	\item $\epdact{\comp{e_1}{e_2}}{c} \> z \> y = \epdact{e_2}{c} \> (\semE{e} \> X \> z) \> (\epdact{e_1}{c} \> z \> y)$;
	\item $\epdact{\inle}{c} \> z \> y = y$;
	\item $\epdact{\inre}{c} \> z \> y = y$;
	\item $\epdact{\prle}{c} \> z \> y = \prlt \> y$;
	\item $\epdact{\prre}{c} \> z \> y = \prrt \> y$;
	\item $\epdact{\pair{e_1}{e_2}}{c} \> z \> y = (\epdact{e_1}{c} \> z \> y , \epdact{e_2}{c} \> z \> y)$;
	\item $\epdact{\Ce \> t}{c} \> z \> y = t$;
	\item $\epdact{\constr}{c} = c$.
\end{itemize}
\end{definition}

With this in place, we define displayed algebras.
Note that since we are working in a type family, we need to use the dependent equality type from Definition \ref{def:depeq} instead.

\begin{definition}
Let $\Sigma$ be a HIT signature and let $X$ be an algebra on $\sigma$.
Then a \emph{displayed algebra} over $X$ consists of
\begin{itemize}
	\item A type family $Y : X \rightarrow \hset$;
	\item An operation $c_Y : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)}$;
	\item For each $j : \pathI{\Sigma}$, $x : \semP{\pathA{\Sigma}} \> X$, and $y : \polydact{\pathA{\Sigma}}{Y} \> x$,  a path $p_Y : \depeq{\constrP{X} \> j \> x}{\epdact{\pathlh{\Sigma}}{c} \> x \> y}{\epdact{\pathrh{\Sigma}}{c} \> x \> y}$.
\end{itemize} 
\end{definition}

Now we got the input for the elimination rule in place and the next step is to look at the output.
This is a dependent map which preserves the algebra structure.
To state this preservation property, we need yet another operation on polynomials.

\begin{definition}
Let $P$ be a polynomial, let $X$ be a set, and let $Y$ be a family of sets on $X$.
Given a map $f : \deprod{x}{X}{Y \> x}$, we define a map $\polydmap{P}{f} : \deprod{x}{\semP{P} \> X}{\polydact{P}{Y} \> x}$ by induction
\begin{itemize}
	\item $\polydmap{\C \> X}{f} \> x = x$;
	\item $\polydmap{\I}{f} = f$;
	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inl \> x) = \polydmap{P}{f} \> x$;
	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inr \> x) = \polydmap{Q}{f} \> x$;
	\item $\polydmap{\prodP{P}{Q}}{f} \> x = (\polydact{P}{f} \> (\prl \> x) , \polydact{Q}{f} \> (\prr \> x))$.
\end{itemize}
\end{definition}

\begin{definition}
Let $Y$ be a displayed algebra over $X$.
Then a displayed algebra map to $Y$ consists of a map $f : \deprod{x}{X}{Y \> x}$ such that for each $x : \semP{\pointc{\Sigma}}{X}$, we have $f(\constrA{X} \> x) = c_Y \> x \> (\polydmap{\pointc{\Sigma}}{f} \> x)$.
\end{definition}

With all this in place, we can define the notion of a \emph{higher inductive type} on a signature.
Note that a HIT needs to be an algebra so that we have the correct introduction rules and note that we use displayed algebras to formulate the elimination principle.

\begin{definition}
Let $\Sigma$ be a HIT signature.
A \emph{higher inductive type} on $\Sigma$ consists of an algebra $H$ such that for each displayed algebra $Y$ on $H$, we have a displayed algebra map to $Y$.
\end{definition}

\subsection{Obtaining Induction from Initiality}
Now suppose that we have some displayed algebra.
Our goal is to construct an algebra whose objects are dependent pairs.

Give the carrier and operation in plain text

\begin{lemma}
pr1 endpoint
\end{lemma}

\begin{lemma}
pr2 endpoint
\end{lemma}

All in all, we get the following construction.

\begin{theorem}
Total algebra and projection
\end{theorem}

\begin{proposition}
Map to total algebra which projects into identity is section.
\end{proposition}

Hence, to construct a HIT, it suffices to construct an initial object in the category of algebras.

\begin{corollary}

\end{corollary}

\section{Constructing the Initial Algebra}

\subsection{Adjunction between Algebras}
To construct the adjunction between the category of algebras, we use two lemmata

\begin{lemma}
Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and $F : \functor{\mathcal{C}}{\mathcal{D}}$.
Then we get a functor 
\end{lemma}

\begin{lemma}
Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and an adjunction ....
Suppose, the following diagrams commute

Then we get an adjunction
\end{lemma}

\begin{lemma}
Adjunction between full subcategories
\end{lemma}

Now we apply these to get an adjunction between set HIT-algebras and setoid HIT-algebras.
For this, we do the following steps.

\begin{lemma}
The path setoid commutes with sums and products.

The quotient commutes with sums and products.
\end{lemma}

\begin{lemma}
We have a natural isomorphism (path setoid/quotients commutes with polynomials).
\end{lemma}

Now we can lift the quotient and path setoid.
We can verify the conditions and we get

\begin{lemma}
There is an adjunction between prealgebras ...
\end{lemma}

To show this adjunction lifts to an adjunction between algebras, we need to show that they map algebras to algebras.
We only show this for the path setoid

\begin{lemma}
path setoid endpoint
\end{lemma}

\begin{lemma}
Path setoid factors through algebras
\end{lemma}

All in all, we get

\begin{proposition}
We have an adjunction
\end{proposition}

\subsection{Initial Setoid Algebra}

Hence, we conclude

\begin{theorem}
HITs exist
\end{theorem}

\section{Consequences}

\subsection{Recursion}

\begin{definition}
Let $X$ and $Y$ be algebras on $\Sigma$.
Then we define the \emph{constant displayed algebra} on $X$ from $Y$ as follows
\begin{itemize}
	\item The type family is $Y$ for each $x$;
	\item
\end{itemize}
\end{definition}

\begin{proposition}
Let $X$ be $Y$ be algebras on $\Sigma$.
If we have a displayed algebra from $X$ to the constant displayed algebra on $X$ from $Y$, then we have an algebra homomorphism from $X$ to $Y$.
\end{proposition}

\begin{corollary}
If $X$ is a HIT for $\Sigma$, then for each algebra $Y$ we have an algebra map from $X$ to $Y$.
\end{corollary}

\subsection{Uniqueness of HITs}
A first property of higher inductive types, is that they are unique up to equality.
For that, we first show that higher inductives are initial algebras.
Note that in \Cref{sec:induction} we made use of the converse statement, namely that initial algebras are HITs.

To show a HIT $H$ is initial, we must show that for each algebra $X$ the set of morphisms from $H$ to $X$ is contractible.
This means that there is at most one morphism.
To show the existence, we use the recursion rule.
To show uniqueness, we use an alternative induction principle for families of propositions.
More specifically, we use the following lemma.

\begin{lemma}
Let $H$ be a HIT of $\Sigma$ and suppose $Y$ is a family of propositions on $H$.
If we have an operation
\[
c : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (f \> z)},
\]
then we have a map $\deprod{x}{H}{Y \> x}$.
\end{lemma}

To prove the uniqueness of the map, we use function extensionality and the previous lemma.
This is sufficient to conclude that higher inductive types are initial objects.

\begin{proposition}
If $H$ is a HIT for $\Sigma$, then $H$ is an initial $\Sigma$-algebra.
\end{proposition}

Now we take advantage of the fact that the category of algebras is univalent.
Since initial objects in a univalent category are unique up to equality, we can immediately conclude that HITs are actually unique up to equality.
All in all, we get

\begin{theorem}
If $H_1$ and $H_2$ are HITs for $\Sigma$, the $H_1 = H_2$ as $\Sigma$-algebras.
\end{theorem}

\subsection{Path Spaces of HITs}
The construction of HITs also allows us to characterize the path space up to equivalence.

\begin{proposition}
Let $X$ be a type and let $R$ be an equivalence relation on $X$.
Then for each $x, y : X$, we have an equivalence $R \> x \> y \weq \classof \> x = \classof \> y$.
\end{proposition}

\section{Conclusion}

\begin{thebibliography}{10}\label{bibliography}
\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.

\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
  Providence, R.I., 1961.

\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
  Theoretical Computer Science {\bf 1} (1995), URL:
  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.

\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
  preprint 93/52.

\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
  London, New York (1198), 565pp. With associated web site\\  
  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.

\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.

\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
  Press, Princeton, N.J., 1946.

\end{thebibliography}

\end{document}

### 2019-03-30 paper/paper.tex
Work on induction principle

@@
 \usepackage{cleveref}
+\usepackage{listings}
+\usepackage{coq}
+\usepackage{color}
+\usepackage{xcolor}
 
@@
 
+\newcommand{\ie}{\emph{i.e.,} }
+\newcommand{\cf}{\emph{c.f.} }
+\newcommand{\eg}{\emph{e.g.,} }
+\newcommand{\etal}{\emph{et~al.}}
+\newcommand{\etc}{\emph{etc.}}
+\newcommand{\wrt}{w.r.t.~}
+\newcommand{\resp}{resp.~}
+\newcommand{\loccit}{\emph{loc. cit.} }
+
 % Setting modes
@@
 \newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
+\newcommand{\desum}[3]{\sum_{#1 : #2} #3} % dependent sum
 \newcommand{\hset}{\type{hSet}} % sets
@@
 \newcommand{\transport}[2]{\function{transport}^{#1} #2} % transport
+\newcommand{\invP}[1]{(#1)^{-1}} % inverse of a path
 \newcommand{\classof}{\constructor{class}} % class construcor
@@
 % Displayed algebras
-\newcommand{\polydact}[2]{\overline{#1} \> #2}
-\newcommand{\epdact}[2]{\overline{#1} \> #2}
-\newcommand{\polydmap}[2]{\overline{#1} \> #2}
+\newcommand{\polydact}[2]{\overline{#1} \> #2} % dependent action of polynomials on families
+\newcommand{\epdact}[2]{\overline{#1} \> #2} % dependent action of endpoints
+\newcommand{\polydmap}[2]{\overline{#1} \> #2} % action of polynomials on dependent maps
+\newcommand{\total}[1]{\int #1} % total algebra of displayed algebra
+\newcommand{\proj}[1]{\pi_1^{#1}} % projection homomorphism
+\newcommand{\Ppl}[1]{\pi_1^{#1}} % dependent second projection, poly_pr2
+\newcommand{\Ppr}[1]{\pi_2^{#1}} % dependent second projection, poly_pr2
+\newcommand{\Epl}{\function{epr_1}} % first projection of endpoin action
+\newcommand{\Epr}{\function{epr_2}} % first projection of endpoin action
+
+% Examples of HITs
+\newcommand{\Circ}{S^1} % circle
+\newcommand{\base}{\constructor{base}} % base point of circle
+\newcommand{\loopS}{\constructor{loop}} % base point of circle
+
+\newcommand{\remove}{}
 
@@
 \label{intro}
+Homotopy type theory (HoTT) is a form of intensional type theory. 
+It has semantics in the simplicial sets model \cite{simpset}, and types represent spaces, terms represent points, and equalities represent paths.
+Furthermore, equality is proof relevant and we frequently talk about homotopies: paths between paths.
+
+One of the main features of HoTT, is higher inductive types (HITs) \cite{hottbook}.
+These are types generated by constructors for their points, paths, homotopies, and so on.
+HITs have been used in numerous applications among which are homotopical patch theory \cite{AngiuliMLH16}.
+synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.
+
+To get a feeling for what HITs are, let us look a some examples before looking at them more formally.
+
+\lstset{language=Coq}
+\setlength{\tabcolsep}{30pt}	
+\begin{tabular}{ c c c }
+
+\begin{lstlisting}[mathescape=true]
+Inductive $\Circ$ :=
+| $\base$ : $\Circ$
+| $\loopS$ : $\base = \base$
+\end{lstlisting}
+&
+\begin{lstlisting}[mathescape=true]
+Inductive $\trunct{A}$ :=
+| $\truncel{\cdot}$ : $A \rightarrow \trunct{A}$
+| $p$ : $\deprod{x, y}{\trunct{A}}{x = y}$
+\end{lstlisting}
+&
+\begin{lstlisting}[mathescape=true]
+Inductive $H$ :=
+| $c$ : $H \times H \rightarrow H$
+| $p$ : $\deprod{x, y}{H}{c(x,y) = c(y,x)}$
+\end{lstlisting}
+\end{tabular}
+
+The first one, $\Circ$, is the \emph{circle}.
+It has a point, $\base$, and a path $\loopS : \base = \base$.
+Since neither the point nor path constructors uses arguments from $\Circ$, this HIT is \emph{nonrecursive}.
+The second, $\trunct{A}$, is the \emph{propositional truncation} of $A$.
+This type is $A$ with all its points identified.
+Note that the path constructor $p$ uses arguments from $\trunct{A}$, and thus this HIT is called \emph{recursive}.
+
+The last example, CHANGE TO INTEGERS MODULO 2 (with recursive path constr)
+
+Several schemes of HITs have already been developed.
+Awodey \etal \ showed that the rules of inductive types \cite{dybjer1994inductive} in HoTT are equivalent to being a homotopy initial algebra \cite{AwodeyGS12}.
+They extended this result to a class of HITs called \emph{W-suspensions} \cite{Sojakova15}.
+Another scheme, quotient inductive-inductive types, was defined semantically by Altenkirch \etal \ and they prove initial algebra semantics \cite{AltenkirchCDKF18}.
+Assuming UIP, Kaposi \etal \ constructed finitary QIITs as the syntax of a domain specific type theory \cite{KaposiKA19}, and they extended this scheme to higher inductive-inductive types \cite{KaposiK18}.
+Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}.
+Dybjer and Moenclaey defined a scheme allowing constructors for points, paths, and homotopies. and give its semantics in the groupoid model  \cite{DybjerM18,HofmannS94}.
+Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types and proved canonicity \cite{AngiuliHW17,CavalloH19}.
+
+Furthermore, the semantics of HITs also has been studied.
+Coquand \etal \ provide the semantics of various higher inductive types, such as spheres, the torus, the truncation, and the pushout, in cubical type theory \cite{BezemCH13,CohenCHM16,CoquandHM18}.
+On the other hand, Lumsdaine and Shulman also study the semantics of higher inductive types, but they use a semantic scheme (cell monads with parameters) and proof existence in sufficiently nice Quillen model categories \cite{lumsdaine2017semantics}.
+Some recursive higher inductive types can be constructed from nonrecursive HITs.
+Both Kraus and Van Doorn show that the propositional truncation can be constructed from non-recursive HITs \cite{Kraus16,Doorn16} and Rijke shows that every truncation can be constructed via non-recursive HITs \cite{rijke2017join}.
+
+In this paper, we show that all finitary set-truncated HITs can be constructed with quotients and propositional truncations. 
+This briefly means that all higher inductive types exist if a small number of simple ones exist.
+Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
+The latter result is similar to work by Kraus and Von Raumer \cite{KrausRaumer}.
+Note that from this construction we can conclude that finitary set-truncated HITs can be constructed from non-recursive HITs.
+Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction.
+
+The main idea of the proof is to take advantage that the quotient is an adjoint functor \cite{RijkeS15} from setoids to sets.
+To relate this to HITs, we first define schemes, which are an internalized version of the schema by Basold \etal \ \cite{BasoldGW17}, and categories of algebras on them.
+Then we lift the quotient adjunction to an adjunction from algebras in setoids and algebras in sets.
+Since initiality implies induction, it suffices to construct the initial setoid algebra for which we adapt the construction by Dybjer and Moenclaey \cite{moeneclaey2016schema,DybjerM18}.
+
+All definitions and proofs in his paper are formalized over the UniMath library \cite{UniMath}.
+The formalization is 4166 lines of code and it can be found on \url{https://github.com/nmvdw/SetHITs}.
+
+We start in \Cref{sec:prelim} by recalling some definitions from HoTT and category theory required for the rest of the paper.
+In \Cref{sec:signature}, we define signatures for higher inductive types and give a couple of examples.
+Next we define algebras in both the categories of sets and setoids for such signatures in \Cref{sec:algebras}.
+We define the induction principle of HITs via displayed algebras in \Cref{sec:induction} and we show that initial objects satisfy this principle.
+\Cref{sec:construction} is the core of this paper and there we construct an adjunction between algebras in sets and setoids, which we use to construct the initial algebra in sets via the initial algebra in setoids.
+We study the consequences of this construction in \Cref{sec:consequences} and in \Cref{sec:conclusion}, we conclude and discuss further work.
 
@@
 \subsection{Displayed Algebras}
+\label{ref:induction}
 A displayed algebra is the input of the elimination rule.
@@
 \subsection{Obtaining Induction from Initiality}
-Now suppose that we have some displayed algebra.
-Our goal is to construct an algebra whose objects are dependent pairs.
-
-Give the carrier and operation in plain text
+The goal of this section is to obtain the induction principle from initiality.
+This way it suffices construct an initial object of the signature to obtain a HIT.
+To this end, we first define the total algebra $\total{Y}$ of a displayed $Y$ on $X$ together a projection $\proj{Y}$ to $X$.
+Then we show that induction can be obtained by finding a section of the projection.
+Since this is always possible if $X$ is initial, we conclude by saying that initial objects satisfy the induction principle.
+
+We define the carrier of $\total{Y}$ by the dependent sum $\desum{x}{X}{Y \> x}$ and for brevity, we denote this by $\total{Y}$.
+To show this is an algebra, we first need to define a map $c_{\total{Y}} : \semP{\pointc{\Sigma}} \> (\total{Y}) \rightarrow \total{Y}$.
+The main idea is that we use the algebra map of $X$ for the first component and the algebra map of $Y$ for the second one.
+We introduce an intermediate definition, which allows us to access the right data.
+
+\begin{definition}
+Let $P$ be a polynomial and let $Y$ be a family of sets on $X$.
+We define a map
+\[
+\Ppl{P} : \semP{P} \> (\desum{x}{X}{Y \> x} \rightarrow X)
+\quad \quad
+\Ppl{P} \> x = \semP{\pointc{\Sigma}} \> \prl \> x
+\]
+We also define a map $\Ppr{P} : \deprod{x}{\semP{P} \> (\desum{x}{X}{Y \> x})}{\polydact{P}{Y} \> (\Ppl{P} \> x)}$ by induction on $P$.
+\begin{itemize}
+	\item $\Ppr{\C \> T} \> x  = x$;
+	\item $\Ppr{\I} \> x = \prr \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inl x) = \Ppr{P} \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inr x) = \Ppr{Q} \> x$;
+	\item $\Ppr{\prodP{P}{Q}} \> x = (\Ppr{P} \> x , \Ppr{Q} \> (\prr \> x))$.
+\end{itemize}
+\end{definition}
+
+Now let $z : \semP{\pointc{\Sigma}} \> (\total{Y})$.
+The first coordinate of $c_{\total{Y}} \> z$ is defined to be $\constrA{X}(\Ppl{P} \> x)$.
+The second coordinate of $c_{\total{Y}} \> z$ is defined by $c_Y \> (\Ppl{P} \> x) \> (\Ppr{P} \> x)$.
+The main challenge lies within proving the equations.
 
 \begin{lemma}
-pr1 endpoint
+For every endpoint $e : \ep{\pointc{\Sigma}}{P}{Q}$, we have
+\[
+\Epl : \semE{e} \> X \> (\Ppl{P} \> x) = \Ppl{Q}(\semE{e} \> (\total{Y}) \> x) 
+\]
+\[
+\Epr : \epdact{e}{c_Y} \> (\Ppr{P} \> x) = \transport{\polydact{Q}{Y}}{\invP{\Epl}} \> (\Ppr{Q} \> (\semE{e} \> (\total{Y}) \> x))
+\]
 \end{lemma}
 
-\begin{lemma}
-pr2 endpoint
-\end{lemma}
-
-All in all, we get the following construction.
-
-\begin{theorem}
-Total algebra and projection
-\end{theorem}
+All in all, given a displayed algebra $Y$ on some algebra $X$, we get the \emph{total algebra} $\total{Y}$.
+We also define an algebra homomorphism $\proj{Y} : \total{Y} \rightarrow X$, which sends $z$ to its first projection $\prl \> z$.
+The reason why we care about this construction, is the following proposition.
 
 \begin{proposition}
-Map to total algebra which projects into identity is section.
+From an algebra homomorphism $f : X \rightarrow \total{Y}$ such that $\comp{f}{\proj{Y}}$ is the identity, we obtain a displayed algebra map from $X$ to $Y$.
 \end{proposition}
 
-Hence, to construct a HIT, it suffices to construct an initial object in the category of algebras.
+Now suppose $X$ is an initial object in the category of algebras.
+Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because of initiality as well.
+Hence, we conclude
 
 \begin{corollary}
-
+If $X$ is an initial object in the category of algebras on $\Sigma$, then $X$ is a HIT for $\Sigma$.
 \end{corollary}
@@
 \section{Constructing the Initial Algebra}
+\label{sec:construction}
 
@@
 \section{Consequences}
+\label{sec:consequences}
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
+
+\cite{AhrensKS15}
+\cite{AhrensL19}
+\cite{mac2013categories}
 
 \begin{thebibliography}{10}\label{bibliography}
-\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
-    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.
-
-\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
-  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
-  Providence, R.I., 1961.
-
-\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
-  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
-  Theoretical Computer Science {\bf 1} (1995), URL:
-  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
-  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.
-
-\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
-    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
-  preprint 93/52.
-
-\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
-  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
-  London, New York (1198), 565pp. With associated web site\\  
-  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
-  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.
-
-\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
-  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.
-
-\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
-  Press, Princeton, N.J., 1946.
-
+
+	\bibitem{AltenkirchCDKF18}
+	Thorsten Altenkirch, Paolo Capriotti, Gabe Dijkstra, Nicolai Kraus, and
+	Fredrik~Nordvall Forsberg, \emph{{Quotient Inductive-Inductive Types}},
+	Foundations of Software Science and Computation Structures - 21st
+	International Conference, {FOSSACS} 2018, Held as Part of the European Joint
+	Conferences on Theory and Practice of Software, {ETAPS} 2018, Thessaloniki,
+	Greece, April 14-20, 2018, Proceedings, 2018, pp.~293--310.
+
+	\bibitem{AltenkirchDK17}
+	Thorsten Altenkirch, Nils~Anders Danielsson, and Nicolai Kraus,
+	\emph{{Partiality, Revisited - The Partiality Monad as a Quotient
+			Inductive-Inductive Type}}, Foundations of Software Science and Computation
+	Structures - 20th International Conference, {FOSSACS} 2017, Held as Part of
+	the European Joint Conferences on Theory and Practice of Software, {ETAPS}
+	2017, Uppsala, Sweden, April 22-29, 2017, Proceedings, 2017, pp.~534--549.
+
+	\bibitem{ahrens2019bicategories}
+	Benedikt Ahrens, Dan Frumin, Marco Maggesi, and Niels van~der Weide,
+	\emph{{Bicategories in Univalent Foundations}}, arXiv preprint
+	arXiv:1903.01152 (2019).
+
+	\bibitem{AwodeyGS12}
+	Steven Awodey, Nicola Gambino, and Kristina Sojakova, \emph{{Inductive Types in
+			Homotopy Type Theory}}, Proceedings of the 27th Annual {IEEE} Symposium on
+	Logic in Computer Science, {LICS} 2012, Dubrovnik, Croatia, June 25-28, 2012,
+	2012, pp.~95--104.
+
+	\bibitem{AngiuliHW17}
+	Carlo Angiuli, Robert Harper, and Todd Wilson, \emph{{Computational
+			Higher-Dimensional Type Theory}}, Proceedings of the 44th {ACM} {SIGPLAN}
+	Symposium on Principles of Programming Languages, {POPL} 2017, Paris, France,
+	January 18-20, 2017, 2017, pp.~680--693.
+
+	\bibitem{AltenkirchK16}
+	Thorsten Altenkirch and Ambrus Kaposi, \emph{{Type Theory in Type Theory using
+			Quotient Inductive Types}}, Proceedings of the 43rd Annual {ACM}
+	{SIGPLAN-SIGACT} Symposium on Principles of Programming Languages, {POPL}
+	2016, St. Petersburg, FL, USA, January 20 - 22, 2016, 2016, pp.~18--29.
+
+	\bibitem{AhrensKS15}
+	Benedikt Ahrens, Krzysztof Kapulkin, and Michael Shulman, \emph{{Univalent
+			Categories and the Rezk Completion}}, Mathematical Structures in Computer
+	Science \textbf{25} (2015), no.~5, 1010--1039.
+
+	\bibitem{AhrensL19}
+	Benedikt Ahrens and Peter~LeFanu Lumsdaine, \emph{{Displayed Categories}},
+	Logical Methods in Computer Science \textbf{15} (2019), no.~1.
+
+	\bibitem{AngiuliMLH16}
+	Carlo Angiuli, Edward Morehouse, Daniel~R. Licata, and Robert Harper,
+	\emph{{Homotopical Patch Theory}}, J. Funct. Program. \textbf{26} (2016),
+	e18.
+
+	\bibitem{BezemCH13}
+	Marc Bezem, Thierry Coquand, and Simon Huber, \emph{{A Model of Type Theory in
+			Cubical Sets}}, 19th International Conference on Types for Proofs and
+	Programs, {TYPES} 2013, April 22-26, 2013, Toulouse, France, 2013,
+	pp.~107--128.
+
+	\bibitem{BasoldGW17}
+	Henning Basold, Herman Geuvers, and Niels van~der Weide, \emph{{Higher
+			Inductive Types in Programming}}, J. {UCS} \textbf{23} (2017), no.~1, 63--88.
+
+	\bibitem{CohenCHM16}
+	Cyril Cohen, Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg,
+	\emph{{Cubical Type Theory: A Constructive Interpretation of the Univalence
+			Axiom}}, CoRR \textbf{abs/1611.02108} (2016).
+
+	\bibitem{CavalloH19}
+	Evan Cavallo and Robert Harper, \emph{{Higher Inductive Types in Cubical
+			Computational Type Theory}}, {PACMPL} \textbf{3} (2019), no.~{POPL},
+	1:1--1:27.
+
+	\bibitem{CoquandHM18}
+	Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg, \emph{{On Higher
+			Inductive Types in Cubical Type Theory}}, Proceedings of the 33rd Annual
+	{ACM/IEEE} Symposium on Logic in Computer Science, {LICS} 2018, Oxford, UK,
+	July 09-12, 2018, 2018, pp.~255--264.
+
+	\bibitem{capriotti2017univalent}
+	Paolo Capriotti and Nicolai Kraus, \emph{{Univalent Higher Categories via
+			Complete Semi-Segal Types}}, Proceedings of the ACM on Programming Languages
+	\textbf{2} (2017), no.~POPL, 44.
+
+	\bibitem{DybjerM18}
+	Peter Dybjer and Hugo Moeneclaey, \emph{{Finitary Higher Inductive Types in the
+			Groupoid Model}}, Electr. Notes Theor. Comput. Sci. \textbf{336} (2018),
+	119--134.
+
+	\bibitem{dybjer1994inductive}
+	Peter Dybjer, \emph{{Inductive Families}}, Formal aspects of computing
+	\textbf{6} (1994), no.~4, 440--465.
+
+	\bibitem{FruminGGW18}
+	Dan Frumin, Herman Geuvers, L{\'{e}}on Gondelman, and Niels van~der Weide,
+	\emph{{Finite Sets in Homotopy Type Theory}}, Proceedings of the 7th {ACM}
+	{SIGPLAN} International Conference on Certified Programs and Proofs, {CPP}
+	2018, Los Angeles, CA, USA, January 8-9, 2018, 2018, pp.~201--214.
+
+	\bibitem{HofmannS94}
+	Martin Hofmann and Thomas Streicher, \emph{{The Groupoid Model Refutes
+			Uniqueness of Identity Proofs}}, Proceedings of the Ninth Annual Symposium on
+	Logic in Computer Science {(LICS} '94), Paris, France, July 4-7, 1994, 1994,
+	pp.~208--212.
+
+	\bibitem{KaposiK18}
+	Ambrus Kaposi and Andr{\'{a}}s Kov{\'{a}}cs, \emph{{A Syntax for Higher
+			Inductive-Inductive Types}}, 3rd International Conference on Formal
+	Structures for Computation and Deduction, {FSCD} 2018, July 9-12, 2018,
+	Oxford, {UK}, 2018, pp.~20:1--20:18.
+
+	\bibitem{KaposiKA19}
+	Ambrus Kaposi, Andr{\'{a}}s Kov{\'{a}}cs, and Thorsten Altenkirch,
+	\emph{{Constructing Quotient Inductive-Inductive Types}}, {PACMPL} \textbf{3}
+	(2019), no.~{POPL}, 2:1--2:24.
+
+	\bibitem{simpset}
+	Chris Kapulkin and Peter~LeFanu Lumsdaine, \emph{{The Simplicial Model of
+			Univalent Foundations (after Voevodsky)}}, 2012.
+
+	\bibitem{Kraus16}
+	Nicolai Kraus, \emph{{Constructions with Non-Recursive Higher Inductive
+			Types}}, Proceedings of the 31st Annual {ACM/IEEE} Symposium on Logic in
+	Computer Science, {LICS} '16, New York, NY, USA, July 5-8, 2016, 2016,
+	pp.~595--604.
+
+	\bibitem{KrausRaumer}
+	Nicolai Kraus and Jakob von Raumer, \emph{{Path Spaces of Higher Inductive
+			Types in Homotopy Type Theory}}, CoRR \textbf{abs/1901.06022} (2019).
+
+	\bibitem{LicataF14}
+	Daniel~R. Licata and Eric Finster, \emph{{Eilenberg-MacLane Spaces in Homotopy
+			Type Theory}}, Joint Meeting of the Twenty-Third {EACSL} Annual Conference on
+	Computer Science Logic {(CSL)} and the Twenty-Ninth Annual {ACM/IEEE}
+	Symposium on Logic in Computer Science (LICS), {CSL-LICS} '14, Vienna,
+	Austria, July 14 - 18, 2014, 2014, pp.~66:1--66:9.
+
+	\bibitem{LicataS13}
+	Daniel~R. Licata and Michael Shulman, \emph{{Calculating the Fundamental Group
+			of the Circle in Homotopy Type Theory}}, 28th Annual {ACM/IEEE} Symposium on
+	Logic in Computer Science, {LICS} 2013, New Orleans, LA, USA, June 25-28,
+	2013, 2013, pp.~223--232.
+
+	\bibitem{lumsdaine2017semantics}
+	Peter~LeFanu Lumsdaine and Mike Shulman, \emph{{Semantics of Higher Inductive
+			Types}}, arXiv preprint arXiv:1705.07088 (2017).
+
+	\bibitem{mac2013categories}
+	Saunders Mac~Lane, \emph{{Categories for the Working Mathematician}}, vol.~5,
+	Springer Science \& Business Media, 2013.
+
+	\bibitem{moeneclaey2016schema}
+	H.~Moeneclaey.
+	\newblock {A Schema for Higher Inductive Types of Level One and Its
+		Interpretation}.
+	\newblock {\em Internship report, supervised by Peter Dybjer, ENS
+		Paris-Saclay}, 2016.
+
+	\bibitem{rijke2017join}
+	Egbert Rijke, \emph{{The Join Construction}}, arXiv preprint arXiv:1701.07538
+	(2017).
+
+	\bibitem{RijkeS15}
+	Egbert Rijke and Bas Spitters, \emph{{Sets in Homotopy Type Theory}},
+	Mathematical Structures in Computer Science \textbf{25} (2015), no.~5,
+	1172--1202.
+
+	\bibitem{Sojakova15}
+	Kristina Sojakova, \emph{{Higher Inductive Types as Homotopy-Initial
+			Algebras}}, Proceedings of the 42nd Annual {ACM} {SIGPLAN-SIGACT} Symposium
+	on Principles of Programming Languages, {POPL} 2015, Mumbai, India, January
+	15-17, 2015, 2015, pp.~31--42.
+
+	\bibitem{hottbook}
+	{The Univalent Foundations Program}, \emph{{Homotopy Type Theory: Univalent
+			Foundations of Mathematics}}, \url{https://homotopytypetheory.org/book},
+	Institute for Advanced Study, 2013.
+
+	\bibitem{UniMath}
+	Vladimir Voevodsky, Benedikt Ahrens, Daniel Grayson, et~al., \emph{{UniMath ---
+			a computer-checked library of univalent mathematics}}, {available} at
+	\url{https://github.com/UniMath/UniMath}.
+
+	\bibitem{Doorn16}
+	Floris van Doorn, \emph{{Constructing the Propositional Truncation using
+			Non-Recursive HITs}}, Proceedings of the 5th {ACM} {SIGPLAN} Conference on
+	Certified Programs and Proofs, Saint Petersburg, FL, USA, January 20-22,
+	2016, 2016, pp.~122--129.	
 \end{thebibliography}
 
+%\begin{thebibliography}{10}\label{bibliography}
+%\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
+%    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.
+
+%\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
+%  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
+%  Providence, R.I., 1961.
+
+%\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
+%  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
+%  Theoretical Computer Science {\bf 1} (1995), URL:
+%  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
+%  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.
+
+%\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
+%    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
+%  preprint 93/52.
+
+%\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
+%  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
+%  London, New York (1198), 565pp. With associated web site\\  
+%  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
+%  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.
+
+%\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
+%  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.
+
+%\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
+%  Press, Princeton, N.J., 1946.
+
+%\end{thebibliography}
 \end{document}

### 2019-03-30 paper/paper.tex
Added example of integers modulo 2, further work on text

@@
 
+\newtheorem{notation}[thm]{Notation}
+
 \newcommand{\ie}{\emph{i.e.,} }
@@
 % HoTT
-\newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
-\newcommand{\desum}[3]{\sum_{#1 : #2} #3} % dependent sum
+\newcommand{\deprod}[3]{\prod(#1 : #2), #3} % dependent product
+%\newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
+\newcommand{\desum}[3]{\sum(#1 : #2), #3} % dependent sum
+%\newcommand{\desum}[3]{\sum_{#1 : #2} #3} % dependent sum
 \newcommand{\hset}{\type{hSet}} % sets
@@
 \newcommand{\1}{\textbf{1}} % unit type
+\newcommand{\TT}{\constructor{tt}} % element of unit type
 \newcommand{\inl}{\term{inl}} %left inclusion
@@
 \newcommand{\pairTm}[2]{(#1 , #2)} % pairing
-\newcommand{\weq}{\simeq} % weak equivalence
+\newcommand{\weq}{\simeq} % equivalence
 \newcommand{\setquot}[2]{#1 / #2} % quotient type
-\newcommand{\transport}[2]{\function{transport}^{#1} #2} % transport
+\newcommand{\transport}[2]{\function{transport}^{#1} \> #2} % transport
 \newcommand{\invP}[1]{(#1)^{-1}} % inverse of a path
@@
 \newcommand{\depeq}[3]{#2 =_{#1} #3} % dependent equality type
+\newcommand{\Def}{:=} % symbol for definition
 
@@
 \newcommand{\idm}[1]{\morphism{id}_{#1}} % identity morphism
-\newcommand{\compm}[2]{#1 \circ #2} % composition of morphisms
+\newcommand{\compm}[2]{#2 \circ #1} % composition of morphisms
 \newcommand{\iso}[2]{#1 \cong #2} % isomorphisms
@@
 \newcommand{\Cf}[1]{\functortxt{C}_{#1}} % constant functor
-\newcommand{\compf}[2]{#1 \circ #2} % composition of functors
+\newcommand{\compf}[2]{#2 \circ #1} % composition of functors
 \newcommand{\prodf}[2]{#1 \times #2} % product of functors
@@
 \newcommand{\idt}[1]{\nattranstxt{id}} % identity transformation
-\newcommand{\compt}[2]{#1 \circ #2} % composition of natural transformations
-\newcommand{\lwhisker}[2]{#1 \vartriangleleft #2} % left whiskering of transformations
+\newcommand{\compt}[2]{#2 \circ #1} % composition of natural transformations
+\newcommand{\lwhisker}[2]{#2 \vartriangleright #1} % whiskering of transformations
 \newcommand{\inlt}{\nattranstxt{inl}} %left inclusion of transformations
@@
 \newcommand{\idtoiso}{\function{idtoiso}} % identity to iso
+\newcommand{\falg}[1]{\category{FAlg}(#1)} % category of algebras on a functor
 
@@
 \newcommand{\prodR}[2]{#1 \times #2} % product of equivalence relations
-\newcommand{\polyR}[2]{#1 \> #2} % action of polynomials on equivalence relations
+\newcommand{\polyR}[2]{\widehat{#1} \> #2} % action of polynomials on equivalence relations
 
@@
 
-\newcommand{\comm}{\function{comm}}
-\newcommand{\trunc}{\function{trunc}}
+\newcommand{\comm}{\function{comm}} % remove
+\newcommand{\modsig}{\function{mod}} % signature for integers mod 2
+\newcommand{\trunc}{\function{trunc}} % signature for truncation
+\newcommand{\sig}{\mathcal{S}} % variable for signatures
 
@@
 \newcommand{\prealg}[1]{\category{PreAlg}_{\hset}(#1)} % category of prealgebras
-\newcommand{\forget}[1]{F_{#1}} % forgetful functor
+\newcommand{\forget}[1]{\mathcal{F}_{#1}} % forgetful functor
 \newcommand{\semE}[1]{\llbracket #1 \rrbracket} % semantics of endpoints
@@
 \newcommand{\Ppr}[1]{\pi_2^{#1}} % dependent second projection, poly_pr2
-\newcommand{\Epl}{\function{epr_1}} % first projection of endpoin action
-\newcommand{\Epr}{\function{epr_2}} % first projection of endpoin action
+\newcommand{\Epl}{\function{epr_1}} % first projection of endpoint action
+\newcommand{\Epr}{\function{epr_2}} % first projection of endpoint action
+\newcommand{\constdisp}{\function{const}} % constant displayed algebra
 
@@
 \newcommand{\loopS}{\constructor{loop}} % base point of circle
+\newcommand{\modZ}{\mathbb{Z}_2} % integers modulo 2
+\newcommand{\ZZ}{\constructor{Z}} % zero
+\newcommand{\SZ}{\constructor{S}} % zero
+\newcommand{\modP}{\constructor{mod}} % n = n + 2
+\newcommand{\HIT}{\function{HIT}} % the HIT of a signature
 
@@
 
-\def\lastname{Please list Your Lastname Here}
+\def\lastname{Van der Weide}
 \begin{document}
 \begin{frontmatter}
-  \title{An Example Paper} \author{My
-    Name\thanksref{ALL}\thanksref{myemail}}
-  \address{My Department\\ My University\\
-    My City, My Country} \author{My Co-author\thanksref{coemail}}
+  \title{The Construction of Set-Truncated Higher Inductive Types} \author{Niels van der Weide
+    \thanksref{ALL}\thanksref{myemail}}
+  \address{Institute for Computation and Information Sciences\\ Radboud Universiteit\\
+    Nijmegen, The Netherlands} \author{My Co-author\thanksref{coemail}}
   \address{My Co-author's Department\\My Co-author's University\\
-    My Co-author's City, My Co-author's Country} \thanks[ALL]{Thanks
-    to everyone who should be thanked} \thanks[myemail]{Email:
-    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
-        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
+    My Co-author's City, My Co-author's Country} \thanks[ALL]{We would like to thank Dan Frumin and Andrej Bauer for inspiring discussions.
+Work on this article was supported by a grant from the \href{https://eutypes.cs.ru.nl/}{COST Action EUTypes CA15123}.} \thanks[myemail]{Email:
+    \href{mailto:nweide@cs.ru.nl} {\texttt{\normalshape
+        nweide@cs.ru.nl}}} \thanks[coemail]{Email:
     \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
@@
 \begin{abstract} 
-  This is a short example to show the basics of using the ENTCS style
-  macro files.  Ample examples of how files should look may be found
-  among the published volumes of the series at the ENTCS Home Page
-  \texttt{http://www.elsevier.com/locate/entcs}.
+  We construct finitary set-truncated higher inductive types (HITs) using quotients and the propositional truncation.
+  Using a modification of the schema by Basold \etal, we define a notion of signatures and univalent categories of algebras in both sets and setoids.
+  To interpret HITs, we use initial algebra semantics for which we show that the initiality implies induction.
+  The desired algebra is obtained by lifting the quotient adjunction to the level of algebras and adapting Dybjer's and Moenclaey's interpretation of HITs in setoids.
+  From this construction, we conclude that the equality types of HITs are freely generated and that HITs are unique.
+  The results are formalized in the UniMath library.
 \end{abstract}
 \begin{keyword}
-  Please list keywords from your paper here, separated by commas.
+higher inductive types, homotopy type theory, category theory, setoids, intuitionistic type theory, Coq
 \end{keyword}
@@
 \begin{lstlisting}[mathescape=true]
-Inductive $H$ :=
-| $c$ : $H \times H \rightarrow H$
-| $p$ : $\deprod{x, y}{H}{c(x,y) = c(y,x)}$
+Inductive $\modZ$ :=
+| $\ZZ$ : $\modZ \rightarrow \modZ$
+| $\SZ$ : $\modZ \rightarrow \modZ$
+| $\modP$ : $\deprod{x}{\modZ}{\SZ(\SZ \> x) = x}$
 \end{lstlisting}
@@
 Note that the path constructor $p$ uses arguments from $\trunct{A}$, and thus this HIT is called \emph{recursive}.
-
-The last example, CHANGE TO INTEGERS MODULO 2 (with recursive path constr)
-
-Several schemes of HITs have already been developed.
+The last one $, \modZ$ is the \emph{integers modulo 2} and note that both the point constructor $\SZ$ and path constructor $\modP$ are recursive.
+
+HITs have also been studied more formally and several schemes have already been developed.
 Awodey \etal \ showed that the rules of inductive types \cite{dybjer1994inductive} in HoTT are equivalent to being a homotopy initial algebra \cite{AwodeyGS12}.
@@
 \label{sec:prelim}
-We start by recalling some definitions from homotopy type theory (HoTT) and fixing the notation.
-The first definition we need, is the \emph{dependent equality type}.
+We start by recalling some definitions and notations from homotopy type theory and category theory \cite{mac2013categories,hottbook}.
+The first notion we need, is the \emph{dependent equality type}.
 
@@
 \label{def:depeq}
-Given a type $X$, a type family $Y$ on $X$, and a path $p : x = y$, then we have a map
+Given a type $X$, inhabitants $x, y : X$, a type family $Y$ on $X$, and a path $p : x = y$, we define
 \[
@@
 \]
-Given a path $p : x = y$ and inhabitants $z_1 : Y \> x$ and $z_2 : Y \> y$, we write $\depeq{p}{z_1}{z_2}$ for $\transport{Y}{p} \> z_1 = z_2$.
+Given a path $p : x = y$ and inhabitants $z_1 : Y \> x$ and $z_2 : Y \> y$, we write $\depeq{p}{z_1}{z_2}$ for $\transport{Y}{p} \ z_1 = z_2$.
 \end{definition}
@@
 One of the core features of HoTT, is that equality is proof relevant.
-This means that not every inhabitant of $x = y$ is necessarily equal.
-There might be some types for which this is the case though, and we call such types \emph{sets}.
+This means that not all inhabitants of $x = y$ are necessarily equal.
+Some types might actually have proof irrelevant equality, and we call such types \emph{sets}.
 More precisely, we define
@@
 
-To construct higher inductive types, we make use of only two.
-These are the \emph{quotient type} and the \emph{propositional truncation}.
-For their elimination and computation rules, we refer the reader to the literature.
+Our goal is to construct all higher inductive types from two specific ones, namely the \emph{quotient type} and the \emph{propositional truncation}.
+We only give their introduction rules here, and for their elimination and computation rules, we refer the reader to the literature \cite{hottbook}.
 
@@
 Let $X$ be a type and let $R$ be an equivalence relation on $X$.
-The \emph{quotient type} $\setquot{X}{R}$ is the higher inductive type generated by the following rules
+The \emph{quotient type} $\setquot{X}{R}$ is the higher inductive type generated by
 \begin{center}
@@
 Let $X$ be a type.
-The \emph{propositional truncation} $\trunct{X}$ is the higher inductive type generated by the following rules
+The \emph{propositional truncation} $\trunct{X}$ is the higher inductive type generated by
 \begin{center}
@@
 
-Next we briefly discuss category theory in univalent foundations.
+Next we briefly discuss category theory in univalent foundations \cite{AhrensKS15,hottbook}.
 We start by recalling the definition of categories.
@@
 While the objects can be any type, the arrows have to form a set.
-If equality was proof relevant, then this would give the structure of a higher category instead of an ordinary one.
+Proof relevant equality on arrows would induce the structure of a higher category instead of an ordinary one.
 This leads to the following definition.
@@
 
-We define isomorphisms in the usual way and we denote the type of isomorphisms from $X$ to $Y$ by $\iso{X}{Y}$.
-... is the notion of \emph{univalent categories}.
+We define isomorphisms in categories the usual way and we denote the type of isomorphisms from $X$ to $Y$ by $\iso{X}{Y}$.
+In the remainder, we also make use of \emph{univalent categories}.
 These are categories in which equality on objects is equivalent to isomorphisms between them.
+For the definition of equivalence of equivalences, we refer the reader to the literature \cite{hottbook}.
 More precisely, we define them as follows.
@@
 Note that for all objects $X$ and $Y$ we have a map $\idtoiso_{X,Y} : X = Y \rightarrow \iso{X}{Y}$ sending the reflexivity path to the identity isomorphism.
-Then we say $\mathcal{C}$ is \emph{univalent} if $\idtoiso_{X,Y}$ is a weak equivalence for each $X$ and $Y$.
+Then we say $\mathcal{C}$ is \emph{univalent} if $\idtoiso_{X,Y}$ is an equivalence for each $X$ and $Y$.
 \end{definition}
@@
 The primary example of a univalent category is the category $\hset$ of sets and functions between them.
-Its univalence follows from the univalence axiom.
 Another example of a univalent category which we use frequently, is the category of \emph{setoids}.
@@
 When it is clear from the context, we write $\equiv$ for the relation.
-We finish this section by giving some operations of functor and natural transformations.
-For categories $\mathcal{C}$ and $\mathcal{D}$, we write $\functor{\mathcal{C}}{\mathcal{D}}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$.
-For functor $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we write $\nattrans{F}{G}$ for the type of natural transformations from $\mathcal{F}$ to $\mathcal{G}$.
-
-\begin{lemma}
+We finish this section by giving some operations of functor and natural transformations, which we need later.
+Functors and transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and natural transformations from $\mathcal{F}$ to $\mathcal{G}$ respectively.
+
+\begin{notation}
 \label{def:functor}
@@
 \end{itemize}
-\end{lemma}
-
-\begin{lemma}
+\end{notation}
+
+\begin{notation}
 \label{def:nattrans}
@@
 \begin{itemize}
-	\item Suppose, $F, G : \functor{\mathcal{C}}{\mathcal{D}}$
+	\item Given $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have
 	\[
@@
 \end{itemize}
-\end{lemma}
+\end{notation}
 
@@
 Before we study the construction of set truncated HITs, we first give a precise definition of those.
-We do this by internalizing a scheme, so, more concretely, we define a type of signatures.
+We do this by internalizing the scheme by Basold \etal \ \cite{BasoldGW17} via a type of signatures.
 In this section, we give the definition of signatures, and then in the upcoming sections, we define the notion of HITs for a signature.
@@
 \label{def:poly}
-We define the type $\mathcal{\poly}$ of \emph{polynomial functors} inductively by the following rules
+The type $\mathcal{\poly}$ of \emph{codes of polynomials} is inductively generated by the following constructors.
 \begin{center}
@@
 
-Next we describe the possible path constructors.
-Note that these depend on the point constructor.
-Furthermore, the path constructors are universally quantified equations of which the arguments depend polynomially on the type being defined.
-Again we use an inductive definition to describe all possibilities.
+In the next section, we show that each code $P : \poly$ gives rise to a functor $\semP{P} : \functor{\hset}{\hset}$.
+A higher inductive type $H$ should have a constructor $\semP{P} \> H \rightarrow H$, which represents the introduction rule for points.
+
+HITs also have an introduction rule for paths, and for those, we need to give the possible endpoints of paths.
+Note that in the equations the point constructor can be used, and thus the type of endpoint must depend on the data of the point constructor.
+Since each equation is universally quantified, we also have to indicate the source of the arguments, which again depends polynomially on the HIT being defined.
+In addition, we allow each equation to have a target also depending polynomially on the HIT.
+We define the type of endpoints again as an inductive type.
 
@@
 \label{def:endpoint}
-Given polynomials, $A, P, Q : \poly$, we define the type $\ep{A}{P}{Q}$ of \emph{endpoints} inductively by the following rules
+Given polynomials, $A, P, Q : \poly$, the type $\ep{A}{P}{Q}$ of \emph{endpoints} is inductively generated by the following constructors.
 \begin{center}
@@
 
-Next we put it all together.
+The polynomial $A$ represents the point constructor and that explains the endpoint $\constr$.
+The polynomials $P$ and $Q$ represent the source and target of the equation respectively.
+If we have a set $X$ with a map $c : \semP{A} \> X \rightarrow X$, each endpoint $e : \ep{A}{P}{Q}$ gives rise to a natural map $\semP{P} \> X \rightarrow \semP{Q} \> X$ where $\constr$ is interpreted with $c$.
+These maps are the left- and right-hand side of  the equations.
+
+Now we put it all together to define signatures of HITs.
 Note that we index the path constructors by a type meaning that we could possibly have infinitely many path constructors.
@@
 \label{def:signature}
-A \emph{HIT signature} $\Sigma$ consists of
-\begin{itemize}
-	\item A polynomial $\pointc{\Sigma} : \poly$;
-	\item A type $\pathI{\Sigma}$;
-	\item A family $\pathA{\Sigma} : \pathI{\Sigma} \rightarrow \poly$;
-	\item For each $j : \pathI{\Sigma}$, endpoints $\pathlh{\Sigma} \> j, \pathrh{\Sigma} \> j : \ep{P}{Q \> j}{I}$.
-\end{itemize}
-\end{definition}
-
-To illustrate the possibilities of this definition, we consider two examples.
-The first one is a set with a commutative operation and the second one is the propositional truncation.
+A \emph{HIT signature} $\sig$ consists of
+\begin{itemize}
+	\item A polynomial $\pointc{\sig} : \poly$ representing the point constructor;
+	\item A type $\pathI{\sig}$ representing the names of path constructors;
+	\item A family $\pathA{\sig} : \pathI{\sig} \rightarrow \poly$ representing the source of the paths;
+	\item Maps $\pathlh{\sig}, \pathrh{\sig} : \deprod{j}{\pathA{\sig}}{\ep{\pointc{\sig}}{\pathA{\sig} \> j}{I}}$ representing the left- and right-hand side of the equations.
+\end{itemize}
+\end{definition}
+
+Briefly, the signature $\sig$ represents the following HIT
+
+\begin{lstlisting}[mathescape=true]
+Inductive $H$ :=
+| $c$ : $\pointc{\sig} \> H \rightarrow H$
+| $p$ : $\deprod{j}{\pathI{\sig}}{\deprod{x}{\pathA{\sig} \> H}{\pathlh{\sig} \> j \> x = \pathrh{\sig} \> j \> x}}$
+\end{lstlisting}
+
+To illustrate the possibilities of this definition, we define two examples from the introduction as HIT signatures.
+The first one is the integers modulo 2 and the second one is the propositional truncation of a set.
 
 \begin{example}
-\label{ex:commsig}
-Define a signature $\comm$ such that
-\begin{itemize}
-	\item $\pointc{\comm} = \prodP{\I}{\I}$;
-	\item $\pathI{\comm} = \1$;
-	\item $\pathA{\comm} = \prodP{\I}{\I}$;
-	\item $\pathlh{\comm} \> j = \comp{\constr}{\id{\prodP{\I}{\I}}}$;
-	\item $\pathrh{\comm} \> j = \comp{\constr}{\pair{\comp{\prle}{\id{\prodP{\I}{\I}}}}{\comp{\prre}{\id{\prodP{\I}{\I}}}}}$;
+\label{ex:modsig}
+Recall $\modZ$ from the introduction.
+We represent it by the signature $\modsig$ defined as follows
+\begin{itemize}
+	\item $\pointc{\modsig} \Def \sumP{\I}{(\C \> \1)}$;
+	\item $\pathI{\modsig} \Def \1$;
+	\item $\pathA{\modsig} \Def \I$;
+	\item $\pathlh{\modsig} \> j \Def \comp{\comp{\comp{\comp{\id{\I}}{\inle}}{\constr}}{\inle}}{\constr}$;
+	\item $\pathrh{\modsig} \> j \Def \id{\I}$;
 \end{itemize}
@@
 
-Similarly, one can define signatures for groups or finite sets.
-Since signatures can depend on types, we can define the propositional truncation.
+Intuitively, this signature represents a HIT $H$ with operation $H + \1 \rightarrow H$ representing the successor and zero.
+Note that the endpoint $\comp{\inle}{\constr}$ takes the successor, so, the equation says that $S(S \> x) = x$ for all $x : X$.
+Similarly, one can define signatures for groups or join semi-lattices.
+Since signatures can depend on types, we can also define the propositional truncation.
 
@@
 Let $A$ be a set.
-Define a signature $\trunc$ such that
-\begin{itemize}
-	\item $\pointc{\trunc} = \C \> A$;
-	\item $\pathI{\trunc} = \1$;
-	\item $\pathA{\trunc} = \prodP{\I}{\I}$;
-	\item $\pathlh{\trunc} \> j = \comp{\prle}{\id{\prodP{\I}{\I}}}$;
-	\item $\pathrh{\trunc} \> j = \comp{\prre}{\id{\prodP{\I}{\I}}}$;
+We represent the truncation of a set by the following signature.
+\begin{itemize}
+	\item $\pointc{\trunc} \Def \C \> A$;
+	\item $\pathI{\trunc} \Def \1$;
+	\item $\pathA{\trunc} \Def \prodP{\I}{\I}$;
+	\item $\pathlh{\trunc} \> j \Def \comp{\id{\prodP{\I}{\I}}}{\prle}$;
+	\item $\pathrh{\trunc} \> j \Def \comp{\id{\prodP{\I}{\I}}}{\prre}$;
 \end{itemize}
 \end{example}
+This signature represents a HIT $H$ with a map $A \rightarrow H$ and for which all inhabitants are equal.
 
@@
 \label{sec:algebras}
+
+\subsection{Algebras in Sets}
 Now we know what signatures are, the next goal is to define HITs for signatures.
@@
 \begin{itemize}
-	\item $\semP{\C \> X} = \Cf{X}$;
-	\item $\semP{\I} = \idf{\hset}$;
-	\item $\semP{\sumP{P}{Q}} = \sumf{\semP{P}}{\semP{Q}}$;
-	\item $\semP{\sumP{P}{Q}} = \prodf{\semP{P}}{\semP{Q}}$.
-\end{itemize}
-\end{definition}
-
-Now we define the category $\prealg{\Sigma}$ to be the category of algebras on the functor $\semP{\pointc{\Sigma}}$.
-Its objects are maps $\semP{\pointc{\Sigma}} \> X \rightarrow X$.
-We call this the category of \emph{prealgebras} since these do not yet satisfy the equations in $\Sigma$.
-Note that we always have a forgetful functor $\forget{P} : \functor{\semP{P}}{\hset}$.
-
-To obtain actual algebras of $\Sigma$, we need to be able to interpret the equations and for that, we first need to interpret endpoints.
-These are interpreted as natural transformations, which are constructed using the transformations from Lemma \ref{def:nattrans}.
-Beside those, we need a transformation $\constrt{P} : \nattrans{\comp{\forget{P}}{\semP{P}}}{\comp{\forget{P}}{\semP{\I}}}$ for each polynomial $P$.
-Its components are given by the prealgebra map.
+	\item $\semP{\C \> X} \Def \Cf{X}$;
+	\item $\semP{\I} \Def \idf{\hset}$;
+	\item $\semP{\sumP{P}{Q}} \Def \sumf{\semP{P}}{\semP{Q}}$;
+	\item $\semP{\sumP{P}{Q}} \Def \prodf{\semP{P}}{\semP{Q}}$.
+\end{itemize}
+\end{definition}
+
+We write $\falg{F}$ for the category of algebras on the functor $F : \functor{\mathcal{C}}{\mathcal{C}}$.
+Its objects are pairs $X : \mathcal{C}$ together with an arrow $\mathcal{C}_1(F \> X, X)$.
+Note that we always have a forgetful functor $\forget{F} : \functor{\falg{F}}{\mathcal{C}}$.
+
+Now we define the category $\prealg{\sig}$ to be $\falg{\semP{\pointc{\sig}}}$.
+Since the objects do not satisfy the equations in $\sig$, we call this the category of \emph{prealgebras}.
+To obtain actual algebras of $\sig$, we need to interpret the equations and for that, we first need to interpret endpoints.
+These are interpreted as natural transformations, which are constructed using the transformations from \Cref{sec:prelim}.
+Beside those, we use for each polynomial $P$ the transformation $\constrt{P} : \nattrans{\comp{\forget{P}}{\semP{P}}}{\comp{\forget{P}}{\semP{\I}}}$ whose  components are given by the prealgebra map.
 
@@
 \begin{itemize}
-	\item $\semE{\id{P}} = \idt{\compf{\forget{A}}{\semP{P}}}$;
-	\item $\semE{\comp{e_1}{e_2}} = \compt{\semE{e_1}}{\semE{e_2}}$;
-	\item $\semE{\inle} = \lwhisker{\forget{A}}{\inlt}$;
-	\item $\semE{\inre} = \lwhisker{\forget{A}}{\inrt}$;
-	\item $\semE{\prle} = \lwhisker{\forget{A}}{\prlt}$;
-	\item $\semE{\prre} = \lwhisker{\forget{A}}{\prrt}$;
-	\item $\semE{\pair{e_1}{e_2}} = \pairt{\semE{e_1}}{\semE{e_2}}$;
-	\item $\semE{\Ce \> t} = \ctrans{t}$;
-	\item $\semE{\constr} = \constrt{A}$.
-\end{itemize}
-\end{definition}
-
-Now we have everything in place to define algebras on $\Sigma$.
-An algebra on $\Sigma$ need to have an operation which satisfies certain equations.
-For the operation, we use $\prealg{\pointc{\Sigma}}$.
+	\item $\semE{\id{P}} \Def \idt{\compf{\forget{A}}{\semP{P}}}$;
+	\item $\semE{\comp{e_1}{e_2}} \Def \compt{\semE{e_1}}{\semE{e_2}}$;
+	\item $\semE{\inle} \Def \lwhisker{\forget{A}}{\inlt}$;
+	\item $\semE{\inre} \Def \lwhisker{\forget{A}}{\inrt}$;
+	\item $\semE{\prle} \Def \lwhisker{\forget{A}}{\prlt}$;
+	\item $\semE{\prre} \Def \lwhisker{\forget{A}}{\prrt}$;
+	\item $\semE{\pair{e_1}{e_2}} \Def \pairt{\semE{e_1}}{\semE{e_2}}$;
+	\item $\semE{\Ce \> t} \Def \ctrans{t}$;
+	\item $\semE{\constr} \Def \constrt{A}$.
+\end{itemize}
+\end{definition}
+
+Now we have everything in place to define algebras on $\sig$.
+An algebra on $\sig$ consists of a carrier together with an operation which satisfies the equations specified by $\sig$.
+For the operation, we use $\prealg{\pointc{\sig}}$.
 Since the carrier of each prealgebra is a set, the equations form a proposition.
-Hence, we define the category of \emph{$\Sigma$-algebras} as a full subcategory of $\prealg{\pointc{\Sigma}}$.
+Hence, we define the category of \emph{$\sig$-algebras} as a full subcategory of $\prealg{\pointc{\sig}}$.
 
@@
 \label{def:algebra}
-Let $\Sigma$ be a HIT signature.
-Then we define the category $\Alg{\Sigma}$ of \emph{$\Sigma$-algebras} as the full subcategory of $\prealg{\pointc{\Sigma}}$ such that each object satisfies
+Let $\sig$ be a HIT signature.
+Then we define the category $\Alg{\sig}$ of \emph{$\sig$-algebras} as the full subcategory of $\prealg{\pointc{\sig}}$ such that each object $X$ satisfies
 \[
-\deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x = \semE{\pathrh{\Sigma} \> j} \> x}}.
+\deprod{j}{\pathI{\sig}}{\deprod{x}{\semP{\pathA{\sig} \> j} \> X}{\semE{\pathlh{\sig} \> j} \> X \> x = \semE{\pathrh{\sig} \> j} \> X \> x}}.
 \]
@@
 
-For an algebra $X$, we denote its operation by $\constrA{X} : \semP{\pointc{\Sigma}} \> X \rightarrow X$.
-The path witnessing the equalities of the algebra is denoted by $\constrP{X} : \deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x = \semE{\pathrh{\Sigma} \> j} \> x}}$.
-The category of $\Sigma$-algebras is univalent, which means that isomorphism of algebras corresponds to equality of algebras.
+For an algebra $X$, we denote its operation by $\constrA{X} : \semP{\pointc{\sig}} \> X \rightarrow X$.
+The path witnessing the equalities of the algebra is denoted by $\constrP{X} : \deprod{j}{\pathI{\sig}}{\deprod{x}{\semP{\pathA{\sig} \> j} \> X}{\semE{\pathlh{\sig} \> j} \> x = \semE{\pathrh{\sig} \> j} \> x}}$.
+Note that the category of $\sig$-algebras is univalent.
 This follows from the fact that the category of algebras on a functor is univalent and that univalence is preserved under taking full subcategories.
@@
 \label{prop:univalg}
-The category of $\Sigma$-algebras is univalent.
+The category of $\sig$-algebras is univalent.
 \end{proposition}
@@
 \label{ex:commalg}
-Recall the signature $\comm$ from Example \ref{ex:commsig}.
-An algebra of $\comm$ consists of a set $X$ and a map $f : X \times X \rightarrow X$ such that for all $(x , y) : X \times X$, we have $f(x, y) = f(y, x)$.
+Recall the signature $\modsig$ from Example \ref{ex:modsig}.
+A prealgebra of $\modsig$ consists of a set $X$ and a map $f : X + \1 \rightarrow X$.
+We define $S_X \> x \Def f(\inl \> x)$ and $Z_X = f(\inr \> \TT)$.
+An algebra of $\modsig$ consists of a prealgebra $X$ such that for all $x : X \times X$, we have $S_X(S_X \> x) = x$.
 \end{example}
@@
 
+\subsection{Algebras in Setoids}
 Recall that the core idea is that we define the initial algebra in sets by taking the quotient of the initial algebra in setoids.
@@
 
-To define the action of polynomials on equivalence relations, we need so preliminary operations.
+To define the action of polynomials on equivalence relations, we need some preliminary operations.
 For a set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y = (x = y)$.
 Furthermore, given types $X$ and $Y$ with equivalence relations $R_X$ and $R_Y$ on them, we can define equivalence relations $\sumR{R_X}{R_Y}$ and $\prodR{R_X}{R_Y}$ on $X + Y$ and $X \times Y$ respectively.
-These are defined such that
+These are defined as follows
 \[
-\prodR{R_X}{R_Y} \> (x_1,y_1) \> (x_2,y_2) = (R_X \> x_1 \> x_2) \times (R_Y \> y_1 \> y_2)
+\prodR{R_X}{R_Y} \> (x_1,y_1) \> (x_2,y_2) \Def (R_X \> x_1 \> x_2) \times (R_Y \> y_1 \> y_2)
 \]
@@
 \begin{array}{ccc}
-\sumR{R_X}{R_Y} \> (\inl \> x_1) \> (\inl \> x_2) = R_X \> x_1 \> x_2 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y_1) \> (\inr \> y_2) = R_Y \> y_1 \> y_2\\
-\sumR{R_X}{R_Y} \> (\inl \> x) \> (\inr \> y) = \0 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y) \> (\inl \> x) = \0\\ 
+\sumR{R_X}{R_Y} \> (\inl \> x_1) \> (\inl \> x_2) \Def R_X \> x_1 \> x_2 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y_1) \> (\inr \> y_2) \Def R_Y \> y_1 \> y_2\\
+\sumR{R_X}{R_Y} \> (\inl \> x) \> (\inr \> y) \Def \0 & \quad & \sumR{R_X}{R_Y} \> (\inr \> y) \> (\inl \> x) \Def \0\\ 
 \end{array}
@@
 \begin{itemize}
-	\item $\polyR{(\C \> T)}{R} = \pathR{T}$;
-	\item $\polyR{\I}{R} = R$;
-	\item $\polyR{(\sumP{P}{Q})}{R} = \sumR{(\polyR{P}{R})}{(\polyR{Q}{R})}$;
-	\item $\polyR{(\prodP{P}{Q})}{R} = \prodR{(\polyR{P}{R})}{(\polyR{Q}{R})}$.
-\end{itemize}
-Now we define a functor $\semPT{P} : \functor{\setoids}{\setoids}$ such that $\semPT{P}(X,R) = (\semP{P} \> X, P \> R)$.
-\end{definition}
-
-Again this gives rise to a category $\prealgst{\Sigma}$ of \emph{setoid prealgebras on $\Sigma$}.
-To define algebras on $\Sigma$, we also need to interpret endpoints.
+	\item $\polyR{(\C \> T)}{R} \Def \pathR{T}$;
+	\item $\polyR{\I}{R} \Def R$;
+	\item $\polyR{(\sumP{P}{Q})}{R} \Def \sumR{(\polyR{P}{R})}{(\polyR{Q}{R})}$;
+	\item $\polyR{(\prodP{P}{Q})}{R} \Def \prodR{(\polyR{P}{R})}{(\polyR{Q}{R})}$.
+\end{itemize}
+Now we define the functor $\semPT{P} : \functor{\setoids}{\setoids}$ by $\semPT{P}(X,R) = (\semP{P} \> X, \polyR{P}{R})$.
+\end{definition}
+
+Again this gives rise to a category $\prealgst{\sig}$ of \emph{setoid prealgebras on $\sig$}.
+To define algebras on $\sig$, we also need to interpret endpoints.
 However, these are just setoid morphisms instead of natural transformations.
@@
 Let $e : \ep{A}{P}{Q}$ be an endpoint and let $X$ be a setoid prealgebra on $A$.
-Then we define $\semE{e}$ to be the setoid morphism from $\semE{P}(X)$ to $\semE{Q}(X)$ whose carrier is $\semP{e}$.
-\end{definition}
-
-The category of algebras on $\Sigma$ is defined differently for setoids that for sets.
-While for sets we require actual equalities, for setoids the equations need to be witnessed by the equivalence relation instead.
-Note that such relations are families of propositions meaning again this gives rise to a proposition and thus we define i as a full subcategory.
-
-\begin{definition}
-Let $\Sigma$ be a HIT signature.
-Then we define the category of \emph{$\Sigma$-setoid-algebras} as the full subcategory of $\prealgst{\pointc{\Sigma}}$ such that each object satisfies
+Then we define $\semET{e}$ to be the setoid morphism from $\semE{P}(X)$ to $\semE{Q}(X)$ whose carrier is $\semP{e}$.
+\end{definition}
+
+The category of algebras on $\sig$ is defined differently for setoids than for sets.
+While for sets, the equations of algebras are witnessed by actual equalities, but for setoids, the equations are witnessed by the equivalence relation.
+Note that such relations are families of propositions meaning again this gives rise to a proposition and thus we define it as a full subcategory.
+
+\begin{definition}
+Let $\sig$ be a HIT signature.
+Then we define the category of \emph{$\sig$-setoid-algebras} as the full subcategory of $\prealgst{\pointc{\sig}}$ such that each object satisfies
 \[
-\deprod{j}{\pathI{\Sigma}}{\deprod{x}{\pathA{\Sigma} \> j}{\semE{\pathlh{\Sigma} \> j} \> x \equiv \semE{\pathrh{\Sigma} \> j} \> x}}.
+\deprod{j}{\pathI{\sig}}{\deprod{x}{\pathA{\sig} \> j}{\semE{\pathlh{\sig} \> j} \> x \equiv \semE{\pathrh{\sig} \> j} \> x}}
 \]
-\end{definition}
-
-Since the category of setoids is univalent, the category of $\Sigma$-setoid-algebras is univalent as well.
+where $\equiv$  is the setoid relation.
+\end{definition}
+
+Since the category of setoids is univalent, the category of $\sig$-setoid-algebras is univalent as well.
 
 \begin{proposition}
-The category of $\Sigma$-setoid-algebras is unvialent.
+The category of $\sig$-setoid-algebras is unvialent.
 \end{proposition}
@@
 To formulate these two rules, we make use of \emph{displayed algebras}, which represent the input of the elimination rule.
-When we got all this machinery in place, we define the notion of \emph{higher inductive type} for a signature.
-
-Since our goal is to construct HITs, we need verify the induction rule and for that, we use initial algebra semantics.
+When we have all this machinery in place, we define the notion of \emph{higher inductive type} for a signature.
+
+Since our goal is to construct HITs, we need to verify the induction rule and for that, we use initial algebra semantics.
 More specifically, we show that the initial algebra satisfies the induction rule.
-Hence, to obtain it a HIT, it suffices to construct the initial algebra for which we use category theory.
+Hence, to obtain a HIT, it suffices to construct the initial algebra, for which we use category theory.
 
@@
 This means that we have a dependent family and a dependent map over the point constructor.
-Furthermore, dependent versions of the equations in the signature needs to hold.
-To formulate these requirements more precisely, we need two preliminary definitions.
-The first one gives an action of polynomials on type families while the second one interprets endpoints as dependent maps.
+Furthermore, dependent versions of the equations in the signature need to hold.
+Displayed algebras are similar to displayed categories \cite{AhrensL19}.
+
+To formulate these requirements precisely, we need two preliminary definitions.
+The first one is the action of polynomials on families of sets while the second one interprets endpoints as dependent maps.
 
@@
 \begin{itemize}
-	\item $\polydact{\C \> X}{Y} \> x = X$;
-	\item $\polydact{\I}{Y} \> x = Y \> x$;
-	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inl \> x) = \polydact{P}{Y} \> x$;
-	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inr \> x) = \polydact{Q}{Y} \> x$;
-	\item $\polydact{\prodP{P}{Q}}{Y} \> x = \polydact{P}{Y} \> (\prl \> x) \times \polydact{Q}{Y} \> (\prr \> x)$.
+	\item $\polydact{\C \> X}{Y} \> x \Def X$;
+	\item $\polydact{\I}{Y} \> x \Def Y \> x$;
+	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inl \> x) \Def \polydact{P}{Y} \> x$;
+	\item $\polydact{\sumP{P}{Q}}{Y} \> (\inr \> x) \Def \polydact{Q}{Y} \> x$;
+	\item $\polydact{\prodP{P}{Q}}{Y} \> x \Def \polydact{P}{Y} \> (\prl \> x) \times \polydact{Q}{Y} \> (\prr \> x)$.
 \end{itemize}
@@
 \begin{itemize}
-	\item $\epdact{\id{P}}{c} \> z \> y = y$;
-	\item $\epdact{\comp{e_1}{e_2}}{c} \> z \> y = \epdact{e_2}{c} \> (\semE{e} \> X \> z) \> (\epdact{e_1}{c} \> z \> y)$;
-	\item $\epdact{\inle}{c} \> z \> y = y$;
-	\item $\epdact{\inre}{c} \> z \> y = y$;
-	\item $\epdact{\prle}{c} \> z \> y = \prlt \> y$;
-	\item $\epdact{\prre}{c} \> z \> y = \prrt \> y$;
-	\item $\epdact{\pair{e_1}{e_2}}{c} \> z \> y = (\epdact{e_1}{c} \> z \> y , \epdact{e_2}{c} \> z \> y)$;
-	\item $\epdact{\Ce \> t}{c} \> z \> y = t$;
-	\item $\epdact{\constr}{c} = c$.
+	\item $\epdact{\id{P}}{c} \> z \> y \Def y$;
+	\item $\epdact{\comp{e_1}{e_2}}{c} \> z \> y \Def \epdact{e_2}{c} \> (\semE{e} \> X \> z) \> (\epdact{e_1}{c} \> z \> y)$;
+	\item $\epdact{\inle}{c} \> z \> y \Def y$;
+	\item $\epdact{\inre}{c} \> z \> y \Def y$;
+	\item $\epdact{\prle}{c} \> z \> y \Def \prlt \> y$;
+	\item $\epdact{\prre}{c} \> z \> y \Def \prrt \> y$;
+	\item $\epdact{\pair{e_1}{e_2}}{c} \> z \> y \Def (\epdact{e_1}{c} \> z \> y , \epdact{e_2}{c} \> z \> y)$;
+	\item $\epdact{\Ce \> t}{c} \> z \> y \Def t$;
+	\item $\epdact{\constr}{c} \Def c$.
 \end{itemize}
@@
 With this in place, we define displayed algebras.
-Note that since we are working in a type family, we need to use the dependent equality type from Definition \ref{def:depeq} instead.
-
-\begin{definition}
-Let $\Sigma$ be a HIT signature and let $X$ be an algebra on $\sigma$.
+Note that since we are working in a family of sets, we need to use the dependent equality type from Definition \ref{def:depeq} instead.
+
+\begin{definition}
+Let $\sig$ be a HIT signature and let $X$ be an algebra on $\sigma$.
 Then a \emph{displayed algebra} over $X$ consists of
@@
 	\item An operation $c_Y : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)}$;
-	\item For each $j : \pathI{\Sigma}$, $x : \semP{\pathA{\Sigma}} \> X$, and $y : \polydact{\pathA{\Sigma}}{Y} \> x$,  a path $p_Y : \depeq{\constrP{X} \> j \> x}{\epdact{\pathlh{\Sigma}}{c} \> x \> y}{\epdact{\pathrh{\Sigma}}{c} \> x \> y}$.
+	\item For each $j : \pathI{\sig}$, $x : \semP{\pathA{\sig}} \> X$, and $y : \polydact{\pathA{\sig}}{Y} \> x$,  a path $p_Y : \depeq{\constrP{X} \> j \> x}{\epdact{\pathlh{\sig}}{c} \> x \> y}{\epdact{\pathrh{\sig}}{c} \> x \> y}$.
 \end{itemize} 
@@
 \begin{itemize}
-	\item $\polydmap{\C \> X}{f} \> x = x$;
-	\item $\polydmap{\I}{f} = f$;
-	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inl \> x) = \polydmap{P}{f} \> x$;
-	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inr \> x) = \polydmap{Q}{f} \> x$;
-	\item $\polydmap{\prodP{P}{Q}}{f} \> x = (\polydact{P}{f} \> (\prl \> x) , \polydact{Q}{f} \> (\prr \> x))$.
+	\item $\polydmap{\C \> X}{f} \> x \Def x$;
+	\item $\polydmap{\I}{f} \Def f$;
+	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inl \> x) \Def \polydmap{P}{f} \> x$;
+	\item $\polydmap{\sumP{P}{Q}}{f} \> (\inr \> x) \Def \polydmap{Q}{f} \> x$;
+	\item $\polydmap{\prodP{P}{Q}}{f} \> x \Def (\polydact{P}{f} \> (\prl \> x) , \polydact{Q}{f} \> (\prr \> x))$.
 \end{itemize}
@@
 Let $Y$ be a displayed algebra over $X$.
-Then a displayed algebra map to $Y$ consists of a map $f : \deprod{x}{X}{Y \> x}$ such that for each $x : \semP{\pointc{\Sigma}}{X}$, we have $f(\constrA{X} \> x) = c_Y \> x \> (\polydmap{\pointc{\Sigma}}{f} \> x)$.
+Then a displayed algebra map to $Y$ consists of a map $f : \deprod{x}{X}{Y \> x}$ such that for each $x : \semP{\pointc{\sig}}{X}$, we have $f(\constrA{X} \> x) = c_Y \> x \> (\polydmap{\pointc{\sig}}{f} \> x)$.
 \end{definition}
@@
 \begin{definition}
-Let $\Sigma$ be a HIT signature.
-A \emph{higher inductive type} on $\Sigma$ consists of an algebra $H$ such that for each displayed algebra $Y$ on $H$, we have a displayed algebra map to $Y$.
+Let $\sig$ be a HIT signature.
+A \emph{higher inductive type} on $\sig$ consists of an algebra $H$ such that for each displayed algebra $Y$ on $H$, we have a displayed algebra map to $Y$.
 \end{definition}
@@
 We define the carrier of $\total{Y}$ by the dependent sum $\desum{x}{X}{Y \> x}$ and for brevity, we denote this by $\total{Y}$.
-To show this is an algebra, we first need to define a map $c_{\total{Y}} : \semP{\pointc{\Sigma}} \> (\total{Y}) \rightarrow \total{Y}$.
+To show this is an algebra, we first need to define a map $c_{\total{Y}} : \semP{\pointc{\sig}} \> (\total{Y}) \rightarrow \total{Y}$.
 The main idea is that we use the algebra map of $X$ for the first component and the algebra map of $Y$ for the second one.
@@
 \quad \quad
-\Ppl{P} \> x = \semP{\pointc{\Sigma}} \> \prl \> x
+\Ppl{P} \> x \Def \semP{\pointc{\sig}} \> \prl \> x
 \]
@@
 \begin{itemize}
-	\item $\Ppr{\C \> T} \> x  = x$;
-	\item $\Ppr{\I} \> x = \prr \> x$;
-	\item $\Ppr{\sumP{P}{Q}} \> (\inl x) = \Ppr{P} \> x$;
-	\item $\Ppr{\sumP{P}{Q}} \> (\inr x) = \Ppr{Q} \> x$;
-	\item $\Ppr{\prodP{P}{Q}} \> x = (\Ppr{P} \> x , \Ppr{Q} \> (\prr \> x))$.
-\end{itemize}
-\end{definition}
-
-Now let $z : \semP{\pointc{\Sigma}} \> (\total{Y})$.
+	\item $\Ppr{\C \> T} \> x  \Def x$;
+	\item $\Ppr{\I} \> x \Def \prr \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inl x) \Def \Ppr{P} \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inr x) \Def \Ppr{Q} \> x$;
+	\item $\Ppr{\prodP{P}{Q}} \> x \Def (\Ppr{P} \> x , \Ppr{Q} \> (\prr \> x))$.
+\end{itemize}
+\end{definition}
+
+Now let $z : \semP{\pointc{\sig}} \> (\total{Y})$.
 The first coordinate of $c_{\total{Y}} \> z$ is defined to be $\constrA{X}(\Ppl{P} \> x)$.
@@
 The main challenge lies within proving the equations.
+To do so, we compute the valuation of endpoints in the total algebra via those in $X$ and $Y$.
 
 \begin{lemma}
-For every endpoint $e : \ep{\pointc{\Sigma}}{P}{Q}$, we have
+For every endpoint $e : \ep{\pointc{\sig}}{P}{Q}$, we have
 \[
@@
 \begin{proposition}
-From an algebra homomorphism $f : X \rightarrow \total{Y}$ such that $\comp{f}{\proj{Y}}$ is the identity, we obtain a displayed algebra map from $X$ to $Y$.
+From an algebra homomorphism $f : X \rightarrow \total{Y}$ such that $\compm{f}{\proj{Y}}$ is the identity, we obtain a displayed algebra map from $X$ to $Y$.
 \end{proposition}
@@
 Now suppose $X$ is an initial object in the category of algebras.
-Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because of initiality as well.
+Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because initiality ensures uniqueness of homomorphisms from $X$ to $X$.
 Hence, we conclude
@@
 \begin{corollary}
-If $X$ is an initial object in the category of algebras on $\Sigma$, then $X$ is a HIT for $\Sigma$.
+If $X$ is an initial object in the category of algebras on $\sig$, then $X$ is a HIT for $\sig$.
 \end{corollary}
@@
 \begin{theorem}
+\label{thm:hit-exist}
 HITs exist
@@
 \label{sec:consequences}
-
-\subsection{Recursion}
-
-\begin{definition}
-Let $X$ and $Y$ be algebras on $\Sigma$.
-Then we define the \emph{constant displayed algebra} on $X$ from $Y$ as follows
-\begin{itemize}
-	\item The type family is $Y$ for each $x$;
-	\item
-\end{itemize}
-\end{definition}
-
-\begin{proposition}
-Let $X$ be $Y$ be algebras on $\Sigma$.
-If we have a displayed algebra from $X$ to the constant displayed algebra on $X$ from $Y$, then we have an algebra homomorphism from $X$ to $Y$.
-\end{proposition}
-
-\begin{corollary}
-If $X$ is a HIT for $\Sigma$, then for each algebra $Y$ we have an algebra map from $X$ to $Y$.
-\end{corollary}
-
 \subsection{Uniqueness of HITs}
@@
 To show a HIT $H$ is initial, we must show that for each algebra $X$ the set of morphisms from $H$ to $X$ is contractible.
-This means that there is at most one morphism.
-To show the existence, we use the recursion rule.
+This means that there is precisely one homomorphism from $H$ to $X$.
+To show the existence, we use the following two lemmata.
+
+\begin{lemma}
+Let $X$ and $Y$ be algebras on $\sig$.
+Then there is a displayed algebra $\constdisp{Y}$ on $X$ of which the underlying type family is $Y$ on each point of $X$.
+\end{lemma}
+
+\begin{lemma}
+Let $X$ be $Y$ be algebras on $\sig$.
+If we have a displayed algebra map from $X$ to $\constdisp{Y}$, then we have an algebra homomorphism from $X$ to $Y$.
+\end{lemma}
+
+\begin{corollary}
+If $X$ is a HIT for $\sig$, then for each algebra $Y$ we have an algebra map from $X$ to $Y$.
+\end{corollary}
+
 To show uniqueness, we use an alternative induction principle for families of propositions.
@@
 \begin{lemma}
-Let $H$ be a HIT of $\Sigma$ and suppose $Y$ is a family of propositions on $H$.
+Let $H$ be a HIT of $\sig$ and suppose $Y$ is a family of propositions on $H$.
 If we have an operation
@@
 \begin{proposition}
-If $H$ is a HIT for $\Sigma$, then $H$ is an initial $\Sigma$-algebra.
+If $H$ is a HIT for $\sig$, then $H$ is an initial $\sig$-algebra.
 \end{proposition}
 
-Now we take advantage of the fact that the category of algebras is univalent.
+Now we take advantage of Proposition \ref{prop:univalg} where we proved that the category of algebras is univalent.
 Since initial objects in a univalent category are unique up to equality, we can immediately conclude that HITs are actually unique up to equality.
@@
 
-\begin{theorem}
-If $H_1$ and $H_2$ are HITs for $\Sigma$, the $H_1 = H_2$ as $\Sigma$-algebras.
-\end{theorem}
+\begin{corollary}
+If $H_1$ and $H_2$ are HITs for $\sig$, then the underlying $\sig$-algebras of $H_1$ and $H_2$ are equal.
+\end{corollary}
 
@@
 The construction of HITs also allows us to characterize the path space up to equivalence.
-
-\begin{proposition}
+For this, we first recall the characterization of the path space of the quotient type.
+
+\begin{proposition}[Lemma 10.1.8 from \cite{hottbook}]
 Let $X$ be a type and let $R$ be an equivalence relation on $X$.
@@
 
-\section{Conclusion}
+Now we specialize this theorem to HITs constructed according to Theorem \ref{thm:hit-exist}.
+This allows us to conclude that the path space of set truncated HITs is freely generated.
+
+\begin{corollary}
+Let $\sig$ be a signature.
+Then for each $x, y : ...$ we have an equivalence $....$.
+\end{corollary}
+
+\section{Conclusion and Further Work}
 \label{sec:conclusion}
-
-\cite{AhrensKS15}
-\cite{AhrensL19}
-\cite{mac2013categories}
+\cite{ahrens2019bicategories}
+\cite{capriotti2017univalent}
 

### 2019-03-31 paper/paper.tex
Futher work on paper

@@
 \newcommand{\falg}[1]{\category{FAlg}(#1)} % category of algebras on a functor
+\newcommand{\adj}[2]{#1 \dashv #2} % adjunction
+\newcommand{\fullsub}[2]{\function{full}(#1,#2)} % full subcategory
+\newcommand{\factorsub}[1]{#1_{\function{sub}}} % factor through full sub
 
@@
 \newcommand{\ZZ}{\constructor{Z}} % zero
-\newcommand{\SZ}{\constructor{S}} % zero
+\newcommand{\SZ}{\constructor{S}} % successor
 \newcommand{\modP}{\constructor{mod}} % n = n + 2
@@
 
-\newcommand{\remove}{}
+% Adjunction
+\newcommand{\quotF}{\mathcal{Q}}
+\newcommand{\pathF}{\pi_0}
+\newcommand{\quotPA}{\mathcal{Q}^{\category{PreAlg}}}
+\newcommand{\pathPA}{\pi^{\category{PreAlg}_0}}
+\newcommand{\quotAA}{\mathcal{Q}^{\category{Alg}}}
+\newcommand{\pathAA}{\pi_0^{\category{Alg}}}
+
+% Free congruence
+\newcommand{\CRC}{\mathcal{X}} % carrier
+\newcommand{\CR}{\mathcal{R}^*} % relation
+\newcommand{\CRR}{\mathcal{R}} % relation
+\newcommand{\CRrefl}{\constructor{refl}} % reflexivity
+\newcommand{\CRsym}{\constructor{sym}} % symmetry
+\newcommand{\CRtrans}{\constructor{trans}} % transitivity
+\newcommand{\CRpair}{\constructor{pair}} % pair
+\newcommand{\CRinl}{\constructor{inl}} % in left
+\newcommand{\CRinr}{\constructor{inr}} % in right
+\newcommand{\CRpath}{\constructor{path}} % path constuctors
+\newcommand{\CRcong}{\constructor{cong}} % congruence
+
+\newcommand{\remove}{} % remove a part
 
@@
   To interpret HITs, we use initial algebra semantics for which we show that the initiality implies induction.
-  The desired algebra is obtained by lifting the quotient adjunction to the level of algebras and adapting Dybjer's and Moenclaey's interpretation of HITs in setoids.
+  The desired algebra is obtained by lifting the quotient adjunction to the level of algebras and adapting Dybjer's and Moeneclaey's interpretation of HITs in setoids.
   From this construction, we conclude that the equality types of HITs are freely generated and that HITs are unique.
@@
 synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.
-
-To get a feeling for what HITs are, let us look a some examples before looking at them more formally.
+To get a feeling for what HITs are, let us look a some examples.
 
@@
 The first one, $\Circ$, is the \emph{circle}.
-It has a point, $\base$, and a path $\loopS : \base = \base$.
+It has a point $\base$ and a path $\loopS : \base = \base$.
 Since neither the point nor path constructors uses arguments from $\Circ$, this HIT is \emph{nonrecursive}.
@@
 This type is $A$ with all its points identified.
-Note that the path constructor $p$ uses arguments from $\trunct{A}$, and thus this HIT is called \emph{recursive}.
-The last one $, \modZ$ is the \emph{integers modulo 2} and note that both the point constructor $\SZ$ and path constructor $\modP$ are recursive.
-
-HITs have also been studied more formally and several schemes have already been developed.
+Note that the path constructor $p$ uses arguments from $\trunct{A}$, which means this HIT is \emph{recursive}.
+The last one, $\modZ$, is the \emph{integers modulo 2} and note that both the point constructor $\SZ$ and path constructor $\modP$ are recursive.
+
+HITs have been studied formally and several schemes have already been developed.
 Awodey \etal \ showed that the rules of inductive types \cite{dybjer1994inductive} in HoTT are equivalent to being a homotopy initial algebra \cite{AwodeyGS12}.
 They extended this result to a class of HITs called \emph{W-suspensions} \cite{Sojakova15}.
-Another scheme, quotient inductive-inductive types, was defined semantically by Altenkirch \etal \ and they prove initial algebra semantics \cite{AltenkirchCDKF18}.
+Another scheme, quotient inductive-inductive types (QIITs), was defined semantically by Altenkirch \etal \ and they show initial algebras are QIITs \cite{AltenkirchCDKF18}.
 Assuming UIP, Kaposi \etal \ constructed finitary QIITs as the syntax of a domain specific type theory \cite{KaposiKA19}, and they extended this scheme to higher inductive-inductive types \cite{KaposiK18}.
-Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}.
-Dybjer and Moenclaey defined a scheme allowing constructors for points, paths, and homotopies. and give its semantics in the groupoid model  \cite{DybjerM18,HofmannS94}.
+Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}
+while Dybjer and Moenclaey defined a scheme allowing constructors for points, paths, and homotopies, and they give its interpretation in the groupoid model  \cite{DybjerM18,HofmannS94}.
 Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types and proved canonicity \cite{AngiuliHW17,CavalloH19}.
@@
 Coquand \etal \ provide the semantics of various higher inductive types, such as spheres, the torus, the truncation, and the pushout, in cubical type theory \cite{BezemCH13,CohenCHM16,CoquandHM18}.
-On the other hand, Lumsdaine and Shulman also study the semantics of higher inductive types, but they use a semantic scheme (cell monads with parameters) and proof existence in sufficiently nice Quillen model categories \cite{lumsdaine2017semantics}.
+On the other hand, Lumsdaine and Shulman also study the semantics of higher inductive types using a semantic scheme (cell monads with parameters) and they prove existence in sufficiently nice Quillen model categories \cite{lumsdaine2017semantics}.
 Some recursive higher inductive types can be constructed from nonrecursive HITs.
@@
 This briefly means that all higher inductive types exist if a small number of simple ones exist.
+A similar result was obtained by Kaposi \etal \ \cite{KaposiKA19}, but we do not assume UIP and we use simpler HITs for the construction.
 Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
-The latter result is similar to work by Kraus and Von Raumer \cite{KrausRaumer}.
-Note that from this construction we can conclude that finitary set-truncated HITs can be constructed from non-recursive HITs.
-Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction.
-
-The main idea of the proof is to take advantage that the quotient is an adjoint functor \cite{RijkeS15} from setoids to sets.
+Kraus and Von Raumer obtained an analogous result for the coequalizer by providing a nicer induction principle for its path types \cite{KrausRaumer}.
+Note that from our construction we can conclude that all finitary set-truncated HITs can be constructed from non-recursive HITs.
+Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction \cite{rijke2017join}.
+
+The main idea of the proof is to take advantage that the quotient is left adjoint functor from setoids to sets \cite{RijkeS15}.
 To relate this to HITs, we first define schemes, which are an internalized version of the schema by Basold \etal \ \cite{BasoldGW17}, and categories of algebras on them.
@@
 \label{sec:construction}
-
-\subsection{Adjunction between Algebras}
-To construct the adjunction between the category of algebras, we use two lemmata
+To construct the initial algebra, we first define a left adjoint from algebras in setoids to algebras in algebras.
+Such functors preserve initial objects, and thus it suffices to construct the initial setoid algebra.
+For that, we use an adaption of Dybjer's and Moeneclaey's interpretation of HITs in the setoid model \cite{DybjerM18,moeneclaey2016schema}.
+In the remainder of this section, we work with a fixed signature $\sig$.
+
+\subsection{Quotient Adjunction}
+We start by defining a left adjoint functor $\quotF : \functor{\setoids}{\hset}$.
+On objects, we define $\quotF \> (X , R) = \setquot{X}{R}$ and its action on morphisms is defined by recursion on the quotient type.
+The laws are proven by quotient induction.
+The right adjoint is the path setoid functor $\pathF : \functor{\hset}{\setoids}$.
+For sets $X$, we define functor $\pathF \> X$ to be $(X, =_X)$ where $=_X$ is the equivalence relation on $X$ defined by $\lambda x y, x = y$.
+Note that this action is functorial and that this gives rise to an adjunction.
+
+\begin{lemma}[Theorem 2.20 from \cite{RijkeS15}]
+We have an adjunction $\adj{\quotF}{\pathF}$.
+\end{lemma}
+
+\subsection{The Adjunction on Prealgebras}
+With this adjunction in place, our first step is to lift it to the level of prealgebras.
+The first step, is to lift the functors for which we use the following lemma.
 
 \begin{lemma}
-Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and $F : \functor{\mathcal{C}}{\mathcal{D}}$.
-Then we get a functor 
+\label{lem:prealgadj}
+Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $F : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{F}{A_2}}{\compf{A_1}{F}}$.
+Then we get a functor $F^{\category{PreAlg}} : \functor{\falg{A_1}}{\falg{A_2}}$.
 \end{lemma}
 
+For algebras $(X, f) : \falg{A_1}$, we define $F^{\category{PreAlg}}(X,f) = (F \> X, \compm{F \> f}{n \> X})$.
+
 \begin{lemma}
-Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$, $A_{\mathcal{D}} : \functor{\mathcal{D}}{\mathcal{D}}$, and an adjunction ....
-Suppose, the following diagrams commute
-
-Then we get an adjunction
+\label{lem:comm}
+We have
+\begin{itemize}
+	\item $\pathF$ commutes with sums and products.
+	\item $\quotF$ commutes with sums and products.
+\end{itemize}
+This gives rise to two natural isomorphisms $n_1 : \nattrans{\compf{\pathF}{\semPT{\pointc{\sig}}}}{\compf{\semP{\pointc{\sig}}}{\pathF}}$
 \end{lemma}
 
+Now we use Lemmata \ref{lem:prealgadj} and \ref{lem:comm} to lift both the quotient and the path setoid functors and we get
+\[
+\quotPA : \functor{\prealgst{\sig}}{\prealg{\sig}}
+\quad \quad
+\pathPA : \functor{\prealg{\sig}}{\prealgst{\sig}}.
+\]
+
 \begin{lemma}
-Adjunction between full subcategories
+We have an adjunction $\adj{\quotPA}{\pathPA}$.
 \end{lemma}
 
-Now we apply these to get an adjunction between set HIT-algebras and setoid HIT-algebras.
-For this, we do the following steps.
+\subsection{Algebras}
+
+If $\mathcal{C}$ is a category and $P$ is a family of propositions on $\mathcal{C}$, then we write $\fullsub{\mathcal{C}}{P}$ for the full subcategory of $\mathcal{C}$ in which each object satisfies $P$.
+First, we look at way to obtain adjunctions between full subcategories.
 
 \begin{lemma}
-The path setoid commutes with sums and products.
-
-The quotient commutes with sums and products.
+Let $\mathcal{C}$ and $\mathcal{D}$ be categories, let $P_1$ and $P_2$ be families of propositions on $\mathcal{C}$ and $\mathcal{D}$ respectively, and suppose we have a functor $F : \functor{\mathcal{C}}{\mathcal{D}}$.
+If for each object $x : \mathcal{C}$ we have $P_1 \> x \rightarrow P_2(F \> x)$, then we get a functor $\factorsub{F} : \functor{\fullsub{\mathcal{C}}{P_1}}{\fullsub{\mathcal{D}}{P_2}}$.
 \end{lemma}
 
-\begin{lemma}
-We have a natural isomorphism (path setoid/quotients commutes with polynomials).
-\end{lemma}
+\begin{proposition}
+Let $\mathcal{C}$ and $\mathcal{D}$ be categories, let $P_1$ and $P_2$ be families of propositions on $\mathcal{C}$ and $\mathcal{D}$ respectively, and suppose we have an adjunction $\adj{L}{R}$ with $L : \functor{\mathcal{C}}{\mathcal{D}}$.
+If for each object $x : \mathcal{C}$ we have $P_1 \> x \rightarrow P_2(L \> x)$ and for each $y : \mathcal{D}$ we have $P_2 \> x \rightarrow P_1(R \> x)$, then we get an adjunction $\adj{\factorsub{L}}{\factorsub{R}}$.
+\end{proposition}
+
+Now we would like to apply this proposition to the adjunction obtained from Lemma \ref{lem:prealgadj}.
+
+\begin{theorem}
+\label{thm:algadj}
+We have an adjunction $\adj{\quotAA}{\pathAA}$.
+\end{theorem}
 
@@
 We can verify the conditions and we get
-
-\begin{lemma}
-There is an adjunction between prealgebras ...
-\end{lemma}
 
@@
 
+\subsection{Initial Setoid Algebra}
+The initial setoid is constructed in two steps.
+First we define its carrier as the initial algebra on $\pointc{\sig}$ and then we define the equivalence relation as the least congruence relation containing the equations in $\sig$ and preserving equality of the point constructor.
+
+\begin{lemma}
+The category $\prealg{\pointc{\sig}}$ has an initial object.
+\end{lemma}
+
+This follows from Ad\'amek's theorem and the fact that the functors $\semP{P}$ is $\omega$-continuous for each $P$.
+We denote the initial object of this category by $(\CRC , f)$.
+The carrier of the desired setoid is $\CRC$ meaning that the next step is to define the equivalence relation on $\CRC$.
+
+The main difficulty of defining this relation, is that we also must behave correctly on $\semP{\pointc{\sig}}{\CRC}$, because otherwise, we would not be able to lift $f$ to a setoid morphism.
+For that reason, we first define a relation $\CR \> P$ on $\semP{P} \> \CRC$ for each $P : \poly$..
+
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$x : \semP{P} \> \CRC$}
+\UnaryInfC{$\CRrefl \> x : \CR \> P \> x \> x$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$r : \CR \> P \> x \> y$}
+\UnaryInfC{$\CRsym \> r : \CR \> P \> y \> x$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$r_1 : \CR \> P \> x \> y$}
+\AxiomC{$r_2 : \CR \> P \> y \> z$}
+\BinaryInfC{$\CRtrans \> r_1 \> r_2 : \CR \> P \> x \> z$}
+\end{bprooftree}
+\end{center}
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$r : \CR \> P_1 \> x \> y$}
+\UnaryInfC{$\CRinl \> r : \CR \> (\sumP{P_1}{P_2}) \> (\inl \> x) \> (\inl \> y)$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$r : \CR \> P_2 \> x \> y$}
+\UnaryInfC{$\CRinr \> r : \CR \> (\sumP{P_1}{P_2}) \> (\inr \> x) \> (\inr \> y)$}
+\end{bprooftree}
+\end{center}
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$r_1 : \CR \> P_1 \> x_1 \> x_2$}
+\AxiomC{$r_2 : \CR \> P_2 \> y_1 \> y_2$}
+\BinaryInfC{$\CRpair \> r_1 \> r_2 : \CR \> (\prodP{P_1}{P_2}) \> (x_1 , x_2) \> (y_1 , y_2)$}
+\end{bprooftree}
+\end{center}
+\begin{center}
+\begin{bprooftree}
+\AxiomC{$j : \pathI{\sig}$}
+\AxiomC{$x : \semP{\pathA{\sig} \> j} \> \CRC$}
+\BinaryInfC{$\CRpath \> j \> x : \CR \> (\semE{\pathlh{\sig} \> j} \> \CRC \> x) \> (\semE{\pathrh{\sig} \> j} \> \CRC \> x)$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$r : \CR \> (\pointc{\sig}) \> x \> y$}
+\UnaryInfC{$\CRcong \> r : \CR \> \I \> (f \> x) \> (f \> y)$}
+\end{bprooftree}
+\end{center}
+
+Now we define a relation on $\CRC$ by $\CRR \> x \> y = \trunct{\CR \> \I \> x \> y}$.
+Because of the truncation, it takes value in proposition.
+Note that $\CRR$ is an equivalence relation, because of the constructor $\CRrefl$, $\CRsym$, and $\CRtrans$.
+In addition, all equations in $\sig$ are identified in $\CRR$, because of the constructor $\CRpath$.
+Lastly, with the constructors $\CRinl$, $\CRinr$, and $\CRcong$, we can show that $\CRR$ preserves $f$.
+Hence, we obtain a setoid $I \Def (\CR, \CRC)$ together with a setoid morphism $\varphi : \semPT{P} \> I \rightarrow I$.
+To show that this is the initial setoid, we first need a property of $\CRR$, which allows us to make maps from $I$ to algebras.
+
+\begin{lemma}
+\label{lem:mapcongrel}
+If $g$ is a prealgebra morphism from $\CR$ to some algebra $X$, then $g$ preserves $\CRR$.
+\end{lemma}
+
+Now we show that $I$ is an initial object in $\Alg{\sig}$.
+To show that we always have a homomorphism from $I$ to an algebra $X$, we use that $\CR$ is the initial prealgebra and lemma \ref{lem:mapcongrel}.
+Furthermore, note that two setoid morphisms are equal if their underlying carriers are equal and two algebra morphisms are also equal if their underlying carrier is equal.
+Hence, the uniqueness also follows from initiality of $\CR$.
 All in all, we get
 
-\begin{proposition}
-We have an adjunction
-\end{proposition}
-
-\subsection{Initial Setoid Algebra}
-
-Hence, we conclude
-
 \begin{theorem}
+\label{thm:initialsetoid}
+The category $\Algst{\sig}$ has an initial object.
+\end{theorem}
+
+From Theorems \ref{thm:algadj} and \ref{thm:initialsetoid} we conclude
+
+\begin{corollary}
 \label{thm:hit-exist}
-HITs exist
-\end{theorem}
+For each signature $\sig$, we can construct a HIT on $\sig$.
+\end{corollary}
 
@@
 \begin{corollary}
+\label{cor:hit_unique}
 If $H_1$ and $H_2$ are HITs for $\sig$, then the underlying $\sig$-algebras of $H_1$ and $H_2$ are equal.
@@
 \begin{corollary}
+\label{cor:hit_path}
 Let $\sig$ be a signature.
-Then for each $x, y : ...$ we have an equivalence $....$.
+Then for each $x, y : \CR$ we have an equivalence $\CRR \> x \> y \weq \classof \> x = \classof \> y$.
 \end{corollary}
@@
 \label{sec:conclusion}
-\cite{ahrens2019bicategories}
-\cite{capriotti2017univalent}
+We showed how to construct finitary set-truncated higher inductive types using the quotient and propositional truncation in Theorem \ref{thm:hit-exist}.
+Since truncations and the quotient can be constructed from nonrecursive HITs, this proves that all finitary set-truncated HITs can be constructed from nonrecursive ones.
+Besides that, we took advantage of this construction to show uniqueness of HITs in Corollary \ref{cor:hit_unique} and to characterize their path space in Corollary \ref{cor:hit_path}.
+
+For a construction of all finitary HITs, higher path constructors need to be allowed and the HITs need to be interpreted as higher categories instead of sets.
+A first step towards that goal, would be adapting this construction to bicategory theory \cite{ahrens2019bicategories,capriotti2017univalent} and constructing higher inductive 1-types using Dybjer's and Moeneclaey's interpretation of such HITs in groupoids \cite{DybjerM18}.
+Doing so, would require interpreting the path constructor terms and the path computation rule becomes relevant.
+Proving the induction principle from initiality is more difficult then, because equality becomes proof relevant.
+In this setting, Corollary \ref{cor:hit_path} is more interesting, because the computation rules of path constructors become nontrivial.
 
@@
 \end{thebibliography}
-
-%\begin{thebibliography}{10}\label{bibliography}
-%\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
-%    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.
-
-%\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
-%  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
-%  Providence, R.I., 1961.
-
-%\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
-%  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
-%  Theoretical Computer Science {\bf 1} (1995), URL:
-%  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
-%  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.
-
-%\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
-%    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
-%  preprint 93/52.
-
-%\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
-%  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
-%  London, New York (1198), 565pp. With associated web site\\  
-%  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
-%  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.
-
-%\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
-%  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.
-
-%\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
-%  Press, Princeton, N.J., 1946.
-
-%\end{thebibliography}
 \end{document}

### 2019-04-01 paper/paper.tex
Draft

@@
 \usepackage{xcolor}
+\usepackage[all]{xy}
 
@@
 \newcommand{\0}{\textbf{0}} % empty type
-\newcommand{\1}{\textbf{1}} % unit type
+\newcommand{\unitt}{\textbf{1}} % unit type
 \newcommand{\TT}{\constructor{tt}} % element of unit type
@@
 \newcommand{\quotPA}{\mathcal{Q}^{\category{PreAlg}}}
-\newcommand{\pathPA}{\pi^{\category{PreAlg}_0}}
+\newcommand{\pathPA}{\pi^{\category{PreAlg}}_0}
 \newcommand{\quotAA}{\mathcal{Q}^{\category{Alg}}}
@@
 \begin{itemize}
-	\item $\pointc{\modsig} \Def \sumP{\I}{(\C \> \1)}$;
-	\item $\pathI{\modsig} \Def \1$;
+	\item $\pointc{\modsig} \Def \sumP{\I}{(\C \> \unitt)}$;
+	\item $\pathI{\modsig} \Def \unitt$;
 	\item $\pathA{\modsig} \Def \I$;
@@
 
-Intuitively, this signature represents a HIT $H$ with operation $H + \1 \rightarrow H$ representing the successor and zero.
+Intuitively, this signature represents a HIT $H$ with operation $H + \unitt \rightarrow H$ representing the successor and zero.
 Note that the endpoint $\comp{\inle}{\constr}$ takes the successor, so, the equation says that $S(S \> x) = x$ for all $x : X$.
@@
 	\item $\pointc{\trunc} \Def \C \> A$;
-	\item $\pathI{\trunc} \Def \1$;
+	\item $\pathI{\trunc} \Def \unitt$;
 	\item $\pathA{\trunc} \Def \prodP{\I}{\I}$;
@@
 Recall the signature $\modsig$ from Example \ref{ex:modsig}.
-A prealgebra of $\modsig$ consists of a set $X$ and a map $f : X + \1 \rightarrow X$.
+A prealgebra of $\modsig$ consists of a set $X$ and a map $f : X + \unitt \rightarrow X$.
 We define $S_X \> x \Def f(\inl \> x)$ and $Z_X = f(\inr \> \TT)$.
@@
 \end{itemize}
-This gives rise to two natural isomorphisms $n_1 : \nattrans{\compf{\pathF}{\semPT{\pointc{\sig}}}}{\compf{\semP{\pointc{\sig}}}{\pathF}}$
+This gives rise to two natural isomorphisms $n_1^P : \nattrans{\compf{\pathF}{\semPT{P}}}{\compf{\semP{P}}{\pathF}}$ and $n_2 : \nattrans{\compf{\quotF}{\semPT{P}}}{\compf{\semP{P}}{\quotF}}$.
 \end{lemma}
 
-Now we use Lemmata \ref{lem:prealgadj} and \ref{lem:comm} to lift both the quotient and the path setoid functors and we get
+Using Lemmata \ref{lem:prealgadj} and \ref{lem:comm}, we lift lift both the quotient and the path setoid functors to obtain.
 \[
@@
 
+\begin{proposition}
+\label{lem:prealgadjconstr}
+Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $L : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{L}{A_2}}{\compf{A_1}{L}}$.
+In addition, given is a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{L}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
+We also assume the following
+\begin{itemize}
+	\item For each $X : \mathcal{C}$, the following diagram commutes
+	\[
+	\xymatrix
+	{	
+		A_2 (L(R \> X)) \ar[dr]^{\epsilon \> X} \ar[d]_{\theta_1} \\
+		R(L(A_2 \> X)) \ar[r]_{\epsilon(A_2 \> X)} & A_2 \> X
+	}
+	\]
+	where the transformation $\theta_1$ is defined using whiskering, associativity of composition, and $n$ and $m$.
+	\item For each $X : \mathcal{D}$, the following diagram commutes
+	\[
+	\xymatrix
+	{
+		A_1 \> X \ar[dr]_{\eta \> (A_1 \> X)} \ar[r]^{A_1 \> (\eta \> X)} & A_1(R(L \> X)) \ar[d]^{\theta_2}\\
+		& R(L(A_1 \> X))
+	}
+	\]
+	where the transformation $\theta_2$ is defined using whiskering, associativity of composition, and $n$ and $m$.
+\end{itemize}
+With all this, for each $X : \mathcal{D}$ the map $\eta \> X$ is an algebra homomorphism and for each $Y : \mathcal{C}$ the map $\epsilon \> X$ is an algebra homomorphism.
+Furthermore, we have an adjunction $\adj{L^{\category{PreAlg}}}{R^{\category{PreAlg}}}$.
+\end{proposition}
+
+For the verification of the conditions of this proposition for the path setoid and quotient, we refer the reader to the formalization.
+Then we can conclude
+
 \begin{lemma}
+\label{lem:adjprealg}
 We have an adjunction $\adj{\quotPA}{\pathPA}$.
@@
 
-Now we would like to apply this proposition to the adjunction obtained from Lemma \ref{lem:prealgadj}.
+Now we would like to apply this proposition to the adjunction obtained from Lemma \ref{lem:adjprealg}.
+For that, we first need to calculate the action of the endpoints.
+This is done by the following lemma.
+
+\begin{lemma}
+Given is an endpoint $e : \ep{A}{P}{Q}$.
+For every set prealgebra $X$, we have the following equality
+\[
+\compm{\pathF \> (\semE{e} \> X)}{n_1^P \> X} = \compm{n_1^Q \> X}{\semET{e} \> (\pathPA \> X)}.
+\]
+For every setoid prealgebra $X$, we have the following equality.
+\[
+\compm{\quotF \> (\semET{e} \> X)}{n_2^P \> X} = \semE{e} \> (\quotPA \> X).
+\]
+\end{lemma}
+
+Now we obtain the desired adjunction.
 
@@
 \end{theorem}
-
-Now we can lift the quotient and path setoid.
-We can verify the conditions and we get
-
-To show this adjunction lifts to an adjunction between algebras, we need to show that they map algebras to algebras.
-We only show this for the path setoid
-
-\begin{lemma}
-path setoid endpoint
-\end{lemma}
-
-\begin{lemma}
-Path setoid factors through algebras
-\end{lemma}
 

### 2019-04-15 paper/paper.tex
updated

@@
 \newcommand{\transport}[2]{\function{transport}^{#1} \> #2} % transport
-\newcommand{\invP}[1]{(#1)^{-1}} % inverse of a path
+\newcommand{\invP}[1]{#1^{-1}} % inverse of a path
 \newcommand{\classof}{\constructor{class}} % class construcor
@@
 
-\def\lastname{Van der Weide}
+\def\lastname{Van der Weide, Geuvers}
 \begin{document}
@@
   \address{Institute for Computation and Information Sciences\\ Radboud Universiteit\\
-    Nijmegen, The Netherlands} \author{My Co-author\thanksref{coemail}}
-  \address{My Co-author's Department\\My Co-author's University\\
-    My Co-author's City, My Co-author's Country} \thanks[ALL]{We would like to thank Dan Frumin and Andrej Bauer for inspiring discussions.
+  	Nijmegen, The Netherlands}
+  \author{Herman Geuvers\thanksref{coemail}}
+  \address{Institute for Computation and Information Sciences\\ Radboud Universiteit\\
+  	Nijmegen, The Netherlands}
+  \thanks[ALL]{The author would like to thank Dan Frumin and Andrej Bauer for inspiring discussions.
 Work on this article was supported by a grant from the \href{https://eutypes.cs.ru.nl/}{COST Action EUTypes CA15123}.} \thanks[myemail]{Email:
@@
   			nweide@cs.ru.nl}}} \thanks[coemail]{Email:
-    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
-        couserid@codept.coinst.coedu}}}
+  	\href{mailto:herman@cs.ru.nl} {\texttt{\normalshape
+  			herman@cs.ru.nl}}}
 \begin{abstract} 
@@
 The last one, $\modZ$, is the \emph{integers modulo 2} and note that both the point constructor $\SZ$ and path constructor $\modP$ are recursive.
-
+A HIT is called \emph{finitary} if its point constructor is described by a finitary polynomial and it is called \emph{set-truncated} it is a set.
+
+In this paper, we show that all finitary set-truncated HITs can be constructed with quotients and propositional truncations. 
+This briefly means that all higher inductive types exist if a small number of simple ones exist.
+The main idea of the proof is to take advantage that the quotient is left adjoint functor from setoids to sets \cite{RijkeS15}.
+To relate this to HITs, we first define schemes, which are an internalized version of the schema by Basold \etal \ \cite{BasoldGW17}, and categories of algebras on them.
+Then we lift the quotient adjunction to an adjunction from algebras in setoids to algebras in sets.
+Since initiality implies induction, it suffices to construct the initial setoid algebra for which we adapt the construction by Dybjer and Moeneclaey \cite{DybjerM18,moeneclaey2016schema}.
+Note that from our construction we can conclude that all finitary set-truncated HITs can be constructed from non-recursive ones.
+Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction \cite{rijke2017join}.
+
+A similar result was obtained by Kaposi \etal \ \cite{KaposiKA19}, but we do not assume UIP and we use simpler HITs for the construction.
+Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
+Kraus and Von Raumer obtained a similar property for the coequalizer HIT by providing a nicer induction principle for its path types \cite{KrausRaumer}.
+
+\subsection{Background and Related Work}
 HITs have been studied formally and several schemes have already been developed.
@@
 Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}
-while Dybjer and Moenclaey defined a scheme allowing constructors for points, paths, and homotopies, and they give its interpretation in the groupoid model  \cite{DybjerM18,HofmannS94}.
+while Dybjer and Moeneclaey defined a scheme allowing constructors for points, paths, and homotopies, and they give its interpretation in the groupoid model  \cite{DybjerM18,HofmannS94}.
 Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types and proved canonicity \cite{AngiuliHW17,CavalloH19}.
@@
 
-In this paper, we show that all finitary set-truncated HITs can be constructed with quotients and propositional truncations. 
-This briefly means that all higher inductive types exist if a small number of simple ones exist.
-A similar result was obtained by Kaposi \etal \ \cite{KaposiKA19}, but we do not assume UIP and we use simpler HITs for the construction.
-Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
-Kraus and Von Raumer obtained an analogous result for the coequalizer by providing a nicer induction principle for its path types \cite{KrausRaumer}.
-Note that from our construction we can conclude that all finitary set-truncated HITs can be constructed from non-recursive HITs.
-Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction \cite{rijke2017join}.
-
-The main idea of the proof is to take advantage that the quotient is left adjoint functor from setoids to sets \cite{RijkeS15}.
-To relate this to HITs, we first define schemes, which are an internalized version of the schema by Basold \etal \ \cite{BasoldGW17}, and categories of algebras on them.
-Then we lift the quotient adjunction to an adjunction from algebras in setoids and algebras in sets.
-Since initiality implies induction, it suffices to construct the initial setoid algebra for which we adapt the construction by Dybjer and Moenclaey \cite{moeneclaey2016schema,DybjerM18}.
-
-All definitions and proofs in his paper are formalized over the UniMath library \cite{UniMath}.
-The formalization is 4166 lines of code and it can be found on \url{https://github.com/nmvdw/SetHITs}.
-
+\subsection{Overview}
 We start in \Cref{sec:prelim} by recalling some definitions from HoTT and category theory required for the rest of the paper.
@@
 We define the induction principle of HITs via displayed algebras in \Cref{sec:induction} and we show that initial objects satisfy this principle.
-\Cref{sec:construction} is the core of this paper and there we construct an adjunction between algebras in sets and setoids, which we use to construct the initial algebra in sets via the initial algebra in setoids.
+\Cref{sec:construction} contains the main result of this paper and there we construct an adjunction between algebras in sets and setoids, which we use to construct the initial algebra in sets via the initial algebra in setoids.
 We study the consequences of this construction in \Cref{sec:consequences} and in \Cref{sec:conclusion}, we conclude and discuss further work.
+
+All definitions and proofs in his paper are formalized over the UniMath library \cite{UniMath}.
+The formalization is 4166 lines of code and it can be found on \url{https://github.com/nmvdw/SetHITs}.
 
@@
 \label{sec:prelim}
-We start by recalling some definitions and notations from homotopy type theory and category theory \cite{mac2013categories,hottbook}.
+We start by recalling some definitions and notations from homotopy type theory and the basics of category theory in HoTT \cite{AhrensKS15,mac2013categories,hottbook}.
 The first notion we need, is the \emph{dependent equality type}.
@@
 We start by recalling the definition of categories.
-This is almost the same as the usual definition in mathematics, but their is a slight discrepancy between the objects and arrows.
+This is almost the same as the usual definition in mathematics, but there is a slight discrepancy between the objects and arrows.
 While the objects can be any type, the arrows have to form a set.
 Proof relevant equality on arrows would induce the structure of a higher category instead of an ordinary one.
-This leads to the following definition.
 
@@
 	\item a type $\mathcal{C}_0$ of objects;
-	\item for each $X, Y : \mathcal{C}_0$ a set $\mathcal{C}_1(X,Y)$ of morphisms;
+	\item for each $X, Y : \mathcal{C}_0$ a set $X \rightarrow Y$ of morphisms;
 	\item for each $X : \mathcal{C}_0$ a morphisms $\idm{X}$;
-	\item for all objects $X, Y, Z : \mathcal{C}_0$ and morphisms $f : \mathcal{C}_1(X,Y)$ and $g : \mathcal{C}_1(Y,Z)$, a morphism $\compm{f}{g} : \mathcal{C}_1(X,Z)$
+	\item for all objects $X, Y, Z : \mathcal{C}_0$ and morphisms $f : X \rightarrow Y$ and $g : Y \rightarrow Z$, a morphism $\compm{f}{g} : X \rightarrow Z$
 \end{itemize}
@@
 
+Note that in the usual category of setoids, one would take a quotient of the setoid morphisms.
+However, in our construction, we do not need any additional equality and thus we just use ordinary equality.
+
 If $X$ is a set and $R$ is an equivalence relation on $X$, then we write $(X, R)$ for the setoid with this data.
-When it is clear from the context, we write $\equiv$ for the relation.
+When it is clear from the context, we write $x \equiv y$ for $R \> x \> y$.
 We finish this section by giving some operations of functor and natural transformations, which we need later.
-Functors and transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and natural transformations from $\mathcal{F}$ to $\mathcal{G}$ respectively.
+Functors and natural transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and transformations from $\mathcal{F}$ to $\mathcal{G}$ respectively.
 
@@
 	\item If $\mathcal{D}$ has binary products, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a product $\prodf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
-	\item If $\mathcal{D}$ has binary sum, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a sum $\sumf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
+	\item If $\mathcal{D}$ has binary sums, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a sum $\sumf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
 	\item For each object $X : \mathcal{D}$, we have a constant functor $\Cf{X} : \functor{\mathcal{C}}{\mathcal{D}}$.
@@
 \label{def:nattrans}
-We have the following transformations.
+We have the following natural transformations.
 \begin{itemize}
@@
 In the next section, we show that each code $P : \poly$ gives rise to a functor $\semP{P} : \functor{\hset}{\hset}$.
-A higher inductive type $H$ should have a constructor $\semP{P} \> H \rightarrow H$, which represents the introduction rule for points.
+A higher inductive type $H$ should have a point constructor $c : \semP{P} \> H \rightarrow H$, which represents the introduction rule for points.
 
 HITs also have an introduction rule for paths, and for those, we need to give the possible endpoints of paths.
-Note that in the equations the point constructor can be used, and thus the type of endpoint must depend on the data of the point constructor.
-Since each equation is universally quantified, we also have to indicate the source of the arguments, which again depends polynomially on the HIT being defined.
-In addition, we allow each equation to have a target also depending polynomially on the HIT.
-We define the type of endpoints again as an inductive type.
+Each path is given a universally quantified equation, which can possibly make use of the point constructor.
+For this reason, the type of endpoint must depend on the data of the point constructor.
+We also indicate the source and target of the equation, and both of them depend polynomially on the HIT being defined.
+The type of endpoints is defined as an inductive type.
 
@@
 The polynomials $P$ and $Q$ represent the source and target of the equation respectively.
-If we have a set $X$ with a map $c : \semP{A} \> X \rightarrow X$, each endpoint $e : \ep{A}{P}{Q}$ gives rise to a natural map $\semP{P} \> X \rightarrow \semP{Q} \> X$ where $\constr$ is interpreted with $c$.
+If we have a set $X$ with a map $c : \semP{A} \> X \rightarrow X$, each endpoint $e : \ep{A}{P}{Q}$ gives rise to a natural map $\semP{P} \> X \rightarrow \semP{Q} \> X$ where $\constr$ is interpreted by $c$.
 These maps are the left- and right-hand side of  the equations.
@@
 	\item A family $\pathA{\sig} : \pathI{\sig} \rightarrow \poly$ representing the source of the paths;
-	\item Maps $\pathlh{\sig}, \pathrh{\sig} : \deprod{j}{\pathA{\sig}}{\ep{\pointc{\sig}}{\pathA{\sig} \> j}{I}}$ representing the left- and right-hand side of the equations.
+	\item Maps $\pathlh{\sig}, \pathrh{\sig} : \deprod{j}{\pathA{\sig}}{\ep{\pointc{\sig}}{\pathA{\sig} \> j}{\I}}$ representing the left- and right-hand side of the equations.
 \end{itemize}
@@
 Inductive $H$ :=
-| $c$ : $\pointc{\sig} \> H \rightarrow H$
-| $p$ : $\deprod{j}{\pathI{\sig}}{\deprod{x}{\pathA{\sig} \> H}{\pathlh{\sig} \> j \> x = \pathrh{\sig} \> j \> x}}$
+| $c$ : $\semP{\pointc{\sig}} \> H \rightarrow H$
+| $p$ : $\deprod{j}{\pathI{\sig}}{\deprod{x}{\semP{\pathA{\sig}} \> H}{\semE{\pathlh{\sig} \> j} \> H \> x = \semE{\pathrh{\sig} \> j} \> H \> x}}$
 \end{lstlisting}
@@
 Note that the endpoint $\comp{\inle}{\constr}$ takes the successor, so, the equation says that $S(S \> x) = x$ for all $x : X$.
-Similarly, one can define signatures for groups or join semi-lattices.
+Signatures for groups and join semi-lattices are defined similarly.
 Since signatures can depend on types, we can also define the propositional truncation.
@@
 \end{example}
-This signature represents a HIT $H$ with a map $A \rightarrow H$ and for which all inhabitants are equal.
+
+This signature represents a HIT $H$ with a map $A \rightarrow H$ and for which all inhabitants are equal, which is precisely the propositional truncation from Definition \ref{def:trunc} for sets $A$.
 
@@
 Now we know what signatures are, the next goal is to define HITs for signatures.
-For that we need to give its introduction, elimination, and computation rules.
+For that we need to give the required introduction, elimination, and computation rules.
 In this section, we study the introduction rule of HITs and we do that by defining a category of algebras on a polynomial.
@@
 Since the objects do not satisfy the equations in $\sig$, we call this the category of \emph{prealgebras}.
-To obtain actual algebras of $\sig$, we need to interpret the equations and for that, we first need to interpret endpoints.
-These are interpreted as natural transformations, which are constructed using the transformations from \Cref{sec:prelim}.
-Beside those, we use for each polynomial $P$ the transformation $\constrt{P} : \nattrans{\comp{\forget{P}}{\semP{P}}}{\comp{\forget{P}}{\semP{\I}}}$ whose  components are given by the prealgebra map.
+To obtain actual algebras of $\sig$, we need to interpret the equations.
+For that, we first give a semantics of endpoints as natural transformations, which are defined using the transformations from Lemma \ref{def:nattrans}.
+Besides, we use for each polynomial $P$ the transformation $\constrt{P} : \nattrans{\compf{\forget{P}}{\semP{P}}}{\compf{\forget{P}}{\semP{\I}}}$ whose  components are given by the prealgebra map.
 
@@
 Now we have everything in place to define algebras on $\sig$.
-An algebra on $\sig$ consists of a carrier together with an operation which satisfies the equations specified by $\sig$.
-For the operation, we use $\prealg{\pointc{\sig}}$.
+An algebra on $\sig$ consists of a prealgebra together with proofs that the equations in $\sig$ are satisfied.
 Since the carrier of each prealgebra is a set, the equations form a proposition.
@@
 To define the action of polynomials on equivalence relations, we need some preliminary operations.
-For a set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y = (x = y)$.
+For a set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y \Def x = y$.
 Furthermore, given types $X$ and $Y$ with equivalence relations $R_X$ and $R_Y$ on them, we can define equivalence relations $\sumR{R_X}{R_Y}$ and $\prodR{R_X}{R_Y}$ on $X + Y$ and $X \times Y$ respectively.
@@
 
-Again this gives rise to a category $\prealgst{\sig}$ of \emph{setoid prealgebras on $\sig$}.
-To define algebras on $\sig$, we also need to interpret endpoints.
-However, these are just setoid morphisms instead of natural transformations.
+This gives rise to a category $\prealgst{\sig}$ of \emph{setoid prealgebras on $\sig$}.
+To define algebras on $\sig$, we also need to interpret endpoints for which we use setoid morphisms instead of natural transformations.
 
@@
 The category of algebras on $\sig$ is defined differently for setoids than for sets.
-While for sets, the equations of algebras are witnessed by actual equalities, but for setoids, the equations are witnessed by the equivalence relation.
+While for sets, the equations of algebras are witnessed by actual equalities, the equations for setoids are witnessed by the equivalence relation.
 Note that such relations are families of propositions meaning again this gives rise to a proposition and thus we define it as a full subcategory.
@@
 Let $Y$ be a displayed algebra over $X$.
-Then a displayed algebra map to $Y$ consists of a map $f : \deprod{x}{X}{Y \> x}$ such that for each $x : \semP{\pointc{\sig}}{X}$, we have $f(\constrA{X} \> x) = c_Y \> x \> (\polydmap{\pointc{\sig}}{f} \> x)$.
+Then a \emph{displayed algebra map} to $Y$ consists of a map $f : \deprod{x}{X}{Y \> x}$ such that for each $x : \semP{\pointc{\sig}}{X}$, we have $f(\constrA{X} \> x) = c_Y \> x \> (\polydmap{\pointc{\sig}}{f} \> x)$.
 \end{definition}
@@
 
+Note that HITs of $\sig$ satisfy analogous rules to those defined by Basold \etal \ \cite{BasoldGW17}.
+The algebra structure gives the right introduction rules and the existence of the displayed algebra map gives the required elimination and computation rules.
+
 \subsection{Obtaining Induction from Initiality}
-The goal of this section is to obtain the induction principle from initiality.
-This way it suffices construct an initial object of the signature to obtain a HIT.
+Next we show how to obtain the induction principle from initiality.
+This way it suffices construct an initial object of the signature to obtain a HIT, which is more convenient in category theory.
 To this end, we first define the total algebra $\total{Y}$ of a displayed $Y$ on $X$ together a projection $\proj{Y}$ to $X$.
-Then we show that induction can be obtained by finding a section of the projection.
-Since this is always possible if $X$ is initial, we conclude by saying that initial objects satisfy the induction principle.
 
@@
 To show this is an algebra, we first need to define a map $c_{\total{Y}} : \semP{\pointc{\sig}} \> (\total{Y}) \rightarrow \total{Y}$.
-The main idea is that we use the algebra map of $X$ for the first component and the algebra map of $Y$ for the second one.
+The main idea is that we use the algebra map of $X$ for the first component and the displayed algebra map of $Y$ for the second one.
 We introduce an intermediate definition, which allows us to access the right data.
@@
 	\item $\Ppr{\I} \> x \Def \prr \> x$;
-	\item $\Ppr{\sumP{P}{Q}} \> (\inl x) \Def \Ppr{P} \> x$;
-	\item $\Ppr{\sumP{P}{Q}} \> (\inr x) \Def \Ppr{Q} \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inl \> x) \Def \Ppr{P} \> x$;
+	\item $\Ppr{\sumP{P}{Q}} \> (\inr \> x) \Def \Ppr{Q} \> x$;
 	\item $\Ppr{\prodP{P}{Q}} \> x \Def (\Ppr{P} \> x , \Ppr{Q} \> (\prr \> x))$.
@@
 \]
+Here $\invP{p}$ denotes the inverse of the path $p$.
 \end{lemma}
@@
 Now suppose $X$ is an initial object in the category of algebras.
-Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because initiality ensures uniqueness of homomorphisms from $X$ to $X$.
+Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because initiality ensures uniqueness of homomorphisms.
 Hence, we conclude
@@
 The right adjoint is the path setoid functor $\pathF : \functor{\hset}{\setoids}$.
-For sets $X$, we define functor $\pathF \> X$ to be $(X, =_X)$ where $=_X$ is the equivalence relation on $X$ defined by $\lambda x y, x = y$.
+For sets $X$, we define functor $\pathF \> X$ to be $(X, \pathR{X})$.
 Note that this action is functorial and that this gives rise to an adjunction.
@@
 For algebras $(X, f) : \falg{A_1}$, we define $F^{\category{PreAlg}}(X,f) = (F \> X, \compm{F \> f}{n \> X})$.
+To lift the quotient and the path setoid, we need a lemma.
 
@@
 
-Using Lemmata \ref{lem:prealgadj} and \ref{lem:comm}, we lift lift both the quotient and the path setoid functors to obtain.
+Using Lemmata \ref{lem:prealgadj} and \ref{lem:comm}, we lift both the quotient and the path setoid functors to obtain.
 \[
@@
 \]
+This gives the required functors for the adjunction on the level of algebras, and the next step is to obtain the new unit and counit.
+The main idea is to show that the unit and counit are algebra homormophisms.
 
@@
 Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $L : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{L}{A_2}}{\compf{A_1}{L}}$.
-In addition, given is a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{L}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
-We also assume the following
-\begin{itemize}
-	\item For each $X : \mathcal{C}$, the following diagram commutes
+In addition, suppose we a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{L}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
+We also assume that for each $X : \mathcal{C}$ and $Y : \mathcal{D}$ the following diagrams commute
 \[
@@
 {	
-		A_2 (L(R \> X)) \ar[dr]^{\epsilon \> X} \ar[d]_{\theta_1} \\
-		R(L(A_2 \> X)) \ar[r]_{\epsilon(A_2 \> X)} & A_2 \> X
+	A_2 (L(R \> X)) \ar[ddrr]^{\epsilon \> X} \ar[d]_{n(R \> X)} \\
+	L(A_2(R \> X)) \ar[d]_{L(m \> X} \\
+	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_2 \> X)} & & A_2 \> X
 }
-	\]
-	where the transformation $\theta_1$ is defined using whiskering, associativity of composition, and $n$ and $m$.
-	\item For each $X : \mathcal{D}$, the following diagram commutes
-	\[
+\quad \quad \quad
 \xymatrix
 {
-		A_1 \> X \ar[dr]_{\eta \> (A_1 \> X)} \ar[r]^{A_1 \> (\eta \> X)} & A_1(R(L \> X)) \ar[d]^{\theta_2}\\
-		& R(L(A_1 \> X))
+	A_1 \> Y \ar[ddrr]_{\eta \> (A_1 \> X)} \ar[rr]^-{A_1 \> (\eta \> Y)} & & A_1(R(L \> Y)) \ar[d]^{m(L \> X)}\\
+	& & R(A_1(L \> X)) \ar[d]^{R(n \> X)}\\
+	& & R(L(A_1 \> Y))
 }
 \]
-	where the transformation $\theta_2$ is defined using whiskering, associativity of composition, and $n$ and $m$.
-\end{itemize}
-With all this, for each $X : \mathcal{D}$ the map $\eta \> X$ is an algebra homomorphism and for each $Y : \mathcal{C}$ the map $\epsilon \> X$ is an algebra homomorphism.
+Then the maps $\varepsilon \> X$ and $\eta \> Y$ are algebra homomorphisms for each $X : \mathcal{C}$ and $Y : \mathcal{D}$.
 Furthermore, we have an adjunction $\adj{L^{\category{PreAlg}}}{R^{\category{PreAlg}}}$.
@@
 
-Now we obtain the desired adjunction.
+For the quotient, a similar lemma is required and for its precise formulation, we refer the reader the formalization.
+With all this in place, we obtain the desired adjunction.
 
@@
 We denote the initial object of this category by $(\CRC , f)$.
-The carrier of the desired setoid is $\CRC$ meaning that the next step is to define the equivalence relation on $\CRC$.
-
-The main difficulty of defining this relation, is that we also must behave correctly on $\semP{\pointc{\sig}}{\CRC}$, because otherwise, we would not be able to lift $f$ to a setoid morphism.
-For that reason, we first define a relation $\CR \> P$ on $\semP{P} \> \CRC$ for each $P : \poly$..
-
+The carrier of the desired setoid is $\CRC$ and the next step is to define the equivalence relation on $\CRC$.
+
+The main difficulty of defining this relation, is that we need to be able to lift $f$ to a setoid morphism meaning that $\semP{\pointc{\sig}}{\CRC}$ must be defined correctly.
+For that reason, we first define a relation on $\semP{P} \> \CRC$ for $P : \poly$.
+
+\begin{definition}
+Given is $P : \poly$.
+The relation $\CR \> P$ on $\semP{P} \> \CRC$ is inductively generated by the constructors
 \begin{center}
@@
 \AxiomC{$x : \semP{\pathA{\sig} \> j} \> \CRC$}
-\BinaryInfC{$\CRpath \> j \> x : \CR \> (\semE{\pathlh{\sig} \> j} \> \CRC \> x) \> (\semE{\pathrh{\sig} \> j} \> \CRC \> x)$}
-\end{bprooftree}
-\begin{bprooftree}
-\AxiomC{$r : \CR \> (\pointc{\sig}) \> x \> y$}
+\BinaryInfC{$\CRpath \> j \> x : \CR \> \I \> (\semE{\pathlh{\sig} \> j} \> \CRC \> x) \> (\semE{\pathrh{\sig} \> j} \> \CRC \> x)$}
+\end{bprooftree}
+\begin{bprooftree}
+\AxiomC{$r : \CR \> \pointc{\sig} \> x \> y$}
 \UnaryInfC{$\CRcong \> r : \CR \> \I \> (f \> x) \> (f \> y)$}
@@
 \end{center}
+\end{definition}
 
 Now we define a relation on $\CRC$ by $\CRR \> x \> y = \trunct{\CR \> \I \> x \> y}$.
-Because of the truncation, it takes value in proposition.
+Because of the truncation, each $\CRR \> x \> y$ is a proposition.
 Note that $\CRR$ is an equivalence relation, because of the constructor $\CRrefl$, $\CRsym$, and $\CRtrans$.
-In addition, all equations in $\sig$ are identified in $\CRR$, because of the constructor $\CRpath$.
-Lastly, with the constructors $\CRinl$, $\CRinr$, and $\CRcong$, we can show that $\CRR$ preserves $f$.
+In addition, all equations in $\sig$ are validated in $\CRR$ by $\CRpath$.
+Finally, with the constructors $\CRpair$, $\CRinl$, $\CRinr$, and $\CRcong$, we can show that $\CRR$ preserves $f$.
 Hence, we obtain a setoid $I \Def (\CR, \CRC)$ together with a setoid morphism $\varphi : \semPT{P} \> I \rightarrow I$.
@@
 \label{thm:hit-exist}
-For each signature $\sig$, we can construct a HIT on $\sig$.
+For each signature $\sig$, there is a HIT on $\sig$.
 \end{corollary}
@@
 Let $X$ and $Y$ be algebras on $\sig$.
-Then there is a displayed algebra $\constdisp{Y}$ on $X$ of which the underlying type family is $Y$ on each point of $X$.
+Then there is a displayed algebra $\constdisp \> Y$ on $X$ of which the underlying type family is $Y$ on each point of $X$.
 \end{lemma}
@@
 Let $X$ be $Y$ be algebras on $\sig$.
-If we have a displayed algebra map from $X$ to $\constdisp{Y}$, then we have an algebra homomorphism from $X$ to $Y$.
+If we have a displayed algebra map from $X$ to $\constdisp \> Y$, then we have an algebra homomorphism from $X$ to $Y$.
 \end{lemma}
@@
 Let $\sig$ be a signature.
-Then for each $x, y : \CR$ we have an equivalence $\CRR \> x \> y \weq \classof \> x = \classof \> y$.
+Then for each $x, y : \CRC$ we have an equivalence $\CRR \> x \> y \weq \classof \> x = \classof \> y$.
 \end{corollary}
@@
 \label{sec:conclusion}
-We showed how to construct finitary set-truncated higher inductive types using the quotient and propositional truncation in Theorem \ref{thm:hit-exist}.
+We have shown how to construct finitary set-truncated higher inductive types using the quotient and propositional truncation in Theorem \ref{thm:hit-exist}.
 Since truncations and the quotient can be constructed from nonrecursive HITs, this proves that all finitary set-truncated HITs can be constructed from nonrecursive ones.
@@
 A first step towards that goal, would be adapting this construction to bicategory theory \cite{ahrens2019bicategories,capriotti2017univalent} and constructing higher inductive 1-types using Dybjer's and Moeneclaey's interpretation of such HITs in groupoids \cite{DybjerM18}.
-Doing so, would require interpreting the path constructor terms and the path computation rule becomes relevant.
-Proving the induction principle from initiality is more difficult then, because equality becomes proof relevant.
+Doing so, would require interpreting the endpoints of homotopies.
+In addition, the path computation rules become relevant.
+Proving the induction principle from initiality is more difficult then, because equality becomes proof relevant giving nontrivial transports.
 In this setting, Corollary \ref{cor:hit_path} is more interesting, because the computation rules of path constructors become nontrivial.
@@
 	\emph{{Bicategories in Univalent Foundations}}, arXiv preprint
-	arXiv:1903.01152 (2019).
+	arXiv:1903.01152 (2019), To Appear in FSCD 2019.
 

### 2019-05-01 paper/paper.tex
Added reference, fixed typos

@@
 
-\usepackage{cleveref}
 \usepackage{entcsmacro}
@@
 \usepackage{amsmath}
+\usepackage{cleveref}
 \usepackage{bussproofs}
@@
 With this adjunction in place, our first step is to lift it to the level of prealgebras.
+For this, we use a result from Hermida and Jacobs \cite{hermida1998structural}.
 The first step, is to lift the functors for which we use the following lemma.
@@
 Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $L : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{L}{A_2}}{\compf{A_1}{L}}$.
-In addition, suppose we a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{L}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
+In addition, suppose we a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{R}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
 We also assume that for each $X : \mathcal{C}$ and $Y : \mathcal{D}$ the following diagrams commute
@@
 	A_2 (L(R \> X)) \ar[ddrr]^{\epsilon \> X} \ar[d]_{n(R \> X)} \\
-	L(A_2(R \> X)) \ar[d]_{L(m \> X} \\
+	L(A_2(R \> X)) \ar[d]_{L(m \> X)} \\
 	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_2 \> X)} & & A_2 \> X
@@
 
+	\bibitem{hermida1998structural}
+	C.~Hermida and B.~Jacobs.
+	\newblock Structural induction and coinduction in a fibrational setting.
+	\newblock {\em Information and computation}, 145(2):107--152, 1998.
+
 	\bibitem{HofmannS94}

### 2019-05-16 paper/paper.tex
Additions

@@
 
-\newcommand{\remove}{} % remove a part
+\newcommand{\remove}[1]{} % remove a part
 
@@
 \begin{abstract} 
-  We construct finitary set-truncated higher inductive types (HITs) using quotients and the propositional truncation.
-  Using a modification of the schema by Basold \etal, we define a notion of signatures and univalent categories of algebras in both sets and setoids.
-  To interpret HITs, we use initial algebra semantics for which we show that the initiality implies induction.
+  We construct finitary set-truncated higher inductive types (HITs) from quotients and the propositional truncation.
+  For that, we first define signatures as a modification of the schema by Basold \etal, and we show they give rise to univalent categories of algebras in both sets and setoids.
+  To interpret HITs, we use the well-known method of initial algebra semantics.
   The desired algebra is obtained by lifting the quotient adjunction to the level of algebras and adapting Dybjer's and Moeneclaey's interpretation of HITs in setoids.
@@
 Homotopy type theory (HoTT) is a form of intensional type theory. 
-It has semantics in the simplicial sets model \cite{simpset}, and types represent spaces, terms represent points, and equalities represent paths.
+It has semantics in the simplicial sets model \cite{simpset}, and types represent spaces, terms represent points, and equalities represent paths, and so on.
 Furthermore, equality is proof relevant and we frequently talk about homotopies: paths between paths.
@@
 synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.
-To get a feeling for what HITs are, let us look a some examples.
+To get a feeling for what HITs are, let us look at some examples.
 
@@
 Inductive $\modZ$ :=
-| $\ZZ$ : $\modZ \rightarrow \modZ$
+| $\ZZ$ : $\modZ$
 | $\SZ$ : $\modZ \rightarrow \modZ$
@@
 \subsection{Overview}
-We start in \Cref{sec:prelim} by recalling some definitions from HoTT and category theory required for the rest of the paper.
+We start in \Cref{sec:prelim} by recalling some definitions from HoTT and category theory required for the remainder of the paper.
 In \Cref{sec:signature}, we define signatures for higher inductive types and give a couple of examples.
@@
 We define the induction principle of HITs via displayed algebras in \Cref{sec:induction} and we show that initial objects satisfy this principle.
-\Cref{sec:construction} contains the main result of this paper and there we construct an adjunction between algebras in sets and setoids, which we use to construct the initial algebra in sets via the initial algebra in setoids.
+\Cref{sec:construction} contains the main result of this paper and there we construct an adjunction between algebras in sets and setoids, and we use it to construct the initial algebra in sets via the initial algebra in setoids.
 We study the consequences of this construction in \Cref{sec:consequences} and in \Cref{sec:conclusion}, we conclude and discuss further work.
 
-All definitions and proofs in his paper are formalized over the UniMath library \cite{UniMath}.
-The formalization is 4166 lines of code and it can be found on \url{https://github.com/nmvdw/SetHITs}.
+All material in this paper are formalized over the UniMath library \cite{UniMath}.
+The formalization is 4166 lines of code and, together with additional examples, it can be found on \url{https://github.com/nmvdw/SetHITs}.
 
@@
 \label{def:depeq}
-Given a type $X$, inhabitants $x, y : X$, a type family $Y$ on $X$, and a path $p : x = y$, we define
-\[
-\transport{Y}{p} : Y \> x \rightarrow Y \> y.
-\]
-Given a path $p : x = y$ and inhabitants $z_1 : Y \> x$ and $z_2 : Y \> y$, we write $\depeq{p}{z_1}{z_2}$ for $\transport{Y}{p} \ z_1 = z_2$.
+Given a type $X$, inhabitants $x, y : X$, a type family $Y$ on $X$, and a path $p : x = y$, we define by path induction a function $\transport{Y}{p} : Y \> x \rightarrow Y \> y$, which is the identity function for the reflexivity path.
+If we have a path $p : x = y$ and inhabitants $z_1 : Y \> x$ and $z_2 : Y \> y$, we write $\depeq{p}{z_1}{z_2}$ for $\transport{Y}{p} \ z_1 = z_2$.
 \end{definition}
@@
 \label{def:cat}
+A \emph{category} $\mathcal{C}$ consists of a type $\mathcal{C}_0$ of objects and a set $X \rightarrow Y$ of morphisms for each $X, Y : \mathcal{C}_0$ together with identity morphisms $\idm{X} : X \rightarrow X$ for each $X : \mathcal{C}_0$ and a compositions $\compm{f}{g} : X \rightarrow Z$ for all mophisms $f : X \rightarrow Y$ and $g : Y \rightarrow Z$ such that the usual associativity and identity laws holds.
+\end{definition}
+
+\remove{
+\begin{definition}
 A \emph{category} $\mathcal{C}$ consists of
@@
 \end{definition}
+}
 
@@
 For the definition of equivalence of equivalences, we refer the reader to the literature \cite{hottbook}.
-More precisely, we define them as follows.
+More precisely, we define
 
@@
 
-The primary example of a univalent category is the category $\hset$ of sets and functions between them.
+The primary example of a univalent category is $\hset$, whose objects are sets and morphisms are functions.
 Another example of a univalent category which we use frequently, is the category of \emph{setoids}.
@@
 \label{def:setoid}
+A \emph{setoid} is a set $X$ together with an equivalence relation on $X$.
+A \emph{setoid morphism} between two setoids  is a map between the underlying sets which preserves the equivalence relation.
+The \emph{category of setoids} $\setoids$ is the category with setoids and setoid morphisms as objects and morphisms.
+\end{definition}
+
+\remove{
+\begin{definition}
 We define
@@
 \end{definition}
+}
 
 Note that in the usual category of setoids, one would take a quotient of the setoid morphisms.
-However, in our construction, we do not need any additional equality and thus we just use ordinary equality.
+However, in our construction, we do not need any additional equality and so, we just use the ordinary one.
 
 If $X$ is a set and $R$ is an equivalence relation on $X$, then we write $(X, R)$ for the setoid with this data.
-When it is clear from the context, we write $x \equiv y$ for $R \> x \> y$.
-We finish this section by giving some operations of functor and natural transformations, which we need later.
-Functors and natural transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and transformations from $\mathcal{F}$ to $\mathcal{G}$ respectively.
+If no confusion arises, we write $x \equiv y$ for $R \> x \> y$.
+We finish this section by giving some operations of functors and natural transformations, which we need later.
+Functors and natural transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and transformations from $F$ to $G$ respectively.
 

### 2021-11-17 paper/paper.tex

@@
 \newcommand{\constr}{\constructor{constr}} % constructor endpoint
+\newcommand{\fmap}{\constructor{fmap}} % function endpoint
 
@@
 \newcommand{\prealg}[1]{\category{PreAlg}_{\hset}(#1)} % category of prealgebras
-\newcommand{\forget}[1]{\mathcal{F}_{#1}} % forgetful functor
+\newcommand{\forget}[1]{\functortxt{U}_{#1}} % forgetful functor
 \newcommand{\semE}[1]{\llbracket #1 \rrbracket} % semantics of endpoints
@@
 \newcommand{\Alg}[1]{\category{Alg}_{\hset}(#1)} % category of algebras
-\newcommand{\constrA}[1]{\function{map}_{#1}} % point constructor of algebra
+\newcommand{\constrA}[1]{\function{point}_{#1}} % point constructor of algebra
 \newcommand{\constrP}[1]{\function{path}_{#1}} % path constructor of algebra
@@
 \newcommand{\modP}{\constructor{mod}} % n = n + 2
+\newcommand{\setZ}{\constructor{Ztrunc}} % mod 2 is a set
 \newcommand{\HIT}{\function{HIT}} % the HIT of a signature
@@
   	Nijmegen, The Netherlands}
-  \thanks[ALL]{The author would like to thank Dan Frumin and Andrej Bauer for inspiring discussions.
+  \thanks[ALL]{The authors would like to thank Dan Frumin and Andrej Bauer for inspiring discussions.
+The authors also thank the reviewers for their helpful comments to improve the readability of this paper.
 Work on this article was supported by a grant from the \href{https://eutypes.cs.ru.nl/}{COST Action EUTypes CA15123}.} \thanks[myemail]{Email:
@@
 
-One of the main features of HoTT, is higher inductive types (HITs) \cite{hottbook}.
+One of the main features of HoTT is higher inductive types (HITs) \cite{hottbook}.
 These are types generated by constructors for their points, paths, homotopies, and so on.
-HITs have been used in numerous applications among which are homotopical patch theory \cite{AngiuliMLH16}.
-synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.
+HITs have been used in numerous applications among which are homotopical patch theory \cite{AngiuliMLH16}, synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16,DBLP:journals/lmcs/AltenkirchK17}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.
 To get a feeling for what HITs are, let us look at some examples.
@@
 | $\modP$ : $\deprod{x}{\modZ}{\SZ(\SZ \> x) = x}$
+| $\setZ$ : $\isaset{\modZ}$
 \end{lstlisting}
@@
 It has a point $\base$ and a path $\loopS : \base = \base$.
-Since neither the point nor path constructors uses arguments from $\Circ$, this HIT is \emph{nonrecursive}.
+Since neither the point nor path constructors uses arguments from $\Circ$, this HIT is \emph{non-recursive}.
 The second, $\trunct{A}$, is the \emph{propositional truncation} of $A$.
@@
 The last one, $\modZ$, is the \emph{integers modulo 2} and note that both the point constructor $\SZ$ and path constructor $\modP$ are recursive.
-A HIT is called \emph{finitary} if its point constructor is described by a finitary polynomial and it is called \emph{set-truncated} it is a set.
+A HIT is called \emph{finitary} if its point constructor is described by a finitary polynomial and it is called \emph{set-truncated} if it is a set.
 
@@
 
-A similar result was obtained by Kaposi \etal \ \cite{KaposiKA19}, but we do not assume UIP and we use simpler HITs for the construction.
-Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
-Kraus and Von Raumer obtained a similar property for the coequalizer HIT by providing a nicer induction principle for its path types \cite{KrausRaumer}.
-
 \subsection{Background and Related Work}
-HITs have been studied formally and several schemes have already been developed.
-Awodey \etal \ showed that the rules of inductive types \cite{dybjer1994inductive} in HoTT are equivalent to being a homotopy initial algebra \cite{AwodeyGS12}.
-They extended this result to a class of HITs called \emph{W-suspensions} \cite{Sojakova15}.
-Another scheme, quotient inductive-inductive types (QIITs), was defined semantically by Altenkirch \etal \ and they show initial algebras are QIITs \cite{AltenkirchCDKF18}.
-Assuming UIP, Kaposi \etal \ constructed finitary QIITs as the syntax of a domain specific type theory \cite{KaposiKA19}, and they extended this scheme to higher inductive-inductive types \cite{KaposiK18}.
-Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}
-while Dybjer and Moeneclaey defined a scheme allowing constructors for points, paths, and homotopies, and they give its interpretation in the groupoid model  \cite{DybjerM18,HofmannS94}.
-Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types and proved canonicity \cite{AngiuliHW17,CavalloH19}.
-
-Furthermore, the semantics of HITs also has been studied.
-Coquand \etal \ provide the semantics of various higher inductive types, such as spheres, the torus, the truncation, and the pushout, in cubical type theory \cite{BezemCH13,CohenCHM16,CoquandHM18}.
+The HITs we study in this paper, are set-truncated and recursion is allowed for both the point and path constructors.
+It is a variation of the scheme by Basold \etal \ \cite{BasoldGW17}, which does not allow constructors for higher paths.
+Other schemata of higher inductive types have already been defined.
+\emph{W-suspensions}, developed by Sojakova \cite{Sojakova15}, allow defining HITs without recursive constructors, but these are not necessarily truncated.
+The scheme by Dybjer and Moenclaey is similar to the one by Basold \etal, as it allows recursion for both the points and paths, but in addition, it supports constructors for homotopies.
+Since types are $\omega$-groupoids \cite{van2011types,lumsdaine2009weak}, a type-theoretical version of these also provide a semantic specification of HITs \cite{DBLP:conf/tlca/HirschowitzHT15}.
+At the moment, the definition which encompasses all these options, are higher inductive-inductive types (HIITs) \cite{KaposiK18} where induction-induction and paths in arbitrary dimensions are permitted.
+These are a generalization of quotient inductive-inductive types (QIITs) developed by Altenkirch \etal \ \cite{AltenkirchCDKF18}.
+Furthermore, Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types \cite{AngiuliHW17,CavalloH19}.
+
+In addition to the schemata, some meta theory also has been developed.
+Here we internally provide initial algebra semantics for our scheme meaning that we show initial implies induction.
+Awodey \etal \ showed a stronger result for inductive types in intensional type theory \cite{AwodeyGS12,dybjer1994inductive}, namely that initiality is equivalent to induction, and Sojakova proved this for W-suspensions \cite{Sojakova15}.
+For QIITs, initial algebra semantics has also been given \cite{AltenkirchCDKF18}.
+Beside initial algebra semantics, Cavallo and Harper shows that computational cubical type theory, with cubical inductive types, satisfies canonicity \cite{AngiuliHW17,CavalloH19}.
+
+The main result of this paper is about constructing a class of higher inductive types from simple ones.
+Both Kraus and Van Doorn show that the propositional truncation can be constructed from non-recursive HITs \cite{Kraus16,Doorn16} and Rijke shows that every truncation can be constructed via non-recursive HITs \cite{rijke2017join}.
+Note that these all are about truncations instead of a more general scheme.
+However, contrary to our result, they do not rely on the restriction to set-truncated types.
+Kaposi \etal \ \cite{KaposiKA19} show that can finitary QIITs can be constructed from one specific QIIT, but their construction relies on UIP.
+From our construction, we deduce that the path space of each HIT is freely generated.
+Kraus and Von Raumer obtained a similar property for the coequalizer by providing a nicer induction principle for its path types \cite{KrausRaumer}.
+
+Reducing the existence of HITs to the existence of a small number of them, gives an approach to defining the semantics of HITs.
+Other approaches to this problem have also been considered.
+Coquand \etal \ interpret various higher inductive types, such as spheres, the torus, the truncation, and the pushout, in cubical type theory \cite{BezemCH13,CohenCHM16,CoquandHM18}.
+All of these examples are not set-truncated and thus not covered by our scheme.
 On the other hand, Lumsdaine and Shulman also study the semantics of higher inductive types using a semantic scheme (cell monads with parameters) and they prove existence in sufficiently nice Quillen model categories \cite{lumsdaine2017semantics}.
-Some recursive higher inductive types can be constructed from nonrecursive HITs.
-Both Kraus and Van Doorn show that the propositional truncation can be constructed from non-recursive HITs \cite{Kraus16,Doorn16} and Rijke shows that every truncation can be constructed via non-recursive HITs \cite{rijke2017join}.
+Dybjer and Moeneclaey give an interpretation of their scheme in the groupoid model \cite{DybjerM18,HofmannS94}.
 
@@
 All material in this paper are formalized over the UniMath library \cite{UniMath}.
-The formalization is 4166 lines of code and, together with additional examples, it can be found on \url{https://github.com/nmvdw/SetHITs}.
+The proof of the main theorem is 4060 lines of code and the additional examples are 3278 lines of code.
+The formalization can be found on \url{https://github.com/nmvdw/SetHITs}.
 
@@
 A \emph{setoid morphism} between two setoids  is a map between the underlying sets which preserves the equivalence relation.
-The \emph{category of setoids} $\setoids$ is the category with setoids and setoid morphisms as objects and morphisms.
+The \emph{category $\setoids$ of setoids} is the category with setoids and setoid morphisms as objects and morphisms.
 \end{definition}
@@
 
+Recall that, If $R$ is an equivalence relation on $X$, each $R \> x \> y$ has to be a proposition.
 Note that in the usual category of setoids, one would take a quotient of the setoid morphisms.
-However, in our construction, we do not need any additional equality and so, we just use the ordinary one.
-
+However, we refrain to do so, because in our construction, we do not need any additional equality.
 If $X$ is a set and $R$ is an equivalence relation on $X$, then we write $(X, R)$ for the setoid with this data.
 If no confusion arises, we write $x \equiv y$ for $R \> x \> y$.
-We finish this section by giving some operations of functors and natural transformations, which we need later.
+
+We finish this section by giving some operations of functors and natural transformations, which we need in Definition \ref{def:semendpoint}.
 Functors and natural transformations are defined the usual way \cite{mac2013categories}, and we write $\functor{\mathcal{C}}{\mathcal{D}}$ and $\nattrans{F}{G}$ for the type of functors from $\mathcal{C}$ to $\mathcal{D}$ and transformations from $F$ to $G$ respectively.
@@
 	\item For each category $\mathcal{C}$, we have the identity $\idf{\mathcal{C}} : \functor{\mathcal{C}}{\mathcal{C}}$.
-	\item For $F : \functor{\mathcal{C}_1}{\mathcal{C}_2}$ and $G : \functor{\mathcal{C}_2}{\mathcal{C}_3}$, we have a composition $\compf{F}{G} : \functor{\mathcal{C}_1}{\mathcal{C}_2}$;
+	\item For $F : \functor{\mathcal{C}_1}{\mathcal{C}_2}$ and $G : \functor{\mathcal{C}_2}{\mathcal{C}_3}$, we have a composition $\compf{F}{G} : \functor{\mathcal{C}_1}{\mathcal{C}_3}$;
 	\item If $\mathcal{D}$ has binary products, then for $F, G : \functor{\mathcal{C}}{\mathcal{D}}$, we have a product $\prodf{F}{G} : \functor{\mathcal{C}}{\mathcal{D}}$;
@@
 
+The type of $\pairt{\eta_1}{\eta_2}$ might seem unnatural.
+However, it is precisely this type we need for the constructions in Definition \ref{def:semendpoint}..
+
 \section{Signature of HITs}
@@
 Before we study the construction of set truncated HITs, we first give a precise definition of those.
-We do this by internalizing the scheme by Basold \etal \ \cite{BasoldGW17} via a type of signatures.
-In this section, we give the definition of signatures, and then in the upcoming sections, we define the notion of HITs for a signature.
-
-Higher inductive types are freely generated by both point and path constructors.
-The data of the point constructor is a \emph{polynomial functor}.
-These are described by the following type.
+We describe HITs by saying how to construct points and paths.
+For example, the integers modulo 2, which we considered in the introduction, has two constructors for points, namely $\ZZ$ ad $\SZ$, and one for the paths, namely $\modP$.
+The signature of this type would thus indicate that we have one nullary and one unary operation, and a path of the required type.
+In this section, we define a type of signatures as internalized variation of the one by Basold \etal \ \cite{BasoldGW17}, and then in the upcoming sections, we define HITs for a signature.
+
+The first ingredient of the signature, is the arity of the point constructor.
+This is described by a \emph{finitary polynomial functor}, and we define those as the following type.
 
@@
 \label{def:poly}
-The type $\mathcal{\poly}$ of \emph{codes of polynomials} is inductively generated by the following constructors.
+We define the type $\mathcal{\poly}$ of \emph{codes of finitary polynomials} as the inductive type generated by the following constructors.
 \begin{center}
@@
 In the next section, we show that each code $P : \poly$ gives rise to a functor $\semP{P} : \functor{\hset}{\hset}$.
-A higher inductive type $H$ should have a point constructor $c : \semP{P} \> H \rightarrow H$, which represents the introduction rule for points.
+Each higher inductive type $H$ has a point constructor $c : \semP{P} \> H \rightarrow H$, which represents the introduction rule for points.
 
 HITs also have an introduction rule for paths, and for those, we need to give the possible endpoints of paths.
-Each path is given a universally quantified equation, which can possibly make use of the point constructor.
+Each path is given by a universally quantified equation, which can possibly make use of the point constructor.
 For this reason, the type of endpoint must depend on the data of the point constructor.
 We also indicate the source and target of the equation, and both of them depend polynomially on the HIT being defined.
-The type of endpoints is defined as an inductive type.
+The type of endpoints is defined inductively.
 
@@
 
+In the formalization, we also include for each $f : X \rightarrow Y$ an endpoint $\fmap \> f : \ep{A}{\C \> X}{\C \> Y}$, which we do not discuss here.
 The polynomial $A$ represents the point constructor and that explains the endpoint $\constr$.
 The polynomials $P$ and $Q$ represent the source and target of the equation respectively.
-If we have a set $X$ with a map $c : \semP{A} \> X \rightarrow X$, each endpoint $e : \ep{A}{P}{Q}$ gives rise to a natural map $\semP{P} \> X \rightarrow \semP{Q} \> X$ where $\constr$ is interpreted by $c$.
+If we have a set $X$ with a map $c : \semP{A} \> X \rightarrow X$, each endpoint $e : \ep{A}{P}{Q}$ gives rise to a natural morphism from the functor $\semP{P}$ to $\semP{Q}$ where $\constr$ is interpreted using $c$.
 These maps are the left- and right-hand side of  the equations.
@@
 	\item A type $\pathI{\sig}$ representing the names of path constructors;
-	\item A family $\pathA{\sig} : \pathI{\sig} \rightarrow \poly$ representing the source of the paths;
-	\item Maps $\pathlh{\sig}, \pathrh{\sig} : \deprod{j}{\pathA{\sig}}{\ep{\pointc{\sig}}{\pathA{\sig} \> j}{\I}}$ representing the left- and right-hand side of the equations.
+	\item A family $\pathA{\sig} : \pathI{\sig} \rightarrow \poly$ representing the arguments of the paths;
+	\item Maps $\pathlh{\sig}, \pathrh{\sig} : \deprod{j}{\pathI{\sig}}{\ep{\pointc{\sig}}{\pathA{\sig} \> j}{\I}}$ representing the left- and right-hand side of the equations.
 \end{itemize}
@@
 Inductive $H$ :=
-| $c$ : $\semP{\pointc{\sig}} \> H \rightarrow H$
-| $p$ : $\deprod{j}{\pathI{\sig}}{\deprod{x}{\semP{\pathA{\sig}} \> H}{\semE{\pathlh{\sig} \> j} \> H \> x = \semE{\pathrh{\sig} \> j} \> H \> x}}$
+| $\constructor{c}$ : $\semP{\pointc{\sig}} \> H \rightarrow H$
+| $\constructor{p}$ : $\deprod{j}{\pathI{\sig}}{\deprod{x}{\semP{\pathA{\sig} \> j} \> H}{\semE{\pathlh{\sig} \> j} \> H \> x = \semE{\pathrh{\sig} \> j} \> H \> x}}$
+| $\constructor{s}$ : $\isaset{H}$
 \end{lstlisting}
 
+Since our goal is to interpret set-truncated HITs, we require the constructor $s$.
 To illustrate the possibilities of this definition, we define two examples from the introduction as HIT signatures.
@@
 We represent it by the signature $\modsig$ defined as follows
+\[
+\pointc{\modsig} \Def \sumP{\I}{(\C \> \unitt)}
+\quad \quad \quad
+\pathI{\modsig} \Def \unitt
+\quad \quad \quad
+\pathA{\modsig} \Def \I\]
+\[
+\pathlh{\modsig} \> j \Def \comp{\comp{\comp{\inle}{\constr}}{\inle}}{\constr}
+\quad \quad \quad
+\pathrh{\modsig} \> j \Def \id{\I}
+\]
+\remove{
 \begin{itemize}
@@
 	\item $\pathA{\modsig} \Def \I$;
-	\item $\pathlh{\modsig} \> j \Def \comp{\comp{\comp{\comp{\id{\I}}{\inle}}{\constr}}{\inle}}{\constr}$;
+	\item $\pathlh{\modsig} \> j \Def \comp{\comp{\comp{\inle}{\constr}}{\inle}}{\constr}$;
 	\item $\pathrh{\modsig} \> j \Def \id{\I}$;
 \end{itemize}
+}
 \end{example}
@@
 Note that the endpoint $\comp{\inle}{\constr}$ takes the successor, so, the equation says that $S(S \> x) = x$ for all $x : X$.
-Signatures for groups and join semi-lattices are defined similarly.
 Since signatures can depend on types, we can also define the propositional truncation.
@@
 Let $A$ be a set.
-We represent the truncation of a set by the following signature.
+We represent its truncation by the following signature.
+\[
+\pointc{\trunc} \Def \C \> A
+\quad \quad \quad
+\pathI{\trunc} \Def \unitt
+\quad \quad \quad
+\pathA{\trunc} \Def \prodP{\I}{\I}
+\]
+\[
+\pathlh{\trunc} \> j \Def \prle
+\quad \quad \quad
+\pathrh{\trunc} \> j \Def \prre
+\]
+\remove{
 \begin{itemize}
@@
 	\item $\pathA{\trunc} \Def \prodP{\I}{\I}$;
-	\item $\pathlh{\trunc} \> j \Def \comp{\id{\prodP{\I}{\I}}}{\prle}$;
-	\item $\pathrh{\trunc} \> j \Def \comp{\id{\prodP{\I}{\I}}}{\prre}$;
+	\item $\pathlh{\trunc} \> j \Def \prle$;
+	\item $\pathrh{\trunc} \> j \Def \prre$;
 \end{itemize}
+}
 \end{example}
 
+Other examples, such as the integers, free algebras, and the ring of polynomials, can be found in the formalization.
 This signature represents a HIT $H$ with a map $A \rightarrow H$ and for which all inhabitants are equal, which is precisely the propositional truncation from Definition \ref{def:trunc} for sets $A$.
@@
 \subsection{Algebras in Sets}
-Now we know what signatures are, the next goal is to define HITs for signatures.
-For that we need to give the required introduction, elimination, and computation rules.
-In this section, we study the introduction rule of HITs and we do that by defining a category of algebras on a polynomial.
-Furthermore, since ultimately we want to construct HITs as quotients, we do not just define algebra in sets, but also in setoids.
-Let us start by interpreting polynomials as functors.
+To define HITs on a signature, we need to give the introduction, elimination, and compuation rules.
+Let us start with the introduction rule, which we define via algebras.
+Note that this rule comes in two flavors: one for the points and one forthe paths.
+For this reason, we define algebras in two steps.
+
+We start by saying how to interpret the point constructors.
 
@@
 For each $P : \poly$, we define a functor $\semP{P} : \functor{\hset}{\hset}$ as follows
+\[
+\semP{\C \> X} \Def \Cf{X}
+\quad \quad \quad
+\semP{\I} \Def \idf{\hset}
+\quad \quad \quad
+\semP{\sumP{P}{Q}} \Def \sumf{\semP{P}}{\semP{Q}}
+\quad \quad \quad
+\semP{\prodP{P}{Q}} \Def \prodf{\semP{P}}{\semP{Q}}
+\]
+\remove{
 \begin{itemize}
@@
 \end{itemize}
+}
 \end{definition}
@@
 Its objects are pairs $X : \mathcal{C}$ together with an arrow $\mathcal{C}_1(F \> X, X)$.
+The morphisms from $(X, f)$ to $(Y, g)$ consist of maps $h : \mathcal{C}_1(X,Y)$ such that $h \circ f = g \circ F(h)$.
 Note that we always have a forgetful functor $\forget{F} : \functor{\falg{F}}{\mathcal{C}}$.
@@
 For each endpoint $e : \ep{A}{P}{Q}$, we define a natural transformation $\semE{e} : \nattrans{\compf{\forget{A}}{\semP{P}}} {\compf{\forget{A}}{\semP{Q}}}$
+\[
+\semE{\id{P}} \Def \idt{\compf{\forget{A}}{\semP{P}}}
+\quad \quad \quad
+\semE{\comp{e_1}{e_2}} \Def \compt{\semE{e_1}}{\semE{e_2}}
+\quad \quad \quad
+\semE{\inle} \Def \lwhisker{\forget{A}}{\inlt}
+\quad \quad \quad
+\semE{\inre} \Def \lwhisker{\forget{A}}{\inrt}
+\quad \quad \quad
+\semE{\Ce \> t} \Def \ctrans{t}
+\]
+\[
+\semE{\prle} \Def \lwhisker{\forget{A}}{\prlt}
+\quad \quad \quad
+\semE{\prre} \Def \lwhisker{\forget{A}}{\prrt}
+\quad \quad \quad
+\semE{\pair{e_1}{e_2}} \Def \pairt{\semE{e_1}}{\semE{e_2}}
+\quad \quad \quad
+\semE{\constr} \Def \constrt{A}
+\]
+\remove{
 \begin{itemize}
@@
 \end{itemize}
-\end{definition}
-
+}
+\end{definition}
+
+Note that $\semE{\constr}$ is required to have type $\nattrans{\compf{\forget{P}}{\semP{P}}}{\compf{\forget{P}}{\semP{\I}}}$.
+Since the functors $\compf{\forget{P}}{\semP{\I}}$ and $\forget{P}$ are only equal up to propositional equality, we defined $\constrt{A}$ to be of that type instead of the expected $\nattrans{\compf{\forget{P}}{\semP{P}}}{\forget{P}}$,
 Now we have everything in place to define algebras on $\sig$.
@@
 \label{prop:univalg}
-The category of $\sig$-algebras is univalent.
+The category of $\sig$-algebras in sets is univalent.
 \end{proposition}
@@
 We define $S_X \> x \Def f(\inl \> x)$ and $Z_X = f(\inr \> \TT)$.
-An algebra of $\modsig$ consists of a prealgebra $X$ such that for all $x : X \times X$, we have $S_X(S_X \> x) = x$.
+An algebra of $\modsig$ consists of a prealgebra $X$ such that for all $x : X$, we have $S_X(S_X \> x) = x$.
 \end{example}
@@
 \subsection{Algebras in Setoids}
-Recall that the core idea is that we define the initial algebra in sets by taking the quotient of the initial algebra in setoids.
-For that reason, we also define algebras in setoids and for these, we take a slightly different approach.
-Instead of defining the interpretation of the polynomial $P$ inductively making use of binary sums and products in $\setoids$, we define an equivalence relation on $\semP{P}$.
-
-To define the action of polynomials on equivalence relations, we need some preliminary operations.
-For a set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y \Def x = y$.
+Our goal is to construct HITs as a quotient of a certain setoids.
+To guarantee that the resulting quotient has the right introduction rule, we require extra structure from the setoid.
+This is given by an algebra structure on the setoid.
+
+To interpret the action of $P$ on setoids, we first define its action on equivalence relations, and we need some preliminary operations for that.
+Note that for each set $T$, we have an equivalence relation $\pathR{T}$ on $T$ such that $\pathR{T} \> x \> y \Def x = y$.
 Furthermore, given types $X$ and $Y$ with equivalence relations $R_X$ and $R_Y$ on them, we can define equivalence relations $\sumR{R_X}{R_Y}$ and $\prodR{R_X}{R_Y}$ on $X + Y$ and $X \times Y$ respectively.
@@
 By induction, we define an equivalence relation $\polyR{P}{R}$ on $\semP{P} \> X$.
+\[
+\polyR{(\C \> T)}{R} \Def \pathR{T}
+\quad \quad \quad
+\polyR{\I}{R} \Def R
+\quad \quad \quad
+\polyR{(\sumP{P}{Q})}{R} \Def \sumR{(\polyR{P}{R})}{(\polyR{Q}{R})}
+\quad \quad \quad
+\polyR{(\prodP{P}{Q})}{R} \Def \prodR{(\polyR{P}{R})}{(\polyR{Q}{R})}
+\]
+\remove{
 \begin{itemize}
@@
 \end{itemize}
+}
 Now we define the functor $\semPT{P} : \functor{\setoids}{\setoids}$ by $\semPT{P}(X,R) = (\semP{P} \> X, \polyR{P}{R})$.
@@
 
-This gives rise to a category $\prealgst{\sig}$ of \emph{setoid prealgebras on $\sig$}.
+The functor $\semPT{P}$ could also be defined by using that the category of setoids is Cartesian closed.
+However, we chose this definition, because it was more convenient in the formalization.
+This is because the underlying set of $\semPT{P}(X)$ can be computed definitionally.
+
+With these definitions in place, we obtain a category $\prealgst{\sig}$ of \emph{setoid prealgebras on $\sig$}.
 To define algebras on $\sig$, we also need to interpret endpoints for which we use setoid morphisms instead of natural transformations.
@@
 Let $e : \ep{A}{P}{Q}$ be an endpoint and let $X$ be a setoid prealgebra on $A$.
-Then we define $\semET{e}$ to be the setoid morphism from $\semE{P}(X)$ to $\semE{Q}(X)$ whose carrier is $\semP{e}$.
-\end{definition}
-
+Then we define $\semET{e}$ to be the setoid morphism from $\semPT{P}(X)$ to $\semPT{Q}(X)$ whose carrier is $\semP{e}$.
+\end{definition}
+
+The requirement for $\semET{e}$ to be a setoid morphism, is that for $x, y : \semPT{P} \> X$ with $r : x \equiv y$, we have $\semP{e} \> x \equiv \semP{e} \> y$.
 The category of algebras on $\sig$ is defined differently for setoids than for sets.
@@
 \[
-\deprod{j}{\pathI{\sig}}{\deprod{x}{\pathA{\sig} \> j}{\semE{\pathlh{\sig} \> j} \> x \equiv \semE{\pathrh{\sig} \> j} \> x}}
-\]
-where $\equiv$  is the setoid relation.
+\deprod{j}{\pathI{\sig}}{\deprod{x}{\pathA{\sig} \> j}{\semE{\pathlh{\sig} \> j} \> x \equiv \semE{\pathrh{\sig} \> j} \> x}}.
+\]
 \end{definition}
@@
 \begin{proposition}
-The category of $\sig$-setoid-algebras is unvialent.
+The category of $\sig$-setoid-algebras is univalent.
 \end{proposition}
@@
 \label{sec:induction}
-The introduction rules of higher inductive types are covered by the algebra structure, but the elimination and computation rules require additional structure.
-The main feature of the elimination rule is that it allows defining dependent ``homomorphisms'' to families with some kind of ``dependent algebra structures'' and the computation rule says the algebraic structure is preserved.
-To formulate these two rules, we make use of \emph{displayed algebras}, which represent the input of the elimination rule.
-When we have all this machinery in place, we define the notion of \emph{higher inductive type} for a signature.
-
-Since our goal is to construct HITs, we need to verify the induction rule and for that, we use initial algebra semantics.
+With the introduction rules covered by the algebra structure, we now take a look a the elimination and computation rules.
+For this, we use \emph{displayed algebras} \cite{KaposiK18,Sojakova15}.
+These represent the input of the elimination rule.
+For the output, we define \emph{displayed algebra maps}, also known as sections.
+The elimination rule says that we have a displayed algebra map to every displayed algebra, while the computation rule says that the algebra in place.
+Once we have this machinery in place, we define \emph{higher inductive type} on a signature.
+
+Since our goal is to construct HITs, we need to find an algebra for which the elimination rule holds, and for that, we use initial algebra semantics \cite{AltenkirchCDKF18,AwodeyGS12,Sojakova15}.
 More specifically, we show that the initial algebra satisfies the induction rule.
-Hence, to obtain a HIT, it suffices to construct the initial algebra, for which we use category theory.
+Hence, to obtain a HIT, it suffices to construct the initial algebra, which is more convenient in the language of category theory.
 
@@
 \begin{definition}
-Given are a polynomial $P$ and a family $Y : X \rightarrow \hset$.
-We define a family $\polydact{P}{Y} : \semP{P} \> X \rightarrow \hset$ by induction
+Given are $P : \poly$ and $Y : X \rightarrow \hset$.
+We define $\polydact{P}{Y} : \semP{P} \> X \rightarrow \hset$ by induction
+\[
+\polydact{\C \> X}{Y} \> x \Def X
+\quad \quad \quad
+\polydact{\I}{Y} \> x \Def Y \> x
+\quad \quad \quad
+\polydact{\prodP{P}{Q}}{Y} \> x \Def \polydact{P}{Y} \> (\prl \> x) \times \polydact{Q}{Y} \> (\prr \> x)
+\]
+\[
+\polydact{\sumP{P}{Q}}{Y} \> (\inl \> x) \Def \polydact{P}{Y} \> x
+\quad \quad \quad
+\polydact{\sumP{P}{Q}}{Y} \> (\inr \> x) \Def \polydact{Q}{Y} \> x
+\]
+\remove{
 \begin{itemize}
@@
 We define a map $\epdact{e}{c} : \deprod{z}{\semP{P}{X}}{\polydact{P}{Y} \> z \rightarrow \polydact{Q}{Y} \> (\semE{e} \> z)}$ by induction on $e$
+\[
+\epdact{\id{P}}{c} \> z \> y \Def y
+\quad \quad
+\epdact{\comp{e_1}{e_2}}{c} \> z \> y \Def \epdact{e_2}{c} \> (\semE{e_1} \> X \> z) \> (\epdact{e_1}{c} \> z \> y)
+\quad \quad
+\epdact{\inle}{c} \> z \> y \Def y
+\quad \quad
+\epdact{\inre}{c} \> z \> y \Def y
+\quad \quad
+\epdact{\Ce \> t}{c} \> z \> y \Def t
+\]
+\[
+\epdact{\prle}{c} \> z \> y \Def \prlt \> y
+\quad \quad \quad
+\epdact{\prre}{c} \> z \> y \Def \prrt \> y
+\quad \quad \quad
+\epdact{\pair{e_1}{e_2}}{c} \> z \> y \Def (\epdact{e_1}{c} \> z \> y , \epdact{e_2}{c} \> z \> y)
+\quad \quad \quad
+\epdact{\constr}{c} \Def c
+\]
+\remove{
 \begin{itemize}
@@
 With this in place, we define displayed algebras.
-Note that since we are working in a family of sets, we need to use the dependent equality type from Definition \ref{def:depeq} instead.
-
-\begin{definition}
-Let $\sig$ be a HIT signature and let $X$ be an algebra on $\sigma$.
+Note that since we are working in a family of sets, we need to use the dependent equality type from Definition \ref{def:depeq} instead of the ordinary one.
+
+\begin{definition}
+Give are a signature $\sig$ and an algebra $X$ on $\sig$.
 Then a \emph{displayed algebra} over $X$ consists of
@@
 	\item A type family $Y : X \rightarrow \hset$;
-	\item An operation $c_Y : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)}$;
-	\item For each $j : \pathI{\sig}$, $x : \semP{\pathA{\sig}} \> X$, and $y : \polydact{\pathA{\sig}}{Y} \> x$,  a path $p_Y : \depeq{\constrP{X} \> j \> x}{\epdact{\pathlh{\sig}}{c} \> x \> y}{\epdact{\pathrh{\sig}}{c} \> x \> y}$.
+	\item An operation $c_Y : \deprod{z}{\semP{\pointc{\sig}}{X}}{\polydact{\pointc{\sig}}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)}$;
+	\item For each $j : \pathI{\sig}$, $x : \semP{\pathA{\sig}} \> X$, and $y : \polydact{\pathA{\sig}}{Y} \> x$,  a path $p_Y : \depeq{\constrP{X} \> j \> x}{\epdact{\pathlh{\sig}}{c_Y} \> x \> y}{\epdact{\pathrh{\sig}}{c_Y} \> x \> y}$.
 \end{itemize} 
@@
 Given a map $f : \deprod{x}{X}{Y \> x}$, we define a map $\polydmap{P}{f} : \deprod{x}{\semP{P} \> X}{\polydact{P}{Y} \> x}$ by induction
+\[
+\polydmap{\C \> X}{f} \> x \Def x
+\quad \quad \quad
+\polydmap{\I}{f} \Def f
+\quad \quad \quad
+\polydmap{\prodP{P}{Q}}{f} \> x \Def (\polydact{P}{f} \> (\prl \> x) , \polydact{Q}{f} \> (\prr \> x))
+\]
+\[
+\polydmap{\sumP{P}{Q}}{f} \> (\inl \> x) \Def \polydmap{P}{f} \> x
+\quad \quad \quad
+\polydmap{\sumP{P}{Q}}{f} \> (\inr \> x) \Def \polydmap{Q}{f} \> x
+\]
+\remove{
 \begin{itemize}
@@
 Note that HITs of $\sig$ satisfy analogous rules to those defined by Basold \etal \ \cite{BasoldGW17}.
+As usual, the induction rule only guarantees the existence of a dependent map.
+This obtained map is unique, which is again proven by induction.
+Furthermore, HITs on the signatures we discussed before, the integers modulo 2 in Example \ref{ex:modsig} and the propositional truncation in Example \ref{ex:truncsig}, satisfy the induction rule given in Basold \etal \ \cite{BasoldGW17}.
+
+There are only two differences: the computation rule only holds propositionally rather than definitionally.
+In addition, we can only map HITs into sets.
+This is because it also has constructors, which guarantee it is a set.
 The algebra structure gives the right introduction rules and the existence of the displayed algebra map gives the required elimination and computation rules.
@@
 Next we show how to obtain the induction principle from initiality.
-This way it suffices construct an initial object of the signature to obtain a HIT, which is more convenient in category theory.
+This way it suffices construct an initial algebra of the signature to obtain a HIT, which is more convenient in category theory.
 To this end, we first define the total algebra $\total{Y}$ of a displayed $Y$ on $X$ together a projection $\proj{Y}$ to $X$.
@@
 \[
-\Ppl{P} : \semP{P} \> (\desum{x}{X}{Y \> x} \rightarrow X)
+\Ppl{P} : \semP{P} \> (\desum{x}{X}{Y \> x}) \rightarrow \semP{P} \> X
 \quad \quad
-\Ppl{P} \> x \Def \semP{\pointc{\sig}} \> \prl \> x
+\Ppl{P} \> x \Def \semP{P} \> \prl \> x
 \]
 We also define a map $\Ppr{P} : \deprod{x}{\semP{P} \> (\desum{x}{X}{Y \> x})}{\polydact{P}{Y} \> (\Ppl{P} \> x)}$ by induction on $P$.
+\[
+\Ppr{\C \> T} \> x  \Def x
+\quad \quad \quad
+\Ppr{\I} \> x \Def \prr \> x
+\quad \quad \quad
+\Ppr{\prodP{P}{Q}} \> x \Def (\Ppr{P} \> (\prl \> x) , \Ppr{Q} \> (\prr \> x))
+\]
+\[
+\Ppr{\sumP{P}{Q}} \> (\inl \> x) \Def \Ppr{P} \> x
+\quad \quad \quad
+\Ppr{\sumP{P}{Q}} \> (\inr \> x) \Def \Ppr{Q} \> x
+\]
+\remove{
 \begin{itemize}
@@
 Now let $z : \semP{\pointc{\sig}} \> (\total{Y})$.
-The first coordinate of $c_{\total{Y}} \> z$ is defined to be $\constrA{X}(\Ppl{P} \> x)$.
-The second coordinate of $c_{\total{Y}} \> z$ is defined by $c_Y \> (\Ppl{P} \> x) \> (\Ppr{P} \> x)$.
+The first coordinate of $\constrA{\total{Y}} \> z$ is defined to be $\constrA{X}(\Ppl{\pointc{\sig}} \> x)$.
+The second coordinate of $\constrA{\total{Y}} \> z$ is defined by $c_Y \> (\Ppl{\pointc{\sig}} \> x) \> (\Ppr{\pointc{\sig}} \> x)$.
 The main challenge lies within proving the equations.
@@
 \Epl : \semE{e} \> X \> (\Ppl{P} \> x) = \Ppl{Q}(\semE{e} \> (\total{Y}) \> x) 
-\]
-\[
-\Epr : \epdact{e}{c_Y} \> (\Ppr{P} \> x) = \transport{\polydact{Q}{Y}}{\invP{\Epl}} \> (\Ppr{Q} \> (\semE{e} \> (\total{Y}) \> x))
-\]
-Here $\invP{p}$ denotes the inverse of the path $p$.
+\quad \quad \quad
+\Epr : \depeq{\Epl}{\epdact{e}{c_Y} \> (\Ppr{P} \> x)}{\Ppr{Q} \> (\semE{e} \> (\total{Y}) \> x)}
+\]
 \end{lemma}
@@
 Now suppose $X$ is an initial object in the category of algebras.
-Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because initiality ensures uniqueness of homomorphisms.
+Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\compm{f}{\proj{Y}} : X \rightarrow X$ must be the identity because initiality ensures uniqueness of homomorphisms.
 Hence, we conclude
@@
 \label{sec:construction}
-To construct the initial algebra, we first define a left adjoint from algebras in setoids to algebras in algebras.
+To construct the initial algebra, we first lift the quotient to a left adjoint functor from algebras in setoids to algebras in sets.
 Such functors preserve initial objects, and thus it suffices to construct the initial setoid algebra.
@@
 The right adjoint is the path setoid functor $\pathF : \functor{\hset}{\setoids}$.
-For sets $X$, we define functor $\pathF \> X$ to be $(X, \pathR{X})$.
+For sets $X$, we define the functor $\pathF \> X$ to be $(X, \pathR{X})$.
 Note that this action is functorial and that this gives rise to an adjunction.
@@
 For this, we use a result from Hermida and Jacobs \cite{hermida1998structural}.
+Note that this is also related to the fact that the 2-functor from the bicategory of endofunctors to the bicategory of categories preserves adjunctions \cite{street1972formal}.
+
 The first step, is to lift the functors for which we use the following lemma.
@@
 
-For algebras $(X, f) : \falg{A_1}$, we define $F^{\category{PreAlg}}(X,f) = (F \> X, \compm{F \> f}{n \> X})$.
+For algebras $(X, f) : \falg{A_1}$, we define $F^{\category{PreAlg}}(X,f) = (F \> X, \compm{n \> X}{F \> f})$.
 To lift the quotient and the path setoid, we need a lemma.
@@
 \label{lem:comm}
-We have
-\begin{itemize}
-	\item $\pathF$ commutes with sums and products.
-	\item $\quotF$ commutes with sums and products.
-\end{itemize}
-This gives rise to two natural isomorphisms $n_1^P : \nattrans{\compf{\pathF}{\semPT{P}}}{\compf{\semP{P}}{\pathF}}$ and $n_2 : \nattrans{\compf{\quotF}{\semPT{P}}}{\compf{\semP{P}}{\quotF}}$.
+The functors $\pathF$ and $\quotF$ commute with sums and products.
+This gives rise to two natural isomorphisms $n_1^P : \nattrans{\compf{\pathF}{\semPT{P}}}{\compf{\semP{P}}{\pathF}}$ and $n_2^P : \nattrans{\compf{\quotF}{\semPT{P}}}{\compf{\semP{P}}{\quotF}}$.
 \end{lemma}
 
+Proving that $\quotF$ commutes with products makes essential use of the double recursion principle of the quotient type, which allows defining functions $\quotF \> X \times \quotF \> Y \rightarrow Z$.
 Using Lemmata \ref{lem:prealgadj} and \ref{lem:comm}, we lift both the quotient and the path setoid functors to obtain.
@@
 {	
-	A_2 (L(R \> X)) \ar[ddrr]^{\epsilon \> X} \ar[d]_{n(R \> X)} \\
-	L(A_2(R \> X)) \ar[d]_{L(m \> X)} \\
-	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_2 \> X)} & & A_2 \> X
+	A_2 (L(R \> X)) \ar[ddrr]^{A_2(\epsilon \> X)} \ar[d]_{n(R \> X)} \\
+	L(A_1(R \> X)) \ar[d]_{L(m \> X)} \\
+	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_1 \> X)} & & A_2 \> X
 }
@@
 	A_1 \> Y \ar[ddrr]_{\eta \> (A_1 \> X)} \ar[rr]^-{A_1 \> (\eta \> Y)} & & A_1(R(L \> Y)) \ar[d]^{m(L \> X)}\\
-	& & R(A_1(L \> X)) \ar[d]^{R(n \> X)}\\
+	& & R(A_2(L \> X)) \ar[d]^{R(n \> X)}\\
 	& & R(L(A_1 \> Y))
@@
 For the verification of the conditions of this proposition for the path setoid and quotient, we refer the reader to the formalization.
-Then we can conclude
+Now we conclude
 
@@
 If $\mathcal{C}$ is a category and $P$ is a family of propositions on $\mathcal{C}$, then we write $\fullsub{\mathcal{C}}{P}$ for the full subcategory of $\mathcal{C}$ in which each object satisfies $P$.
-First, we look at way to obtain adjunctions between full subcategories.
+First, we look at a way to obtain adjunctions between full subcategories.
 
@@
 \[
-\compm{\pathF \> (\semE{e} \> X)}{n_1^P \> X} = \compm{n_1^Q \> X}{\semET{e} \> (\pathPA \> X)}.
+\compm{n_1^P \> X}{\pathF \> (\semE{e} \> X)} = \compm{\semET{e} \> (\pathPA \> X)}{n_1^Q \> X}.
 \]
@@
 \[
-\compm{\quotF \> (\semET{e} \> X)}{n_2^P \> X} = \semE{e} \> (\quotPA \> X).
+\compm{n_2^P \> X}{\quotF \> (\semET{e} \> X)} = \semE{e} \> (\quotPA \> X).
 \]
@@
 
-This follows from Ad\'amek's theorem and the fact that the functors $\semP{P}$ is $\omega$-continuous for each $P$.
+This follows from Ad\'amek's theorem and the fact that the functor $\semP{P}$ is $\omega$-continuous for each $P$.
+The colimits required for this theorem are constructed from quotient types.
 We denote the initial object of this category by $(\CRC , f)$.
 The carrier of the desired setoid is $\CRC$ and the next step is to define the equivalence relation on $\CRC$.
-
 The main difficulty of defining this relation, is that we need to be able to lift $f$ to a setoid morphism meaning that $\semP{\pointc{\sig}}{\CRC}$ must be defined correctly.
@@
 \begin{definition}
-Given is $P : \poly$.
+Given is $P : \poly$ and a signature $\sig$.
 The relation $\CR \> P$ on $\semP{P} \> \CRC$ is inductively generated by the constructors
@@
 
+The extra argument $P$ represents the sort of $x$, and we leave the signature $\sig$ implicit when talking about this relation.
 Now we define a relation on $\CRC$ by $\CRR \> x \> y = \trunct{\CR \> \I \> x \> y}$.
@@
 In addition, all equations in $\sig$ are validated in $\CRR$ by $\CRpath$.
-Finally, with the constructors $\CRpair$, $\CRinl$, $\CRinr$, and $\CRcong$, we can show that $\CRR$ preserves $f$.
-Hence, we obtain a setoid $I \Def (\CR, \CRC)$ together with a setoid morphism $\varphi : \semPT{P} \> I \rightarrow I$.
-To show that this is the initial setoid, we first need a property of $\CRR$, which allows us to make maps from $I$ to algebras.
+Finally, with the constructors $\CRpair$, $\CRinl$, $\CRinr$, and $\CRcong$, we can show that $f$ preserves $\CRR$.
+Hence, we obtain a setoid $I \Def (\CRC, \CR)$ together with a setoid morphism $\varphi : \semPT{P} \> I \rightarrow I$.
+To show that this is the initial setoid algebra, we first need a property of $\CRR$, which allows us to construct maps from $I$ to algebras.
 
@@
 \label{lem:mapcongrel}
-If $g$ is a prealgebra morphism from $\CR$ to some algebra $X$, then $g$ preserves $\CRR$.
+If $g$ is a prealgebra morphism from $\CRC$ to an algebra, then $g$ preserves $\CRR$.
 \end{lemma}
@@
 Now we show that $I$ is an initial object in $\Alg{\sig}$.
-To show that we always have a homomorphism from $I$ to an algebra $X$, we use that $\CR$ is the initial prealgebra and lemma \ref{lem:mapcongrel}.
+To show that we always have a homomorphism from $I$ to an algebra $X$, we use that $\CRC$ is the initial prealgebra and Lemma \ref{lem:mapcongrel}.
 Furthermore, note that two setoid morphisms are equal if their underlying carriers are equal and two algebra morphisms are also equal if their underlying carrier is equal.
@@
 \label{thm:initialsetoid}
-The category $\Algst{\sig}$ has an initial object.
+The algebra $I$ is the initial object of $\Algst{\sig}$.
 \end{theorem}
@@
 \subsection{Uniqueness of HITs}
+Now we discuss two consequences of this construction.
 A first property of higher inductive types, is that they are unique up to equality.
 For that, we first show that higher inductives are initial algebras.
-Note that in \Cref{sec:induction} we made use of the converse statement, namely that initial algebras are HITs.
+This requires the well-known result that induction implies initiality \cite{AwodeyGS12,Sojakova15}.
+Note that in \Cref{sec:induction} we used the converse statement, namely that initiality implies induction.
 
@@
 \[
-c : \deprod{z}{\semP{A}{X}}{\polydact{P}{Y} \> z \rightarrow Y \> (f \> z)},
+c : \deprod{z}{\semP{\pointc{\sig}}{H}}{\polydact{\pointc{\sig}}{Y} \> z \rightarrow Y \> (\constrA{X} \> z)},
 \]
@@
 Let $\sig$ be a signature.
-Then for each $x, y : \CRC$ we have an equivalence $\CRR \> x \> y \weq \classof \> x = \classof \> y$.
+Then for each $x, y : \CRC$ we have an equivalence $\CRR \> x \> y \weq \classof \> x = \classof \> y$ using $\CRC$ and $\CRR$ as defined in the previous section.
 \end{corollary}
+
+Hence, since HITs are unique, they must be equal to the HIT we constructed in the previous section, and this determines the path spaces of HITs.
+Note that this corollary gives an induction principle for the type $\classof \> x = \classof \> y$, because $\CRR$ is defined as the propositional truncation of an inductive type,
+For this reason, we conclude that the path space of higher inductive types are freely generated.
 
@@
 We have shown how to construct finitary set-truncated higher inductive types using the quotient and propositional truncation in Theorem \ref{thm:hit-exist}.
-Since truncations and the quotient can be constructed from nonrecursive HITs, this proves that all finitary set-truncated HITs can be constructed from nonrecursive ones.
+Since truncations and the quotient can be constructed from non-recursive HITs, this proves that all finitary set-truncated HITs can be constructed from non-recursive ones.
 Besides that, we took advantage of this construction to show uniqueness of HITs in Corollary \ref{cor:hit_unique} and to characterize their path space in Corollary \ref{cor:hit_path}.
 
-For a construction of all finitary HITs, higher path constructors need to be allowed and the HITs need to be interpreted as higher categories instead of sets.
-A first step towards that goal, would be adapting this construction to bicategory theory \cite{ahrens2019bicategories,capriotti2017univalent} and constructing higher inductive 1-types using Dybjer's and Moeneclaey's interpretation of such HITs in groupoids \cite{DybjerM18}.
-Doing so, would require interpreting the endpoints of homotopies.
+The method used in this paper crucially relies on the polynomials being finitary.
+To show that Infinitary polynomials commute with quotients, one needs the axiom of choice \cite{DBLP:journals/mscs/ChapmanUV19}.
+Furthermore, Lumsdaine and Shulman gave an infinitary HIT which cannot be constructed from pushouts, and thus this result cannot be extended to infinitary polynomials.
+
+However, a possible extension would be by allowing the arguments of point constructors to depend on previous ones \cite{AltenkirchCDKF18}.
+For a construction of all finitary HITs, higher path constructors need to be allowed and the HITs need to be interpreted in some higher category.
+A first step towards that goal, would be adapting this construction to bicategory theory \cite{ahrens2019bicategories,capriotti2017univalent} and constructing higher inductive 1-types using Dybjer's and Moeneclaey's interpretation of those in groupoids \cite{DybjerM18}.
+For non-truncated types, a type theoretic definition of $\omega$-groupoid would be required \cite{DBLP:conf/csl/AltenkirchR12,capriotti2017univalent,DBLP:conf/lics/FinsterM17,DBLP:conf/tlca/HirschowitzHT15}.
+In both cases, one also needs to interpret the endpoints of homotopies.
 In addition, the path computation rules become relevant.
@@
 
-\begin{thebibliography}{10}\label{bibliography}
+\begin{thebibliography}{10}
+
+	\bibitem{ahrens2019bicategories}
+	Benedikt Ahrens, Dan Frumin, Marco Maggesi, and Niels van~der Weide.
+	\newblock {Bicategories in Univalent Foundations}.
+	\newblock {\em arXiv preprint arXiv:1903.01152}, 2019.
+
+	\bibitem{AhrensKS15}
+	Benedikt Ahrens, Krzysztof Kapulkin, and Michael Shulman.
+	\newblock {Univalent Categories and the Rezk Completion}.
+	\newblock {\em Mathematical Structures in Computer Science}, 25(5):1010--1039,
+	2015.
+
+	\bibitem{AhrensL19}
+	Benedikt Ahrens and Peter~LeFanu Lumsdaine.
+	\newblock {Displayed Categories}.
+	\newblock {\em Logical Methods in Computer Science}, 15(1), 2019.
 
@@
 	Thorsten Altenkirch, Paolo Capriotti, Gabe Dijkstra, Nicolai Kraus, and
-	Fredrik~Nordvall Forsberg, \emph{{Quotient Inductive-Inductive Types}},
-	Foundations of Software Science and Computation Structures - 21st
-	International Conference, {FOSSACS} 2018, Held as Part of the European Joint
-	Conferences on Theory and Practice of Software, {ETAPS} 2018, Thessaloniki,
-	Greece, April 14-20, 2018, Proceedings, 2018, pp.~293--310.
+	Fredrik~Nordvall Forsberg.
+	\newblock {Quotient Inductive-Inductive Types}.
+	\newblock In {\em Foundations of Software Science and Computation Structures -
+		21st International Conference, {FOSSACS} 2018, Held as Part of the European
+		Joint Conferences on Theory and Practice of Software, {ETAPS} 2018,
+		Thessaloniki, Greece, April 14-20, 2018, Proceedings}, pages 293--310, 2018.
 
 	\bibitem{AltenkirchDK17}
-	Thorsten Altenkirch, Nils~Anders Danielsson, and Nicolai Kraus,
-	\emph{{Partiality, Revisited - The Partiality Monad as a Quotient
-			Inductive-Inductive Type}}, Foundations of Software Science and Computation
-	Structures - 20th International Conference, {FOSSACS} 2017, Held as Part of
-	the European Joint Conferences on Theory and Practice of Software, {ETAPS}
-	2017, Uppsala, Sweden, April 22-29, 2017, Proceedings, 2017, pp.~534--549.
-
-	\bibitem{ahrens2019bicategories}
-	Benedikt Ahrens, Dan Frumin, Marco Maggesi, and Niels van~der Weide,
-	\emph{{Bicategories in Univalent Foundations}}, arXiv preprint
-	arXiv:1903.01152 (2019), To Appear in FSCD 2019.
+	Thorsten Altenkirch, Nils~Anders Danielsson, and Nicolai Kraus.
+	\newblock {Partiality, Revisited - The Partiality Monad as a Quotient
+		Inductive-Inductive Type}.
+	\newblock In {\em Foundations of Software Science and Computation Structures -
+		20th International Conference, {FOSSACS} 2017, Held as Part of the European
+		Joint Conferences on Theory and Practice of Software, {ETAPS} 2017, Uppsala,
+		Sweden, April 22-29, 2017, Proceedings}, pages 534--549, 2017.
+
+	\bibitem{AltenkirchK16}
+	Thorsten Altenkirch and Ambrus Kaposi.
+	\newblock {Type Theory in Type Theory using Quotient Inductive Types}.
+	\newblock In {\em Proceedings of the 43rd Annual {ACM} {SIGPLAN-SIGACT}
+		Symposium on Principles of Programming Languages, {POPL} 2016, St.
+		Petersburg, FL, USA, January 20 - 22, 2016}, pages 18--29, 2016.
+
+	\bibitem{DBLP:journals/lmcs/AltenkirchK17}
+	Thorsten Altenkirch and Ambrus Kaposi.
+	\newblock Normalisation by Evaluation for Type Theory, in Type Theory.
+	\newblock {\em Logical Methods in Computer Science}, 13(4), 2017.
+
+	\bibitem{DBLP:conf/csl/AltenkirchR12}
+	Thorsten Altenkirch and Ondrej Rypacek.
+	\newblock {A Syntactical Approach to Weak $\omega$-Groupoids}.
+	\newblock In {\em Computer Science Logic (CSL'12) - 26th International
+		Workshop/21st Annual Conference of the EACSL, {CSL} 2012, September 3-6,
+		2012, Fontainebleau, France}, pages 16--30, 2012.
+
+	\bibitem{AngiuliHW17}
+	Carlo Angiuli, Robert Harper, and Todd Wilson.
+	\newblock {Computational Higher-Dimensional Type Theory}.
+	\newblock In {\em Proceedings of the 44th {ACM} {SIGPLAN} Symposium on
+		Principles of Programming Languages, {POPL} 2017, Paris, France, January
+		18-20, 2017}, pages 680--693, 2017.
+
+	\bibitem{AngiuliMLH16}
+	Carlo Angiuli, Edward Morehouse, Daniel~R. Licata, and Robert Harper.
+	\newblock {Homotopical Patch Theory}.
+	\newblock {\em J. Funct. Program.}, 26:e18, 2016.
 
 	\bibitem{AwodeyGS12}
-	Steven Awodey, Nicola Gambino, and Kristina Sojakova, \emph{{Inductive Types in
-			Homotopy Type Theory}}, Proceedings of the 27th Annual {IEEE} Symposium on
-	Logic in Computer Science, {LICS} 2012, Dubrovnik, Croatia, June 25-28, 2012,
-	2012, pp.~95--104.
-
-	\bibitem{AngiuliHW17}
-	Carlo Angiuli, Robert Harper, and Todd Wilson, \emph{{Computational
-			Higher-Dimensional Type Theory}}, Proceedings of the 44th {ACM} {SIGPLAN}
-	Symposium on Principles of Programming Languages, {POPL} 2017, Paris, France,
-	January 18-20, 2017, 2017, pp.~680--693.
-
-	\bibitem{AltenkirchK16}
-	Thorsten Altenkirch and Ambrus Kaposi, \emph{{Type Theory in Type Theory using
-			Quotient Inductive Types}}, Proceedings of the 43rd Annual {ACM}
-	{SIGPLAN-SIGACT} Symposium on Principles of Programming Languages, {POPL}
-	2016, St. Petersburg, FL, USA, January 20 - 22, 2016, 2016, pp.~18--29.
-
-	\bibitem{AhrensKS15}
-	Benedikt Ahrens, Krzysztof Kapulkin, and Michael Shulman, \emph{{Univalent
-			Categories and the Rezk Completion}}, Mathematical Structures in Computer
-	Science \textbf{25} (2015), no.~5, 1010--1039.
-
-	\bibitem{AhrensL19}
-	Benedikt Ahrens and Peter~LeFanu Lumsdaine, \emph{{Displayed Categories}},
-	Logical Methods in Computer Science \textbf{15} (2019), no.~1.
-
-	\bibitem{AngiuliMLH16}
-	Carlo Angiuli, Edward Morehouse, Daniel~R. Licata, and Robert Harper,
-	\emph{{Homotopical Patch Theory}}, J. Funct. Program. \textbf{26} (2016),
-	e18.
+	Steven Awodey, Nicola Gambino, and Kristina Sojakova.
+	\newblock {Inductive Types in Homotopy Type Theory}.
+	\newblock In {\em Proceedings of the 27th Annual {IEEE} Symposium on Logic in
+		Computer Science, {LICS} 2012, Dubrovnik, Croatia, June 25-28, 2012}, pages
+	95--104, 2012.
+
+	\bibitem{BasoldGW17}
+	Henning Basold, Herman Geuvers, and Niels van~der Weide.
+	\newblock {Higher Inductive Types in Programming}.
+	\newblock {\em J. {UCS}}, 23(1):63--88, 2017.
 
 	\bibitem{BezemCH13}
-	Marc Bezem, Thierry Coquand, and Simon Huber, \emph{{A Model of Type Theory in
-			Cubical Sets}}, 19th International Conference on Types for Proofs and
-	Programs, {TYPES} 2013, April 22-26, 2013, Toulouse, France, 2013,
-	pp.~107--128.
-
-	\bibitem{BasoldGW17}
-	Henning Basold, Herman Geuvers, and Niels van~der Weide, \emph{{Higher
-			Inductive Types in Programming}}, J. {UCS} \textbf{23} (2017), no.~1, 63--88.
+	Marc Bezem, Thierry Coquand, and Simon Huber.
+	\newblock {A Model of Type Theory in Cubical Sets}.
+	\newblock In {\em 19th International Conference on Types for Proofs and
+		Programs, {TYPES} 2013, April 22-26, 2013, Toulouse, France}, pages 107--128,
+	2013.
+
+	\bibitem{capriotti2017univalent}
+	Paolo Capriotti and Nicolai Kraus.
+	\newblock {Univalent Higher Categories via Complete Semi-Segal Types}.
+	\newblock {\em Proceedings of the ACM on Programming Languages}, 2(POPL):44,
+	2017.
+
+	\bibitem{CavalloH19}
+	Evan Cavallo and Robert Harper.
+	\newblock {Higher Inductive Types in Cubical Computational Type Theory}.
+	\newblock {\em {PACMPL}}, 3({POPL}):1:1--1:27, 2019.
+
+	\bibitem{DBLP:journals/mscs/ChapmanUV19}
+	James Chapman, Tarmo Uustalu, and Niccol{\`{o}} Veltri.
+	\newblock {Quotienting the Delay Monad by Weak Bisimilarity}.
+	\newblock {\em Mathematical Structures in Computer Science}, 29(1):67--92,
+	2019.
 
 	\bibitem{CohenCHM16}
-	Cyril Cohen, Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg,
-	\emph{{Cubical Type Theory: A Constructive Interpretation of the Univalence
-			Axiom}}, CoRR \textbf{abs/1611.02108} (2016).
-
-	\bibitem{CavalloH19}
-	Evan Cavallo and Robert Harper, \emph{{Higher Inductive Types in Cubical
-			Computational Type Theory}}, {PACMPL} \textbf{3} (2019), no.~{POPL},
-	1:1--1:27.
+	Cyril Cohen, Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg.
+	\newblock {Cubical Type Theory: a Constructive Interpretation of the Univalence
+		Axiom}.
+	\newblock {\em CoRR}, abs/1611.02108, 2016.
 
 	\bibitem{CoquandHM18}
-	Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg, \emph{{On Higher
-			Inductive Types in Cubical Type Theory}}, Proceedings of the 33rd Annual
-	{ACM/IEEE} Symposium on Logic in Computer Science, {LICS} 2018, Oxford, UK,
-	July 09-12, 2018, 2018, pp.~255--264.
-
-	\bibitem{capriotti2017univalent}
-	Paolo Capriotti and Nicolai Kraus, \emph{{Univalent Higher Categories via
-			Complete Semi-Segal Types}}, Proceedings of the ACM on Programming Languages
-	\textbf{2} (2017), no.~POPL, 44.
+	Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg.
+	\newblock {On Higher Inductive Types in Cubical Type Theory}.
+	\newblock In {\em Proceedings of the 33rd Annual {ACM/IEEE} Symposium on Logic
+		in Computer Science, {LICS} 2018, Oxford, UK, July 09-12, 2018}, pages
+	255--264, 2018.
+
+	\bibitem{dybjer1994inductive}
+	Peter Dybjer.
+	\newblock {Inductive Families}.
+	\newblock {\em Formal aspects of computing}, 6(4):440--465, 1994.
 
 	\bibitem{DybjerM18}
-	Peter Dybjer and Hugo Moeneclaey, \emph{{Finitary Higher Inductive Types in the
-			Groupoid Model}}, Electr. Notes Theor. Comput. Sci. \textbf{336} (2018),
-	119--134.
-
-	\bibitem{dybjer1994inductive}
-	Peter Dybjer, \emph{{Inductive Families}}, Formal aspects of computing
-	\textbf{6} (1994), no.~4, 440--465.
+	Peter Dybjer and Hugo Moeneclaey.
+	\newblock {Finitary Higher Inductive Types in the Groupoid Model}.
+	\newblock {\em Electr. Notes Theor. Comput. Sci.}, 336:119--134, 2018.
+
+	\bibitem{DBLP:conf/lics/FinsterM17}
+	Eric Finster and Samuel Mimram.
+	\newblock {A Type-Theoretical Definition of Weak $\omega$-Categories}.
+	\newblock In {\em 32nd Annual {ACM/IEEE} Symposium on Logic in Computer
+		Science, {LICS} 2017, Reykjavik, Iceland, June 20-23, 2017}, pages 1--12,
+	2017.
 
 	\bibitem{FruminGGW18}
-	Dan Frumin, Herman Geuvers, L{\'{e}}on Gondelman, and Niels van~der Weide,
-	\emph{{Finite Sets in Homotopy Type Theory}}, Proceedings of the 7th {ACM}
-	{SIGPLAN} International Conference on Certified Programs and Proofs, {CPP}
-	2018, Los Angeles, CA, USA, January 8-9, 2018, 2018, pp.~201--214.
+	Dan Frumin, Herman Geuvers, L{\'{e}}on Gondelman, and Niels van~der Weide.
+	\newblock {Finite Sets in Homotopy Type Theory}.
+	\newblock In {\em Proceedings of the 7th {ACM} {SIGPLAN} International
+		Conference on Certified Programs and Proofs, {CPP} 2018, Los Angeles, CA,
+		USA, January 8-9, 2018}, pages 201--214, 2018.
 
 	\bibitem{hermida1998structural}
-	C.~Hermida and B.~Jacobs.
-	\newblock Structural induction and coinduction in a fibrational setting.
+	Claudio Hermida and Bart Jacobs.
+	\newblock {Structural Induction and Coinduction in a Fibrational Setting}.
 	\newblock {\em Information and computation}, 145(2):107--152, 1998.
 
+	\bibitem{DBLP:conf/tlca/HirschowitzHT15}
+	Andr{\'{e}} Hirschowitz, Tom Hirschowitz, and Nicolas Tabareau.
+	\newblock {Wild $\omega$-Categories for the Homotopy Hypothesis in Type
+		Theory}.
+	\newblock In {\em 13th International Conference on Typed Lambda Calculi and
+		Applications, {TLCA} 2015, July 1-3, 2015, Warsaw, Poland}, pages 226--240,
+	2015.
+
 	\bibitem{HofmannS94}
-	Martin Hofmann and Thomas Streicher, \emph{{The Groupoid Model Refutes
-			Uniqueness of Identity Proofs}}, Proceedings of the Ninth Annual Symposium on
-	Logic in Computer Science {(LICS} '94), Paris, France, July 4-7, 1994, 1994,
-	pp.~208--212.
+	Martin Hofmann and Thomas Streicher.
+	\newblock {The Groupoid Model Refutes Uniqueness of Identity Proofs}.
+	\newblock In {\em Proceedings of the Ninth Annual Symposium on Logic in
+		Computer Science {(LICS} '94), Paris, France, July 4-7, 1994}, pages
+	208--212, 1994.
 
 	\bibitem{KaposiK18}
-	Ambrus Kaposi and Andr{\'{a}}s Kov{\'{a}}cs, \emph{{A Syntax for Higher
-			Inductive-Inductive Types}}, 3rd International Conference on Formal
-	Structures for Computation and Deduction, {FSCD} 2018, July 9-12, 2018,
-	Oxford, {UK}, 2018, pp.~20:1--20:18.
+	Ambrus Kaposi and Andr{\'{a}}s Kov{\'{a}}cs.
+	\newblock {A Syntax for Higher Inductive-Inductive Types}.
+	\newblock In {\em 3rd International Conference on Formal Structures for
+		Computation and Deduction, {FSCD} 2018, July 9-12, 2018, Oxford, {UK}}, pages
+	20:1--20:18, 2018.
 
 	\bibitem{KaposiKA19}
-	Ambrus Kaposi, Andr{\'{a}}s Kov{\'{a}}cs, and Thorsten Altenkirch,
-	\emph{{Constructing Quotient Inductive-Inductive Types}}, {PACMPL} \textbf{3}
-	(2019), no.~{POPL}, 2:1--2:24.
+	Ambrus Kaposi, Andr{\'{a}}s Kov{\'{a}}cs, and Thorsten Altenkirch.
+	\newblock {Constructing Quotient Inductive-Inductive Types}.
+	\newblock {\em {PACMPL}}, 3({POPL}):2:1--2:24, 2019.
 
 	\bibitem{simpset}
-	Chris Kapulkin and Peter~LeFanu Lumsdaine, \emph{{The Simplicial Model of
-			Univalent Foundations (after Voevodsky)}}, 2012.
+	Chris Kapulkin and Peter~LeFanu Lumsdaine.
+	\newblock {The Simplicial Model of Univalent Foundations (after Voevodsky)},
+	2012.
 
 	\bibitem{Kraus16}
-	Nicolai Kraus, \emph{{Constructions with Non-Recursive Higher Inductive
-			Types}}, Proceedings of the 31st Annual {ACM/IEEE} Symposium on Logic in
-	Computer Science, {LICS} '16, New York, NY, USA, July 5-8, 2016, 2016,
-	pp.~595--604.
+	Nicolai Kraus.
+	\newblock {Constructions with Non-Recursive Higher Inductive Types}.
+	\newblock In {\em Proceedings of the 31st Annual {ACM/IEEE} Symposium on Logic
+		in Computer Science, {LICS} '16, New York, NY, USA, July 5-8, 2016}, pages
+	595--604, 2016.
 
 	\bibitem{KrausRaumer}
-	Nicolai Kraus and Jakob von Raumer, \emph{{Path Spaces of Higher Inductive
-			Types in Homotopy Type Theory}}, CoRR \textbf{abs/1901.06022} (2019).
+	Nicolai Kraus and Jakob von Raumer.
+	\newblock {Path Spaces of Higher Inductive Types in Homotopy Type Theory}.
+	\newblock {\em CoRR}, abs/1901.06022, 2019.
 
 	\bibitem{LicataF14}
-	Daniel~R. Licata and Eric Finster, \emph{{Eilenberg-MacLane Spaces in Homotopy
-			Type Theory}}, Joint Meeting of the Twenty-Third {EACSL} Annual Conference on
-	Computer Science Logic {(CSL)} and the Twenty-Ninth Annual {ACM/IEEE}
+	Daniel~R. Licata and Eric Finster.
+	\newblock {Eilenberg-MacLane Spaces in Homotopy Type Theory}.
+	\newblock In {\em Joint Meeting of the Twenty-Third {EACSL} Annual Conference
+		on Computer Science Logic {(CSL)} and the Twenty-Ninth Annual {ACM/IEEE}
 		Symposium on Logic in Computer Science (LICS), {CSL-LICS} '14, Vienna,
-	Austria, July 14 - 18, 2014, 2014, pp.~66:1--66:9.
+		Austria, July 14 - 18, 2014}, pages 66:1--66:9, 2014.
 
 	\bibitem{LicataS13}
-	Daniel~R. Licata and Michael Shulman, \emph{{Calculating the Fundamental Group
-			of the Circle in Homotopy Type Theory}}, 28th Annual {ACM/IEEE} Symposium on
-	Logic in Computer Science, {LICS} 2013, New Orleans, LA, USA, June 25-28,
-	2013, 2013, pp.~223--232.
+	Daniel~R. Licata and Michael Shulman.
+	\newblock {Calculating the Fundamental Group of the Circle in Homotopy Type
+		Theory}.
+	\newblock In {\em 28th Annual {ACM/IEEE} Symposium on Logic in Computer
+		Science, {LICS} 2013, New Orleans, LA, USA, June 25-28, 2013}, pages
+	223--232, 2013.
+
+	\bibitem{lumsdaine2009weak}
+	Peter~LeFanu Lumsdaine.
+	\newblock {Weak $\omega$-categories from Intensional Type Theory}.
+	\newblock In {\em International Conference on Typed Lambda Calculi and
+		Applications}, pages 172--187. Springer, 2009.
 
 	\bibitem{lumsdaine2017semantics}
-	Peter~LeFanu Lumsdaine and Mike Shulman, \emph{{Semantics of Higher Inductive
-			Types}}, arXiv preprint arXiv:1705.07088 (2017).
+	Peter~LeFanu Lumsdaine and Mike Shulman.
+	\newblock {Semantics of Higher Inductive Types}.
+	\newblock {\em arXiv preprint arXiv:1705.07088}, 2017.
 
 	\bibitem{mac2013categories}
-	Saunders Mac~Lane, \emph{{Categories for the Working Mathematician}}, vol.~5,
-	Springer Science \& Business Media, 2013.
+	Saunders Mac~Lane.
+	\newblock {\em {Categories for the Working Mathematician}}, volume~5.
+	\newblock Springer Science \& Business Media, 2013.
 
 	\bibitem{moeneclaey2016schema}
-	H.~Moeneclaey.
+	Hugo Moeneclaey.
 	\newblock {A Schema for Higher Inductive Types of Level One and Its
@@
 	\bibitem{rijke2017join}
-	Egbert Rijke, \emph{{The Join Construction}}, arXiv preprint arXiv:1701.07538
-	(2017).
+	Egbert Rijke.
+	\newblock {The Join Construction}.
+	\newblock {\em arXiv preprint arXiv:1701.07538}, 2017.
 
 	\bibitem{RijkeS15}
-	Egbert Rijke and Bas Spitters, \emph{{Sets in Homotopy Type Theory}},
-	Mathematical Structures in Computer Science \textbf{25} (2015), no.~5,
-	1172--1202.
+	Egbert Rijke and Bas Spitters.
+	\newblock {Sets in Homotopy Type Theory}.
+	\newblock {\em Mathematical Structures in Computer Science}, 25(5):1172--1202,
+	2015.
 
 	\bibitem{Sojakova15}
-	Kristina Sojakova, \emph{{Higher Inductive Types as Homotopy-Initial
-			Algebras}}, Proceedings of the 42nd Annual {ACM} {SIGPLAN-SIGACT} Symposium
-	on Principles of Programming Languages, {POPL} 2015, Mumbai, India, January
-	15-17, 2015, 2015, pp.~31--42.
+	Kristina Sojakova.
+	\newblock {Higher Inductive Types as Homotopy-Initial Algebras}.
+	\newblock In {\em Proceedings of the 42nd Annual {ACM} {SIGPLAN-SIGACT}
+		Symposium on Principles of Programming Languages, {POPL} 2015, Mumbai, India,
+		January 15-17, 2015}, pages 31--42, 2015.
+
+	\bibitem{street1972formal}
+	Ross Street.
+	\newblock {The Formal Theory of Monads}.
+	\newblock {\em Journal of Pure and Applied Algebra}, 2(2):149--168, 1972.
 
 	\bibitem{hottbook}
-	{The Univalent Foundations Program}, \emph{{Homotopy Type Theory: Univalent
-			Foundations of Mathematics}}, \url{https://homotopytypetheory.org/book},
-	Institute for Advanced Study, 2013.
+	{The Univalent Foundations Program}.
+	\newblock {\em {Homotopy Type Theory: Univalent Foundations of Mathematics}}.
+	\newblock \url{https://homotopytypetheory.org/book}, Institute for Advanced
+	Study, 2013.
+
+	\bibitem{van2011types}
+	Benno Van Den~Berg and Richard Garner.
+	\newblock {Types are Weak $\omega$-Groupoids}.
+	\newblock {\em Proceedings of the London Mathematical Society},
+	102(2):370--394, 2011.
+
+	\bibitem{Doorn16}
+	Floris van Doorn.
+	\newblock {Constructing the Propositional Truncation using Non-Recursive HITs}.
+	\newblock In {\em Proceedings of the 5th {ACM} {SIGPLAN} Conference on
+		Certified Programs and Proofs, Saint Petersburg, FL, USA, January 20-22,
+		2016}, pages 122--129, 2016.
 
 	\bibitem{UniMath}
-	Vladimir Voevodsky, Benedikt Ahrens, Daniel Grayson, et~al., \emph{{UniMath ---
-			a computer-checked library of univalent mathematics}}, {available} at
-	\url{https://github.com/UniMath/UniMath}.
-
-	\bibitem{Doorn16}
-	Floris van Doorn, \emph{{Constructing the Propositional Truncation using
-			Non-Recursive HITs}}, Proceedings of the 5th {ACM} {SIGPLAN} Conference on
-	Certified Programs and Proofs, Saint Petersburg, FL, USA, January 20-22,
-	2016, 2016, pp.~122--129.	
+	Vladimir Voevodsky, Benedikt Ahrens, Daniel Grayson, et~al.
+	\newblock {UniMath --- a computer-checked library of univalent mathematics}.
+	\newblock {available} at \url{https://github.com/UniMath/UniMath}.
+
 \end{thebibliography}

### 2021-11-17 presentation/presentation.tex

\documentclass{beamer}

\usepackage{pgfpages}
\setbeameroption{hide notes} % Only slides
% \setbeameroption{show only notes} % Only notes
%\setbeameroption{show notes on second screen=right}% Both

\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{color}

\usepackage{bussproofs}

\usepackage{colonequals}

\usepackage{listings}

\usepackage[all,cmtip]{xy}

\usetheme{default}
\usecolortheme{default}

\lstset{escapeinside={<@}{@>}}
\setbeamertemplate{sidebar right}{}
\setbeamertemplate{footline}{%
	\hfill\usebeamertemplate***{navigation symbols}
	\hspace{1cm}\insertframenumber{}/\inserttotalframenumber}

\title{The Construction of Set-Truncated Higher Inductive Types}
\author{\textbf{Niels van der Weide} \and Herman Geuvers}
\institute{Radboud University}
\date[MFPS2019]{June 7, 2019}

\newcommand{\remove}[1]{}

\newcommand{\sets}{\mathbf{Set}}
\newcommand{\setoids}{\mathbf{Setoid}}
\newcommand{\quotient}{\mathbf{Quot}}
\newcommand{\paths}{\mathbf{Path}}

\newcommand{\prealgsets}{\mathbf{PreAlgSet}}
\newcommand{\prealgsetoids}{\mathbf{PreAlgSetoid}}
\newcommand{\prealgquotient}{\mathbf{PreAlgQuot}}
\newcommand{\prealgpaths}{\mathbf{PreAlgPath}}

\newcommand{\algsets}{\mathbf{AlgSet}}
\newcommand{\algsetoids}{\mathbf{AlgSetoid}}
\newcommand{\algquotient}{\mathbf{AlgQuot}}
\newcommand{\algpaths}{\mathbf{AlgPath}}

% Endpoints
\newcommand{\ep}[3]{\mathcal{E}_{#1}(#2,#3)} % type of endpoinst
\newcommand{\id}[1]{\constructor{id}_{#1}} % identity endpoints
\newcommand{\comp}[2]{#1 \cdot #2} % composition of endpoints
\newcommand{\inle}{\constructor{inl}} %left inclusion of endpoints
\newcommand{\inre}{\constructor{inr}} % right inclusion of endpoints
\newcommand{\prle}{\constructor{pr}_1} % first projection of endpoints
\newcommand{\prre}{\constructor{pr}_2} % second projection of endpoints
\newcommand{\pair}[2]{(#1 , #2)} % pairing of endpoints
\newcommand{\Ce}{\constructor{c}} % constant endpoint
\newcommand{\constr}{\constructor{constr}} % constructor endpoint
\newcommand{\fmap}{\constructor{fmap}} % function endpoint

\newcommand{\poly}{\mathcal{P}} % type of polynomials
\newcommand{\C}{\constructor{C}} % constant polynomial
\newcommand{\I}{\constructor{I}} % identity polynomial
\newcommand{\sumP}[2]{#1 + #2} % sum of polynomials
\newcommand{\prodP}[2]{#1 \times #2} % product of polynomials

\newcommand{\hset}{\type{hSet}} % sets

\begin{document}
\beamertemplatenavigationsymbolsempty

\frame
{
	\maketitle
}

\begin{frame}
\frametitle{Homotopy Type Theory: Another Perspective on Types}
Its features are:
\begin{itemize}
	\item Equality is proof relevant (\emph{goodbye UIP})
	\item<2,3,4> Interpretation in simplicial sets (\emph{types are spaces, terms are points, equalities are paths})
	\item<3,4> Univalence Axiom (\emph{equality of types is isomorphism})
	\item<4> \textbf{Higher Inductive Types} (\emph{building spaces})
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higher Inductive Types? What are they?}
Inductive Types: a type generated by constructors for its points

For example, $\mathbb{N}$ is generated by $Z : \mathbb{N}$ and $S : \mathbb{N} \rightarrow \mathbb{N}$.
\end{frame}

\begin{frame}
\frametitle{Higher Inductive Types? What are they?}
\textbf{Higher} Inductive Types (HIT): a type generated by constructors for its points \textbf{and paths} (equalities)

For example, $X$ is generated by $Z : X$ and $S : X \rightarrow X$ \textbf{and}
\[
m : \prod_{n : X} n = S(S \> n).
\]

\pause

Now we have two ways to prove $S \> Z = S^3 \> Z$:
\begin{itemize}
	\item use $m(S \> Z)$
	\item use $m(Z)$ and $S$ preserves equality
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higher Inductive Types? What are they?}
\textbf{Higher} Inductive Types (HIT): a type generated by constructors for its points, paths (equalities), \textbf{and homotopies (equalities of equalities)}

For example, $\mathbb{N}_2$ is generated by $Z : \mathbb{N}_2$ and $S : \mathbb{N}_2 \rightarrow \mathbb{N}_2$ \textbf{and two equalities:}
\[
m : \prod_{n : \mathbb{N}_2} n = S(S \> n),
\]
\[
t : \prod_{n, m : \mathbb{N}_2} \prod_{p, q : n = m} p = q.
\]
\end{frame}

\begin{frame}
\frametitle{But let's not get too high}
In this talk, we only consider HITs
\begin{itemize}
	\item constructed by giving points and equalities
	\item and with the constructor
	\[
	t : \prod_{x, y : X} \prod_{p, q : x = y} p = q.
	\]
\end{itemize}
We call these \textbf{set-truncated HITs}.

Recall: a set is a type for which all $p, q : x = y$ are the same.
\end{frame}

\begin{frame}
\frametitle{Now, what did we do?}
Our result: all set-truncated HITs exists if two simple ones exist:
\begin{itemize}
	\item The \textbf{quotient}. Given $A$ and an equivalence relation $R$ on $A$, identify the points in $A$ via $R$.
	\item Given a type $A$, then the \textbf{propositional truncation} $||A||$ is $A$ with all its points identified.
\end{itemize}
Note: we construct them in HoTT. Formalization in UniMath.
\end{frame}

\begin{frame}
\frametitle{A Bird's-Eye View of our Construction}
The steps:
\begin{itemize}
	\item Define signatures of HITs (\emph{how to describe them})
	\item Give categories of algebras in sets \textbf{and setoids} (\emph{the introduction rules})
	\item Use initial algebra semantics (\emph{showing induction by initiality})
	\item Relate those categories by an adjunction (\emph{the main idea})
	\item Construct the initial algebra in setoids (\emph{where we get to work})
\end{itemize}
Recall:
\begin{itemize}
	\item a set is a type for which all proofs of equality are equal
	\item a setoid is a set with an equivalence relation
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Wells of Inspiration}
Note
\begin{itemize}
	\item Initial algebra semantics is used: QIITs (by Altenkirch, Capriotti, Dijkstra, Kraus, Forsberg) and W-suspensions (Sojakova).
	\item To obtain the adjunction, we use a result by Hermida and Jacobs.
	\item The construction of the initial algebra in setoids is an adaption of work by Dybjer and Moenclaey.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Let's Get Started: Signatures for HITs}
Recall: $\mathbb{N}_2$ is generated by $Z : \mathbb{N}_2$ and $S : \mathbb{N}_2 \rightarrow \mathbb{N}_2$ and two equalities:
\[
m : \prod_{n : \mathbb{N}_2} n = S(S \> n),
\]
\[
t : \prod_{n, m : \mathbb{N}_2} \prod_{p, q : n = m} p = q.
\]

To define signatures of HITs, note the following:
\begin{itemize}
	\item We must describe arguments of the point constructors
	\item We must describe the possible endpoints for the equalities, for which we can refer to the point constructor
\end{itemize}
Then the introduction/elimination rules are derived.
\end{frame}

\begin{frame}
\frametitle{First Ingredient: Point Constructors}
Same idea as for inductive types.

We use \textbf{finitary polynomials}.
These are generated by
\begin{itemize}
	\item The \emph{identity}
	\item Given a set $X$, we have a \emph{constant} polynomial on $X$
	\item Given two polynomials, we have their \emph{product} and \emph{sum}
\end{itemize}
Recall $\mathbb{N}$ generated by $Z : \mathbb{N}$ and $S : \mathbb{N} \rightarrow \mathbb{N}$.

This is represented by $F(X) = 1 + X$
\end{frame}

\begin{frame}
\frametitle{Second Ingredient: Path Constructors}
Recall path of $\mathbb{N}_2$:
\[
m : \prod_{n : \mathbb{N}_2} n = S(S \> n),
\]
\pause
There are two ingredients for path constructors:
\begin{itemize}
	\item A polynomial representing the \emph{source} of the equation
	\item Two endpoints representing the \emph{sides} of the equation 
\end{itemize}
The endpoints represent all possible left- and right hand sides of equations.
Note: they \emph{depend on the point constructor and source}.
\pause
Main challenge: define tthe type of endpoints
\begin{itemize}
	\item it's a type $\mathcal{E}_P(S)$ depending polynomials $P, S$
	\item inductively generated by 10 constructors
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Putting it together: Signatures}
\begin{definition}
A \textbf{HIT signature} consists of
\begin{itemize}
	\item A polynomial $P$ representing its \emph{point constructor}
	\item A type $J$ representing \emph{labels for its path constructors}
	\item For each $j : J$, a polynomial $S_j$ representing the \emph{arguments of the path constructors}
	\item For each $j : J$, two endpoint with source $S_j$ using constructors from $P$ representing the \emph{path}
\end{itemize}
\end{definition}
Note: we will interpret signatures in sets, so we always have a constructor
\[
t : \prod_{n, m : X} \prod_{p, q : n = m} p = q.
\]
\end{frame}

\begin{frame}
\frametitle{How does this give rise to a notion of HITs?}
\begin{itemize}
	\item All we did so far, was say how to describe the constructors.
	\item Soon we discuss algebras, which describe the introduction rules.
	\item You also need to formulate an induction principle.
	\item Details on that are in the paper/formalization.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Intermezzo: Some Examples}
\begin{itemize}
	\item Signature $\mathbb{N}_2$ (discussed before)
	\item Similarly, we can define a signature for the integers.
	\item We can define signatures of groups, rings, and so on
	\item Also: polynomials, free algebras
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{A Bird's-Eye View of our Construction}
The steps:
\begin{itemize}
	\item Define signatures of HITs (how to describe them)
	\item \textbf{Give categories of algebras in sets and setoids (the introduction rules)}
	\item Use initial algebra semantics (showing induction by initiality)
	\item Relate those categories by an adjunction (the main idea)
	\item Construct the initial algebra in setoids (where we get to work)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Algebra in Two Steps: the \textbf{pre}algebras}
Note: each polynomial $P$ gives rise to a functor $\overline{P}$ on $\sets$.

Now let $S$ be a signature and let $P$ be the point constructor.
\begin{itemize}
	\item A \textbf{prealgebra} on a signature consists of a set $X$ with a map $\overline{P} \> X \rightarrow X$.
	\item This forms a category $\prealgsets(P)$ whose morphisms are
	\[
	\xymatrix
	{
		\overline{P} \> X \ar[d] \ar[r]^{P \> f} & \overline{P} \> Y \ar[d]\\
		X \ar[r]_f & Y 
	}
	\]
	\item Note: we have a functor $U : \prealgsets(P) \rightarrow \sets$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Algebra in Two Steps: the \textbf{actual} algebras}
Now come the equations.

Let $e$ be an endpoint with source $S$, and constructor $P$.
Note we have functors:
\[
\xymatrix
{
	\prealgsets(P) \ar[r]^-{U} & \sets \ar[r]^{S} & \sets 
}
\]
Then $e$ gives a natural transformation from $S \circ U$ to $U$.

Algebras are defined as a full subcategory of prealgebras.
\end{frame}

\begin{frame}
\frametitle{We can repeat this story for setoids}
It will be much the same but with setoids instead.
\end{frame}

\begin{frame}
\frametitle{A Bird's-Eye View of our Construction}
The steps:
\begin{itemize}
	\item Define signatures of HITs (how to describe them)
	\item Give categories of algebras in sets and setoids (the introduction rules)
	\item \textbf{Use initial algebra semantics (showing induction by initiality)}
	\item Relate those categories by an adjunction (the main idea)
	\item Construct the initial algebra in setoids (where we get to work)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{The Induction Principle and Initial Algebras}
\begin{itemize}
	\item HITs satisfy an \emph{induction principle} (IP)
	\item The IP is formulated with \emph{displayed algebras} (aka fibred algebras)
	\item To verify IP, we use \emph{initial algebra semantics}
	\item It says: \textbf{induction follows from initiality}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{A Bird's-Eye View of our Construction}
The steps:
\begin{itemize}
	\item Define signatures of HITs (how to describe them)
	\item Give categories of algebras in sets and setoids (the introduction rules)
	\item Use initial algebra semantics (showing induction by initiality)
	\item \textbf{Relate those categories by an adjunction (the main idea)}
	\item Construct the initial algebra in setoids (where we get to work)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{The moment we waited for: Adjunctions}
Let's start with the ``base''.
Write
\begin{itemize}
	\item $\sets$ and $\setoids$ for the categories of sets and setoids respectively
	\item $\quotient$ sends a setoid $(X,R)$ to the quotient of $X$ by $R$
	\item $\paths$ sends a set $X$ to the setoid $(X, =)$
\end{itemize}
Then we have an adjunction
\[
\xymatrix
{
	\sets \ar@/^/[rrrrr]_-{\top}^-{\paths} & & & & & \ar@/^/[lllll]^-{\quotient} \setoids
}
\]
\end{frame}

\begin{frame}
\frametitle{The moment we waited for: Adjunctions}
Lift it to an adjunction on prealgebras (Hermida and Jacobs)
\[
\xymatrix
{
	\prealgsets \ar@/^/[rrrrr]_-{\top}^-{\prealgpaths} \ar[d] & & & & & \ar@/^/[lllll]^-{\prealgquotient} \prealgsetoids \ar[d] \\
	\sets \ar@/^/[rrrrr]_-{\top}^-{\paths} & & & & & \ar@/^/[lllll]^-{\quotient} \setoids
}
\]
Here we need the polynomials are finitary.

For infinitary case, we need AC (Chapman, Uustalu, Veltri)
\end{frame}

\begin{frame}
\frametitle{The moment we waited for: Adjunctions}
Next we lift it to the level of algebras
\[
\xymatrix
{
	\algsets \ar@/^/[rrrrr]_-{\top}^-{\algpaths} \ar[d] & & & & & \ar@/^/[lllll]^-{\algquotient} \algsetoids \ar[d] \\
	\prealgsets \ar@/^/[rrrrr]_-{\top}^-{\prealgpaths} \ar[d] & & & & & \ar@/^/[lllll]^-{\prealgquotient} \prealgsetoids \ar[d] \\
	\sets \ar@/^/[rrrrr]_-{\top}^-{\paths} & & & & & \ar@/^/[lllll]^-{\quotient} \setoids
}
\]
\end{frame}

\begin{frame}
\frametitle{Before we continue, where are we?}
\begin{itemize}
	\item Define signatures of HITs (how to describe them)
	\item Give categories of algebras in sets and setoids (the introduction rules)
	\item Use initial algebra semantics (showing induction by initiality)
	\item Relate those categories by an adjunction (the main idea)
	\item \textbf{Construct the initial algebra in setoids (where we get to work)}
\end{itemize}

Recall that our goal was to construct HITs.
However, so far, no constructing actually happened.

We only did preparatory work, which shows that

\center{\textbf{We obtain HITs by constructing initial algebras in setoids!}}
\end{frame}

\begin{frame}
\frametitle{Finishing the proof: The Initial Algebra in Setoids}
\begin{itemize}
	\item Dybjer and Moenclaey give an interpretation of HITs in the setoid and groupoid model
	\item The set is inductively generated by the point constructor
	\item The equivalence relation is the inductive family generated by the path constructors
\end{itemize}
Here we need the propositional truncation.
\begin{itemize}
	\item In HoTT, equivalence relations take values in propositions
	\item Recall: a proposition is a type for which all inhabitants are equal
	\item To force the generated relation to be a proposition, we truncate it
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Time to Wrap Up}
\begin{theorem}
In UF with quotients and the propositional truncation, we can construct all finitary set-truncated HITs.
\end{theorem}
We obtain two consequences of our construction:
\begin{itemize}
	\item A uniqueness principle for HITs (\emph{go univalence})
	\item A characterization of the path space of HITs
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Where to go from here?}
Remove the truncatedness restriction.
\begin{itemize}
	\item First step: go to 1-types/groupoids
	\item Their structure is encapsulated by \textbf{bicategories}
	\item Imitate this construction bicategorically
\end{itemize}
Formalization: \url{https://github.com/nmvdw/SetHITs}.
\end{frame}

\begin{frame}
\frametitle{References}
\begin{enumerate}
	\item T. Altenkirch, P. Capriotti, G. Dijkstra, N. Kraus, and
	F.N. Forsberg.
	Quotient Inductive-Inductive Types.
	In FOSSACS 2018, pages 293--310.
	\item J. Chapman, T. Uustalu, and N. Veltri.
	Quotienting the Delay Monad by Weak Bisimilarity.
	MSCS, 29(1):67--92,
	2019.
	\item P. Dybjer and H. Moeneclaey.
	Finitary Higher Inductive Types in the Groupoid Model.
	ENTCS, 336:119--134.
	\item C. Hermida and B. Jacobs.
	Structural Induction and Coinduction in a Fibrational Setting.
	{\em Information and computation}, 145(2):107--152.
	\item K. Sojakova.
	Higher Inductive Types as Homotopy-Initial Algebras.
	In POPL 2015, pages 31--42.
	\item V. Voevodsky, B. Ahrens, D. Grayson, et~al.
	UniMath --- a computer-checked library of univalent mathematics.
	available at \url{https://github.com/UniMath/UniMath}.
\end{enumerate}
\end{frame}

\remove{
\frametitle{Extra Slide: All Endpoints}
\begin{prooftree}
	\AxiomC{$P : \poly$}
	\UnaryInfC{$\id{A} : \ep{A}{P}{P}$}
\end{prooftree}
\begin{bprooftree}
	\AxiomC{$P, Q, R : \poly$}
	\AxiomC{$e_1 : \ep{A}{P}{Q}$}
	\AxiomC{$e_2 : \ep{A}{Q}{R}$}
	\TrinaryInfC{$\comp{e_1}{e_2} : \ep{A}{P}{R}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P, Q : \poly$}
	\UnaryInfC{$\inle : \ep{A}{P}{\sumP{P}{Q}}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P, Q : \poly$}
	\UnaryInfC{$\inre : \ep{A}{Q}{\sumP{P}{Q}}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P, Q : \poly$}
	\UnaryInfC{$\prle : \ep{A}{\prodP{P}{Q}}{P}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P, Q : \poly$}
	\UnaryInfC{$\prre : \ep{A}{\prodP{P}{Q}}{Q}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$\constr : \ep{A}{A}{\I}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P : \poly$}
	\AxiomC{$X : \hset$}
	\AxiomC{$x : X$}
	\TrinaryInfC{$\Ce \> x : \ep{A}{P}{\C \> X}$}
\end{bprooftree}
\begin{bprooftree}
	\AxiomC{$P, Q, R: \poly$}
	\AxiomC{$e_1 : \ep{A}{P}{Q}$}
	\AxiomC{$e_2 : \ep{A}{P}{R}$}
	\TrinaryInfC{$\pair{e_1}{e_2} : \ep{A}{P}{\prodP{Q}{R}}$}
\end{bprooftree}
}

\end{document}
